### 2015-12-20 paper/images/flow.tex
add paper

% Define block styles
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
text width=4em, text centered, rounded corners, minimum height=3em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, minimum height=2em, node distance = 2.5cm]

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[node distance = 1.5cm, auto]
    % Place nodes
    \node [block] (reomodel) {REO Models};
    \node [cloud, left of=reomodel] (human) {Human};
    \node [block, below left = of reomodel] (tsamodel) {TSA};
    \node [block, below right = of reomodel] (mealymodel) {Mealy Machines};
    %\node [cloud, left = of tsamodel] (verification) {Verification};
    %\node [cloud, right = of mealymodel] (blackbox) {Blackbox};
    % Draw edges
    \path [line] (reomodel) -- (tsamodel);
    \path [line] (reomodel) -- (mealymodel);
    %\path [line] (tsamodel) -- (evaluate);
    \path [line] (mealymodel) -- (tsamodel);
    \path [line] (mealymodel) |-  (reomodel);
    %\path [line] (update) |- (tsamodel);
    %\path [line] (decide) -- node {no}(stop);
    %\path [line,dashed] (human) -- (reomodel);
  \end{tikzpicture}
  \caption{Our Idea}
  \label{fig:idea}
\end{figure}

### 2015-12-20 paper/paper.tex
add paper

\documentclass[conference, a4paper]{IEEEtran}

% used for flow charts
\usepackage{tikz}
% FIXME finally no todos should exist in this draft
\usepackage[textsize=tiny]{todonotes}
% positioning is used for below lef = of
\usetikzlibrary{shapes,arrows, positioning}

\title{Active Learning : From Blackbox To Timed Connectors}
\author{
\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{
  \IEEEauthorrefmark{1}DI, School of Mathematical Sciences, Peking University,
  Beijing, China\\
  liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
}
}

\begin{document}
\maketitle
\begin{abstract}
  Coordination is becoming more and more important, especially in concurrent programming and
  distributed systems. More and more tools are built to verify coordination models while most of
  them are facing the same problem: \emph{lack of models}. In many cases, somehow we need to check a
  connector with nothing more than a binary file. In this paper, we present a learning-based
  framework to formally verify a Reo connector in case there is no source code. From some practical
  cases, we've shown the effciency of our approach. Both the algorithm and Reo itself have been
  ported to \emph{Golang}, making it fully-prepared for parallel programming.
\end{abstract}

\begin{IEEEkeywords}
  active learning, coordination, formal method.
\end{IEEEkeywords}

\section{Introduction}

In the past few years, researchers have been focusing on this area, and come up with a
series of impressive works. 
\todo{a list}
However, most of these works are based on models, instead of binaries. Then it comes a well-known
problem: \emph{how can we obtain these models?}

The application of machine learning in formal models has a long history. There are several main
orientations: extraction of formal models and learning-guided verification technique.

% it seems that we need a graph to describe how we're doing this work
\todo{better graph}
\input{images/flow.tex}

In this paper, we presented an adapted active learning algorithm to extract timed Reo connectors
from binaries with no source code needed.

\section{Preliminaries}

\subsection{Reo Coordination Language}
\label{sec:reo}

\subsection{Active Learning and Mealy Machines}

\section{Timed Connectors as Mealy Machines}

Reo Coordination Model, obviously, is not a \emph{proper model} for learning.

So far as we can tell, most works\cite{DBLP:conf/fase/RaffeltS06} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

\todo{an example as graph}
\begin{figure}[h]
\caption{Infinite States in a Reo Model}
\label{fig:reoinfinite}
\end{figure}

While focusing on behavior of connectors, Reo doesn't give detail depiction on behavior of
components. As shown in \figurename \ref{fig:reoinfinite}, connectors are able to reject any datum
if they are not ready. But what will happen outside the connector, if the datum is rejected? This
question deserves careful consideration if we are taking an external view.

\section{From Blackbox to Timed Connectors}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
 no approximation.
\section{Case Studies}

\section{Conclusion and Future Work}

\bibliographystyle{abbrv}
\bibliography{bib}

% FIXME remove this
\listoftodos

\end{document}

### 2015-12-22 lib/learn/counterexample.go
debugging of counter-example processing functions

@@ -9,19 +9,21 @@ import "../sul"
 func (inst *Obs) CEAnalyze(cin sul.InputSeq) sul.InputSeq {
 	// generally this is a bisection algorithm
 	// written by Yiwu
-
+	logger.Println(cin)
 	oc := inst.orac.MQuery(cin)
 	//	acts := inst.orac.GetInputs()
 	sin, d, d2 := cin, cin, cin
-	lower, upper := 2, len(cin)-1
+	lower, upper := 1, len(cin)-1
 	for {
 		mid := (lower + upper) / 2
-		sin = cin[:mid-1]
+		sin = cin[:mid]
 		sout, _ := inst.Run(sin)
-		d = cin[mid-1:]
-		d2 = cin[mid:]
+		logger.Println("hypothesis execution accessseq:", sin, "->", sout)
+		d = cin[mid:]
+		d2 = cin[mid+1:]
 		sout = append(sout, d...)
 		omid := inst.orac.MQuery(sout)
+		logger.Println("mquery: ", sout, "->", omid)
 		if oc.EqualTo(&omid) {
 			lower = mid + 1
 			if upper < lower {

### 2015-12-22 lib/learn/lstar.go

@@ -29,7 +29,8 @@ func LStar(orac *sul.Oracle) *Obs {
 	c := sul.InputSeq{}
 	// cexist indicates if there's a counter-example found in last round
 	// it's initialized as true otherwise the loop will never be executed
-	for cexist := true; cexist; {
+	var i = 0
+	for cexist := true; cexist; i++ {
 		logger.Println("L* Iteration")
 		// enclose the table
 		obs.TableClose()
@@ -37,6 +38,8 @@ func LStar(orac *sul.Oracle) *Obs {
 			obs.SuffixClose()
 			obs.TableClose()
 		}
+		logger.Println("Hypothesis Iteration", i)
+		logger.Println(obs.GetHypoStr())
 		// looking up for counter-examples
 		c, cexist = orac.EQuery(obs)
 		if cexist {

### 2015-12-22 lib/learn/obstable.go

@@ -113,27 +113,40 @@ func (self *Obs) expandLp() {
 	acts := self.orac.GetInputs()
 	for i, _ := range self.SL {
 		self.SL[i].Dist = []int{}
-		for j, d := range acts {
+		for _, d := range acts {
 			newLp = append(newLp, NewLine(append(self.SL[i].Index, d)))
-			self.SL[i].Dist = append(self.SL[i].Dist, self.SpLoc+1+j)
+			self.SL[i].Dist = append(self.SL[i].Dist, len(self.SL)+len(newLp)-1)
 		}
 	}
 	self.SL = append(self.SL, newLp...)
 }
 
-func (self *Obs) Run(in sul.InputSeq) (sul.InputSeq, sul.Output) {
+func (self *Obs) SeqRun(in sul.InputSeq) ([]sul.InputSeq, []sul.Output) {
 	var loc = 0
 	var rel *sul.Output
+	indarr, outarr := []sul.InputSeq{}, []sul.Output{}
 	for i := 0; i < len(in); i++ {
 		inputindex := self.orac.GetInputIndex(*in[i])
-		loc = self.SL[loc].Dist[inputindex]
 		rel = self.SL[loc].Result[inputindex]
+		loc = self.SL[loc].Dist[inputindex]
+		indarr = append(indarr, self.SL[loc].Index)
+		outarr = append(outarr, *rel)
 	}
-	return self.SL[loc].Index, *rel
+	return indarr, outarr
+}
+
+func (self *Obs) Run(in sul.InputSeq) (sul.InputSeq, sul.Output) {
+	seqs, outs := self.SeqRun(in)
+	tail := len(seqs) - 1
+	if tail < 0 {
+		panic("hypothesis cannot be executed with no input")
+	}
+	return seqs[tail], outs[tail]
 }
 
 func (self *Obs) AddSuffix(suf sul.InputSeq) {
 	self.D = append(self.D, suf)
+	logger.Println("[SUFFIX ADD]", suf)
 }
 
 func (self *Obs) GetHypoStr() string {
@@ -146,7 +159,7 @@ func (self *Obs) GetHypoStr() string {
 			rel += self.SL[i].Index.String()
 			rel += "  with edges: \n"
 			for j := 0; j < len(acts); j++ {
-				rel += fmt.Sprintf("[%s]\t -> state %d\n", acts[j].String(), self.SL[i].Dist[j])
[…]

### 2015-12-22 lib/sul/interface.go
bug fixed in equivalence query

@@ -19,6 +19,7 @@ import (
 
 var logger *log.Logger = log.New(os.Stderr, "SUL - ", 2)
 var ibound = 3
+var ebound = 4
 
 func SetLog(w io.Writer) {
 	logger = log.New(w, "SUL", 2)
@@ -38,6 +39,10 @@ func SetReoDelay(t time.Duration) {
 
 func SetBound(b int) {
 	ibound = b
+}
+
+func SetEquivBound(b int) {
+	ebound = b
 }
 
 /********************* Definitions of Input/Output **********************/
@@ -335,7 +340,7 @@ func (self *Oracle) MQuery(in InputSeq) Output {
 		seq = self.SeqSimulate(in)
 		if len(seq) == 0 {
 			// a panic happens
-			logger.Println("[MQUERY] PANIC CATCHED")
+			logger.Println("[MQUERY] PANIC CAUGHT")
 			continue
 		} else {
 			t := seq[len(seq)-1]
@@ -354,10 +359,55 @@ func (self *Oracle) MQuery(in InputSeq) Output {
 
 type Executable interface {
 	Run(InputSeq) (InputSeq, Output)
+	SeqRun(InputSeq) ([]InputSeq, []Output)
 }
 
 func (self Oracle) EQuery(hypo Executable) (InputSeq, bool) {
-	// TODO
+	// FIXME bound is set for iteration depth, but who will tell us its value ?
+	var bound = ebound
+	/*
+		  1. generate a series of all permutation
+		  2. TODO check if these sequences are in the tree
+			   - if true, just ignore them
+				 - if false, use SeqRun to generate it's corresponding hypo-execution
+				   to compare and see if we can find a counter-example
+	*/
+	seqs := []InputSeq{InputSeq{}}
+	acts := self.GetInputs()
+	// FIXME coud we encapsulate this part into a single function? this may lead to better
+	// performance
+	for i := 0; i < bound; i++ {
+		nseqs := []InputSeq{}
+		for j := 0; j < len(seqs); j++ {
+			for k := 0; k < len(acts); k++ {
+				// check if the sequence is existing in the tree
+				curr := InputSeq{}
+				// NOTE still not sure what cause the problem
+				curr = append(curr, seqs[j]...)
+				curr = append(curr, acts[k])
+				nseqs = append(nseqs, curr)
+			}
+		}
+		seqs = nseqs
+	}
+	// existing-check and generation of it's corresponding execution under hypothesis
[…]

### 2015-12-22 lib/reo/reolib.go
.

@@ -54,10 +54,10 @@ func SyncdrainChannel(in1, in2, stop Port) {
 			stop.Main,
 			Operation{"read", in1.Slave, ""},
 			Operation{"read", in2.Slave, ""},
-			Operation{"debug", in1.Slave, "sync first hand-shake finished"},
+			Operation{"debug", in1.Slave, "SYNCDRAIN first hand-shake finished"},
 			Operation{"write", in1.Slave, "read"},
 			Operation{"write", in2.Slave, "read"},
-			Operation{"debug", in1.Slave, "sync second hand-shake finished"},
+			Operation{"debug", in1.Slave, "SYNCDRAIN second hand-shake finished"},
 			Operation{"read", in1.Main, ""},
 			Operation{"read", in2.Main, ""},
 		)
@@ -125,14 +125,14 @@ func MergerChannel(in1, in2, out, stop Port) {
 	var step int = 0
 	// we need some assistant function to deal with step
 	pushData := func(d string) {
-		logger.Println("start pushing data")
+		logger.Println("[MERGER] start pushing data")
 		select {
 		case <-stop.Main:
-			logger.Println("pushdata timeout")
+			logger.Println("[MERGER] pushdata timeout")
 			return
 		case out.Main <- d:
 			step = 0
-			logger.Println("data pushed.", d)
+			logger.Println("[MERGER] data pushed.", d)
 		}
 	}
 
@@ -159,7 +159,7 @@ func MergerChannel(in1, in2, out, stop Port) {
 				lock.Unlock()
 				// otherwise nothing has to be done
 			}
-			logger.Println("first handshake", label, step)
+			logger.Println("[MERGER] first handshake", label, step)
 			// second hand-shake with output port
 			select {
 			case <-stop.Main:
@@ -190,7 +190,7 @@ func MergerChannel(in1, in2, out, stop Port) {
 				lock.Unlock()
 				// otherwise nothing has to be done
 			}
-			logger.Println("second handshake", label, step)
+			logger.Println("[MERGER] second handshake", label, step)
 			// final hand-shake with input port
 			select {
 			case <-stop.Main:
@@ -226,7 +226,7 @@ func MergerChannel(in1, in2, out, stop Port) {
 				}
 				lock.Unlock()
 			}
-			logger.Println("FINAL handshake", label, step)
+			logger.Println("[MERGER] FINAL handshake", label, step)
 		}
 	}
 

### 2015-12-22 sultest.go
.

@@ -7,9 +7,11 @@ package main
 // GetOracle, this way of importing is more easy because
 // we can change the system-under-learn without changing
 // main code but the library we're going to import
-import . "./example/alternator"
 
-// import . "./example/fifo"
+import buf2 "./example/2-buffer"
+import altn "./example/alternator"
+import fifo "./example/fifo"
+
 import "./lib/learn"
 import "./lib/sul"
 import "log"
@@ -28,20 +30,29 @@ func main() {
 	// logs on/off
 	sul.CloseLog()
 	sul.CloseReoLog()
-	learn.CloseLog()
+	// learn.CloseLog()
 	// -------------- CONFIGURATION END --------------------
-	s := GetOracle()
-	logger.Println("MAIN PROC START")
+	var sulname = "buf2"
+	var s *sul.Oracle
+	switch sulname {
+	case "buf2":
+		s = buf2.GetOracle()
+		break
+	case "altn":
+		s = altn.GetOracle()
+		break
+	case "fifo":
+		s = fifo.GetOracle()
+		break
+	}
+	// -------------- ACTIVE LEARNING START --------------------
 	// following are test code for MQuery
 	var debug = false
 	if debug {
 		counter := 0
 		for {
 			var tin sul.InputSeq = sul.InputSeq{
-				&sul.Input{map[string]bool{"A": true, "B": true}, false},
-				&sul.Input{map[string]bool{"A": true, "B": true}, false},
 				&sul.Input{map[string]bool{"A": true, "B": false}, false},
-				&sul.Input{map[string]bool{"A": true, "B": false}, true},
 			}
 			r := s.MQuery(tin)
 			logger.Println("RESULT:", r, counter)

### 2015-12-23 lib/learn/closeness.go
debug

@@ -60,9 +60,18 @@ func (self *Obs) fillTable() {
 
 func (self *Obs) TableClose() {
 	var i, j int
+	var lastnumlines = -1
 	// after close the table, we need to construct a hypothesis
 	defer self.direct_hypothesis()
 	for self.fillTable(); ; self.fillTable() {
+		// NOTE if after a iteration there're no change in obstable
+		// something **must** be wrong
+		if len(self.SL) == lastnumlines {
+			panic("fatal error: lines unchanged during an iteration")
+		} else {
+			lastnumlines = len(self.SL)
+		}
+
 		// check if the table is closed now
 		flag := true
 		for i = self.SpLoc + 1; i < len(self.SL); i++ {

### 2015-12-23 lib/learn/obstable.go

@@ -147,6 +147,9 @@ func (self *Obs) Run(in sul.InputSeq) (sul.InputSeq, sul.Output) {
 func (self *Obs) AddSuffix(suf sul.InputSeq) {
 	self.D = append(self.D, suf)
 	logger.Println("[SUFFIX ADD]", suf)
+	if len(suf) == 0 {
+		panic("fatal error: empty suffixes added")
+	}
 }
 
 func (self *Obs) GetHypoStr() string {
@@ -181,7 +184,10 @@ func (self *Obs) String() string {
 		for j := 0; j < len(self.D); j++ {
 			// fmt.Println(self.SL[i].Result)
 			var nxt = ""
-			if i <= self.SpLoc {
+			// NOTE in one line, there could be more columns than actions
+			// especially when some suffixed are added. so we use j < len(self.SL[i].Dist) to make sure
+			// panics won't happen
+			if i <= self.SpLoc && j < len(self.SL[i].Dist) {
 				nxt = fmt.Sprintf("#%d", self.SL[i].Dist[j])
 			}
 			rel += fmt.Sprintf("%s%s\t", self.SL[i].Result[j].String(), nxt)

### 2015-12-23 sultest.go
.

@@ -25,10 +25,10 @@ func main() {
 	// set up multicores
 	runtime.GOMAXPROCS(4)
 	// configurations in simulation
-	sul.SetReoDelay(5)
-	sul.SetBound(1)
+	sul.SetReoDelay(10)
+	sul.SetBound(2)
 	// logs on/off
-	sul.CloseLog()
+	// sul.CloseLog()
 	sul.CloseReoLog()
 	// learn.CloseLog()
 	// -------------- CONFIGURATION END --------------------
@@ -47,17 +47,21 @@ func main() {
 	}
 	// -------------- ACTIVE LEARNING START --------------------
 	// following are test code for MQuery
-	var debug = false
+	var debug = true
 	if debug {
 		counter := 0
 		for {
 			var tin sul.InputSeq = sul.InputSeq{
+				&sul.Input{map[string]bool{"A": false, "B": false}, false},
+				&sul.Input{map[string]bool{"A": false, "B": true}, false},
+				&sul.Input{map[string]bool{"A": false, "B": false}, false},
 				&sul.Input{map[string]bool{"A": true, "B": false}, false},
 			}
-			r := s.MQuery(tin)
+			r := s.SeqSimulate(tin)
 			logger.Println("RESULT:", r, counter)
 			counter++
-			if r.String() != "C:B," {
+
+			if len(r[3]) == 0 {
 				break
 			}
 		}

### 2015-12-25 lib/reo/reolib.go
timer channel

@@ -5,6 +5,7 @@ import "log"
 import "io"
 import "io/ioutil"
 import "os"
+import "time"
 
 // NOTE when later some more complicated example would be trapped
 // into deadlocks plz kindly check this
@@ -88,6 +89,41 @@ func FifoChannel(in, out, stop Port) {
 			return
 		} else {
 			logger.Println("[FIFO] RELEASED", <-c)
+		}
+	}
+}
+
+func timer(t time.Duration) chan string {
+	r := make(chan string)
+	go func() {
+		// use time.After
+		<-time.After(t)
+		close(r)
+	}()
+	return r
+}
+
+func TimerChannel(in, out Port, t time.Duration, stop Port) {
+	defer close(stop.Slave)
+	c := make(chan string, 1)
+	for {
+		status := StepExec(
+			stop.Main,
+			Operation{"read", in.Slave, ""},
+			Operation{"write", in.Slave, "read"},
+			Operation{"read", in.Main, "datum"},
+			Operation{"write", c, "datum"},
+			Operation{"debug", c, "[FIFO] BUFFERED"},
+			Operation{"read", timer(t), ""},
+			// following are the syncwrite part
+			Operation{"write", out.Slave, "write"},
+			Operation{"read", out.Slave, ""},
+			Operation{"write", out.Main, "datum"},
+		)
+		if !status {
+			return
+		} else {
+			logger.Println("[TIMER] RELEASED", <-c)
 		}
 	}
 }

### 2015-12-25 paper/paper.tex
paper update
.

@@
 % used for flow charts
+\usepackage{pgf}
 \usepackage{tikz}
+\usepackage{reotex}
+
+\usepackage{amssymb}
+\usepackage{cite}
+\usepackage[normalem]{ulem}
 % FIXME finally no todos should exist in this draft
@@
 % positioning is used for below lef = of
-\usetikzlibrary{shapes,arrows, positioning}
+\usetikzlibrary{shapes,arrows,automata,positioning}
+% some tikz-styles on reo channels, not required in papers that have nothing to do with Reo
+
+% declaration of environments
+\newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
 
@@
 
-The application of machine learning in formal models has a long history. There are several main
-orientations: extraction of formal models and learning-guided verification technique.
+To solve this problem, many techniques in model constructing were proposed, for instance in
+\cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.
 
@@
 \label{sec:reo}
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/basic.tex}
+  \end{center}
+  \caption{Basic Reo Channels}
+  \label{fig:basic}
+\end{figure}
 
@@
 \todo{an example as graph}
+
+\subsection{Parameterized Mealy Machine}
+\begin{definition}[Parameterized Mealy Machine]
+  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle S(\Sigma), s_0,
+  \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an alphabet to its corresponding Mealy Machine.
+  \begin{itemize}
+    \item[-] $\Sigma$ is a \emph{finite} input/output alphabet
+    \item[-] $S$ is a function that maps a \emph{finite} alphabet to a \emph{finite} set of
+      states. We use $S(\Sigma)$ to denote the state set.
+    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
+    \item[-] $\delta$ 
+  \end{itemize}
+\end{definition}
+
 \begin{figure}[h]
@@
 no approximation.
+
+Equivalence queries are used to search for counter-examples. But what makes counter-examples even
+existing? In Reo models, we believe that \emph{FIFO} channels and \emph{Timer} channels are to
+blame. Here we present a brief example. To make things eaiser, we have only untimed Reo here.
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/3buf.tex}
+  \end{center}
+  \caption{A Switching Connector $S$ with Three Buffers}
+  \label{fig:buf3}
+\end{figure}
+
+A \emph{Switching} connector in \figurename \ref{fig:buf3} has two source-ends $A,B$ and one
+sink-end $C$. In a nutshell, datum come from $A$ and be stored temporarily in buffers. These datum
+will never flow out until signals come to $B$. With the Mealy-Machine semantics given, the semantics
+of \emph{Switching} connectors can be defined as following \figurename \ref{fig:buf3semantics}.
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/3bufsemantics.tex}
+  \end{center}
+  \caption{\emph{Gate} as Mealy Machine $\mathcal{M}(S)$}
+  \label{fig:buf3semantics}
+\end{figure}
+
+According to the production of Mealy-Machines, 8 different states should be found in
+$\mathcal{M}(S)$. We use $q_{abc}$ to denote them. $q_{001}$ indicates that the last buffer is
+filled and others are empty, and $q_{111}$ means that there are no space in any buffer. It's
+obvious that some states like $q_{100}$ is unreachable.
+
+\begin{definition}[Similar]
+  In a mealy machine, two states are similar iff. they have the same output signature.
+\end{definition}
+
+\begin{theorem}[Bound of Counter-Example]
+  \label{the:cebound} Assume that an observation table has already been closed with maximum
+  query length \todo{find a better phrase?} $l$. An counter-example of length $l+2$ would be
+  found iff. there're possible counter-examples.
+\end{theorem}
+\begin{IEEEproof}
+  Sketch of this proof are shown in several points:
+  \begin{enumerate}
+    \item Hypothesises are subgraphs of the semantics graph.
+    \item Inputs on reverse edges are complementary.
+    \item 
+  \end{enumerate}
+\end{IEEEproof}
+
 \section{Case Studies}

### 2015-12-25 sultest.go
.

@@ -11,6 +11,7 @@ package main
 import buf2 "./example/2-buffer"
 import altn "./example/alternator"
 import fifo "./example/fifo"
+import timer "./example/timer"
 
 import "./lib/learn"
 import "./lib/sul"
@@ -32,7 +33,7 @@ func main() {
 	sul.CloseReoLog()
 	// learn.CloseLog()
 	// -------------- CONFIGURATION END --------------------
-	var sulname = "buf2"
+	var sulname = "time"
 	var s *sul.Oracle
 	switch sulname {
 	case "buf2":
@@ -44,10 +45,12 @@ func main() {
 	case "fifo":
 		s = fifo.GetOracle()
 		break
+	case "time":
+		s = timer.GetOracle()
 	}
 	// -------------- ACTIVE LEARNING START --------------------
 	// following are test code for MQuery
-	var debug = true
+	var debug = false
 	if debug {
 		counter := 0
 		for {

### 2015-12-25 example/timer/oracle.go
new example

@@ -1,0 +1,38 @@
+package timer
+
+import "../../lib/sul"
+import "../../lib/reo"
+import "time"
+
+/*
+	[ARCHITECTURE]
+*/
+
+func GetOracle() *sul.Oracle {
+	o := new(sul.Oracle)
+	o.InPorts = []string{"A", "B"}
+	o.MidPorts = []string{"M0", "M1", "M2", "M3", "M4", "M5"}
+	o.OutPorts = []string{"C"}
+	o.TimeUnit = 40 * time.Millisecond
+	o.GenerateInst = func() *sul.SulInst {
+		r := new(sul.SulInst)
+		// if there're several channels, a better solution is that
+		// we use one stop flag to close all of them
+		// and multiple stop finish flag to make sure that all of them
+		// are closed
+		r.GeneratePort(o)
+		// generating stop ports
+		r.StopPorts = reo.GenerateStopPort(7)
+		r.Start = func() {
+			go reo.BufferChannel(1, r.InPorts["A"], r.MidPorts["M0"], r.StopPorts[0])
+			go reo.BufferChannel(1, r.InPorts["B"], r.MidPorts["M1"], r.StopPorts[1])
+			go reo.OutputChannel(r.MidPorts["M5"], r.OutPorts["C"], r.StopPorts[2])
+			go reo.FifoChannel(r.MidPorts["M0"], r.MidPorts["M2"], r.StopPorts[3])
+			go reo.TimerChannel(r.MidPorts["M2"], r.MidPorts["M3"], 100*time.Millisecond, r.StopPorts[4])
+			go reo.SyncdrainChannel(r.MidPorts["M1"], r.MidPorts["M4"], r.StopPorts[5])
+			go reo.ReplicatorChannel(r.MidPorts["M3"], r.MidPorts["M4"], r.MidPorts["M5"], r.StopPorts[6])
+		}
+		return r
+	}
+	return o
+}

### 2015-12-27 paper/paper.tex
semantics of fifo

@@
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 
-\subsection{Parameterized Mealy Machine}
-\begin{definition}[Parameterized Mealy Machine]
-  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle S(\Sigma), s_0,
-  \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an alphabet to its corresponding Mealy Machine.
-  \begin{itemize}
-    \item[-] $\Sigma$ is a \emph{finite} input/output alphabet
-    \item[-] $S$ is a function that maps a \emph{finite} alphabet to a \emph{finite} set of
-      states. We use $S(\Sigma)$ to denote the state set.
-    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
-    \item[-] $\delta$ 
-  \end{itemize}
-\end{definition}
-
 \begin{figure}[h]
@@
 question deserves careful consideration if we are taking an external view.
+
+\subsection{Parameterized Mealy Machine}
+\begin{definition}[Parameterized Mealy Machine]
+  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
+  S(\Sigma), s_0, I(\Sigma), O(\Sigma), \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
+  alphabet to its corresponding Mealy Machine. 
+  \begin{itemize}
+    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
+    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
+      states. We use $S(\Sigma)$ to denote the state set.
+    \item[-] $I(\Sigma)$ maps an alphabet to a set of input actions.
+    \item[-] $O(\Sigma)$ maps an alphabet to a set of output actions.
+    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
+    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
+      $\delta(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow O(\Sigma)$ to denote the output function.
+    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
+      $\lambda(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow S(\Sigma)$ to denote the transiton
+      function.
+  \end{itemize}
+\end{definition}
+
+Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
+\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
+  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
+  \begin{itemize}
+    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
+    \item[-] $I(\Sigma)=\{(A:d)|d\in\Sigma\cup \{\bot\}\}$
+    \item[-] $O(\Sigma)=\{(B:d)|d\in\Sigma\cup\{\bot\}\}$
+    \item[-] transition function
+      \begin{displaymath}
+        \delta(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d) \\
+          q_d & s=q_{d'}\land i=(A:d) \\
+          q_0 & s=q_d\land i=(A:\bot) \\
+        \end{array}
+        \right.
+      \end{displaymath}
+    \item[-] output function
+      \begin{displaymath}
+        \delta(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d) \\
+          q_d & s=q_{d'}\land i=(A:d) \\
+          q_0 & s=q_d\land i=(A:\bot) \\
+        \end{array}
+        \right.
+      \end{displaymath}
+  \end{itemize}
+\end{example}
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/pmmfifo.tex}
+  \end{center}
+  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
+  \label{fig:pmmfifo}
+\end{figure}
+
+\todo{finish the definition ..}
+\begin{definition}[Production of Parameterized Mealy Machines]
+  Now we're going to define the production of two parameterized mealy Machine
+  \[
+  Prod(PM_1,PM_2)=PM_3
+  \]
+  as follows,
+  \begin{itemize}
+    \item[-] $\forall\Sigma,PM_3.I(\Sigma)=PM_1.I(\Sigma)\cup PM_2.I(\Sigma)$
+    \item
+  \end{itemize}
+\end{definition}
 

### 2015-12-28 paper/paper.tex
.

@@
 \usepackage[normalem]{ulem}
+% for a smile-face character
+\usepackage{wasysym}
 % FIXME finally no todos should exist in this draft
@@
 \newtheorem{example}{Example}
+
+% personal characters
+\newcommand{\rblock}[0]{\circleddash}
+\newcommand{\rread}[0]{\smiley}
+\newcommand{\rnoread}[0]{\frownie}
 
@@
   A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
-  S(\Sigma), s_0, I(\Sigma), O(\Sigma), \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
+  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
   alphabet to its corresponding Mealy Machine. 
@@
       states. We use $S(\Sigma)$ to denote the state set.
-    \item[-] $I(\Sigma)$ maps an alphabet to a set of input actions.
-    \item[-] $O(\Sigma)$ maps an alphabet to a set of output actions.
+    \item[-] $I$ is a finite set of source-ends.
+    \item[-] $O$ is a finite set of sink-ends.
     \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
     \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
-      $\delta(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow O(\Sigma)$ to denote the output function.
+      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
     \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
-      $\lambda(\Sigma):S(\Sigma)\times I(\Sigma)\rightarrow S(\Sigma)$ to denote the transiton
+      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
       function.
@@
 \end{definition}
+
+In the definition above, \emph{Input} and \emph{Output} are used to generate input actions and output actions by the corresponding alphabets and ends.
+\todo{How to say?}
+\[
+Input(\Sigma,I)=\{\}
+\]
+\[
+Output(\Sigma,I)=\{\}
+\]
 
@@
     \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
-    \item[-] $I(\Sigma)=\{(A:d)|d\in\Sigma\cup \{\bot\}\}$
-    \item[-] $O(\Sigma)=\{(B:d)|d\in\Sigma\cup\{\bot\}\}$
-    \item[-] transition function
-      \begin{displaymath}
-        \delta(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
-          q_d & s=q_0\land i=(A:d) \\
-          q_d & s=q_{d'}\land i=(A:d) \\
-          q_0 & s=q_d\land i=(A:\bot) \\
-        \end{array}
-        \right.
-      \end{displaymath}
+    \item[-] $I=\{A\}$
+    \item[-] $O=\{B\}$
+    \item[-] $s_0=q_0$
     \item[-] output function
@@
         \begin{array}[h]{ll}
-          q_d & s=q_0\land i=(A:d) \\
-          q_d & s=q_{d'}\land i=(A:d) \\
-          q_0 & s=q_d\land i=(A:\bot) \\
+          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
+          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
+          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
+          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
+          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
+          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
+        \end{array}
+        \right.
+      \end{displaymath}
+    \item[-] transition function
+      \begin{displaymath}
+        \lambda(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
+          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
+          q_0 & otherwise \\
         \end{array}
@@
 \begin{definition}[Production of Parameterized Mealy Machines]
-  Now we're going to define the production of two parameterized mealy Machine
+  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
   \[
-  Prod(PM_1,PM_2)=PM_3
+  prod(PM_1,PM_2)=PM_3
   \]
@@
   \begin{itemize}
-    \item[-] $\forall\Sigma,PM_3.I(\Sigma)=PM_1.I(\Sigma)\cup PM_2.I(\Sigma)$
-    \item
+  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
+    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O\cup PM_2.O$
+    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_1.I\cup PM_2.I$
+    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
+    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
+      \begin{displaymath}
+        \left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
+          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
+          q_0 & otherwise \\
+        \end{array}
+        \right.
+      \end{displaymath}
+    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=$
+      \begin{displaymath}
+        \left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
+          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
+          q_0 & otherwise \\
+        \end{array}
+        \right.
+      \end{displaymath}
   \end{itemize}
@@
 \section{Case Studies}
+\subsection{Alternator}
+\subsection{Timed TODO}
 

### 2015-12-29 paper/paper.tex
.

@@
 
-So far as we can tell, most works\cite{DBLP:conf/fase/RaffeltS06} on automata learning are not
+So far as we can tell, most
+works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
 capable of infinite models. \todo{reason?} Considering the semantics defined in section
@@
   \]
-  as follows, 
+  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
   \begin{itemize}
   	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
-    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O\cup PM_2.O$
-    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_1.I\cup PM_2.I$
+    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
+    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
     \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
@@
         \begin{array}[h]{ll}
-          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
-          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
-          q_0 & otherwise \\
+          (Out_1 + Out_2)|_{PM_3.O} & \rblock\land Out_2\neq\rblock \\
+          \rblock & otherwise \\
         \end{array}
@@
       \end{displaymath}
-    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=$
-      \begin{displaymath}
-        \left\{
-        \begin{array}[h]{ll}
-          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
-          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
-          q_0 & otherwise \\
-        \end{array}
-        \right.
-      \end{displaymath}
+      where we have
+      \begin{itemize}
+        \item[*] $In_1 = i|_{PM_1.I}$
+        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
+        \item[*] $In_2 = (Out_1 + i)|_{PM_2.I}$
+        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
+      \end{itemize}
+    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
+      where we have
+      \begin{itemize}
+        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
+        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
+      \end{itemize}
   \end{itemize}

### 2015-12-29 paper/paper.tex
.

@@
 
-Reo Coordination Model, obviously, is not a \emph{proper model} for learning.
-
+\subsection{External Behavior of Reo Connectors}
 So far as we can tell, most
@@
 
+\subsection{Time Axis}
+Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.\todo{citations}
+Generally, these models are designed to handle real-time behavior where time is defined in
+$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
+easier\todo{citations}.
+
 \subsection{Parameterized Mealy Machine}
+We present a model named \emph{parameterized mealy machine} to represent timed connectors. This
+model is supposed to behave as a middle representation. Connectors are defined as parameterized
+mealy machines, and composed via its production operator. Then original mealy-machine model will be
+taken as semantics of PMM model.
+
 \begin{definition}[Parameterized Mealy Machine]
@@
 \[
-Input(\Sigma,I)=\{\}
+Input(\Sigma,I)=\{\}\cup\{T\}
 \]
+where we use $T$ to denote the time action.
 \[
@@
 
-\todo{finish the definition ..}
 \begin{definition}[Production of Parameterized Mealy Machines]
@@
 \section{From Blackbox to Timed Connectors}
+\subsection{Adapted L* Algorithm}
 \subsection{Equivalence Query}
@@
 
-\begin{definition}[Similar]
-  In a mealy machine, two states are similar iff. they have the same output signature.
-\end{definition}
+We say if two states are \emph{similiar} iff. they have the same output signature.
 

### 2016-01-06 paper/paper.tex
.

@@
 \label{sec:reo}
+Reo Coordination Language\cite{DBLP:journals/mscs/Arbab04}
 
@@
 
-\subsection{Time Axis}
-Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.\todo{citations}
+\subsection{Time Domain}
+Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.
 Generally, these models are designed to handle real-time behavior where time is defined in
@@
 
+In this paper, we choose the rational number field $\mathbb{Q}$ as our time domain, which simplifies
+discretization of timed behaviors greatly.
+
+As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with the
+\emph{t-timer} channels, and the number of these channels are apparently finite. We use
+$t_i\in\mathbb{Q}$ to denote the delays of these timer channels, and now we can define a precision
+function $prec$.
+\[
+prec(t_1,\cdots,t_n) = \max_T\{\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
+\]
+It's easy to prove that such a $T$ is always existing.
+
+In real systems, the concept \emph{time precision} is widely used with the name ``clock-period''.
+Most of the time, we know the clock-cycle of some hardware components, even without any idea of its
+structure. With such precision $T$ given, it's reasonable to assume that all $t$-timers are actually
+$nT$-timers. In following sections, we'll use $n$-timers instead.
+
+Besides, we're going to add a single ``T'' action in mealy machines. It indicates that a transition
+will take a time unit to finish, and all outputs would come out after that.
+
 \subsection{Parameterized Mealy Machine}
-We present a model named \emph{parameterized mealy machine} to represent timed connectors. This
+We present a model named \emph{parameterized mealy machine} to represent timed connectors
+(hereinafter referred to as PMM). This
 model is supposed to behave as a middle representation. Connectors are defined as parameterized
@@
   \begin{itemize}
-    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
+    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereinafter referred to as an alphabet)
     \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
@@
 
+\todo{example of production, maybe fifo+timer}
+
 \section{From Blackbox to Timed Connectors}

### 2016-01-08 paper/paper.tex
.

@@
 
-Besides, we're going to add a single ``T'' action in mealy machines. It indicates that a transition
+Besides, we're going to add a ``T'' action in mealy machines. It indicates that a transition
 will take a time unit to finish, and all outputs would come out after that.
@@
 We present a model named \emph{parameterized mealy machine} to represent timed connectors
-(hereinafter referred to as PMM). This
-model is supposed to behave as a middle representation. Connectors are defined as parameterized
+(hereinafter referred to as PMM).
+
+This model is supposed to behave as a middle representation. Connectors are defined as parameterized
 mealy machines, and composed via its production operator. Then original mealy-machine model will be
@@
 \section{From Blackbox to Timed Connectors}
-\subsection{Adapted L* Algorithm}
-\subsection{Equivalence Query}
+
+\subsection{Observation Table}
+
+\subsection{Closeness}
+
+\subsection{Perfomance Optimization}
+
+\subsection{Counter-Examples}
 Generally, equivalence query has been proved impossible in blackbox

### 2016-01-08 example/expfifo/oracle.go
new example: expiring fifo1

@@ -1,0 +1,38 @@
+package alternator
+
+import "../../lib/sul"
+import "../../lib/reo"
+import "time"
+
+/*
+	[ARCHITECTURE]
+*/
+
+func GetOracle() *sul.Oracle {
+	o := new(sul.Oracle)
+	o.InPorts = []string{"A", "B"}
+	o.MidPorts = []string{"M0", "M1", "M2", "M3", "M4", "M5"}
+	o.OutPorts = []string{"C"}
+	o.TimeUnit = 40 * time.Millisecond
+	o.GenerateInst = func() *sul.SulInst {
+		r := new(sul.SulInst)
+		// if there're several channels, a better solution is that
+		// we use one stop flag to close all of them
+		// and multiple stop finish flag to make sure that all of them
+		// are closed
+		r.GeneratePort(o)
+		// generating stop ports
+		r.StopPorts = reo.GenerateStopPort(7)
+		r.Start = func() {
+			go reo.BufferChannel(1, r.InPorts["A"], r.MidPorts["M0"], r.StopPorts[0])
+			go reo.BufferChannel(1, r.InPorts["B"], r.MidPorts["M1"], r.StopPorts[1])
+			go reo.OutputChannel(r.MidPorts["M5"], r.OutPorts["C"], r.StopPorts[2])
+			go reo.FifoChannel(r.MidPorts["M0"], r.MidPorts["M2"], r.StopPorts[3])
+			go reo.FifoChannel(r.MidPorts["M2"], r.MidPorts["M3"], r.StopPorts[4])
+			go reo.SyncdrainChannel(r.MidPorts["M1"], r.MidPorts["M4"], r.StopPorts[5])
+			go reo.ReplicatorChannel(r.MidPorts["M3"], r.MidPorts["M4"], r.MidPorts["M5"], r.StopPorts[6])
+		}
+		return r
+	}
+	return o
+}

### 2016-01-08 lib/sul/interface.go
redundance in SeqSimulate

@@ -141,6 +141,19 @@ func (self *Output) EqualTo(o *Output) bool {
 	return true
 }
 
+func (self OutputSeq) EqualTo(o OutputSeq) bool {
+	if len(self) != len(o) {
+		return false
+	} else {
+		for i := 0; i < len(o); i++ {
+			if !self[i].EqualTo(&o[i]) {
+				return false
+			}
+		}
+	}
+	return true
+}
+
 /********************* Definition of SulInst ******************/
 
 // Instance of System Under Test
@@ -244,7 +257,8 @@ func (self *Oracle) GetInputIndex(item Input) int {
 	panic("there's an undefined action " + item.String())
 }
 
-func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
+// NOTE this function is used to process directly simultion on suls
+func (self *Oracle) SeqSimulateIteration(ins InputSeq) OutputSeq {
 	inst := self.GenerateInst()
 	inst.OutBufs = map[string]chan string{}
 	// initialization of buffers
@@ -303,6 +317,33 @@ func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
 	return out
 }
 
+func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
+	var ct = 0
+	var count = 0
+	var seq OutputSeq
+	var rec OutputSeq = OutputSeq{}
+
+	for ct <= ibound {
+		count++
+		reo.GetLogger().Println("[SEQSIMULATE] ITERATE", count, "---------------------------------------")
+		seq = self.SeqSimulateIteration(ins)
+		if len(seq) == 0 {
+			// a panic happens
+			logger.Println("[SEQSIMULATE] PANIC CAUGHT")
+			continue
+		} else {
+			if ct > 0 && seq.EqualTo(rec) {
+				ct++
+			} else {
+				// ct = 0 : the first iteration || not equal : means there's an error
+				ct = 1
+				rec = seq
+			}
+		}
+	}
+	return seq
+}
+
 var mqcounter int = 0
 var rdcounter int = 0
 
@@ -330,31 +371,10 @@ func (self *Oracle) MQuery(in InputSeq) Output {
 	}
 	logger.Println("[MQUERY]", in.String(), "COUNTER: ", mqcounter)
 	mqcounter++
-	var rec Output
-	var ct = 0
-	var count = 0
-	var seq OutputSeq
-	for ct <= ibound {
-		count++
[…]

### 2016-01-08 example/expfifo/oracle.go
new example expiring fifo1

@@ -1,18 +1,14 @@
-package alternator
+package expfifo
 
 import "../../lib/sul"
 import "../../lib/reo"
 import "time"
 
-/*
-	[ARCHITECTURE]
-*/
-
 func GetOracle() *sul.Oracle {
 	o := new(sul.Oracle)
-	o.InPorts = []string{"A", "B"}
+	o.InPorts = []string{"A"}
 	o.MidPorts = []string{"M0", "M1", "M2", "M3", "M4", "M5"}
-	o.OutPorts = []string{"C"}
+	o.OutPorts = []string{"B"}
 	o.TimeUnit = 40 * time.Millisecond
 	o.GenerateInst = func() *sul.SulInst {
 		r := new(sul.SulInst)

### 2016-01-09 lib/learn/obstable.go
time-cost recoder added

@@ -7,6 +7,7 @@ import "log"
 import "os"
 import "io"
 import "io/ioutil"
+import "time"
 
 /*
 	Created By Li Yi @ Nov 17
@@ -121,9 +122,21 @@ func (self *Obs) expandLp() {
 	self.SL = append(self.SL, newLp...)
 }
 
+/********************************* PERFORMANCE ANALYSIS ******************************************/
+// time-cost analysis
+var hyporuntime float64 = 0
+
+func RunTime() float64 {
+	return hyporuntime
+}
+
+/*************************************************************************************************/
+
 func (self *Obs) SeqRun(in sul.InputSeq) ([]sul.InputSeq, []sul.Output) {
 	var loc = 0
 	var rel *sul.Output
+	starttime := time.Now()
+
 	indarr, outarr := []sul.InputSeq{}, []sul.Output{}
 	for i := 0; i < len(in); i++ {
 		inputindex := self.orac.GetInputIndex(*in[i])
@@ -132,6 +145,8 @@ func (self *Obs) SeqRun(in sul.InputSeq) ([]sul.InputSeq, []sul.Output) {
 		indarr = append(indarr, self.SL[loc].Index)
 		outarr = append(outarr, *rel)
 	}
+
+	hyporuntime += time.Now().Sub(starttime).Seconds()
 	return indarr, outarr
 }
 

### 2016-01-09 lib/sul/interface.go
.

@@ -257,6 +257,36 @@ func (self *Oracle) GetInputIndex(item Input) int {
 	panic("there's an undefined action " + item.String())
 }
 
+/********************************* PERFORMANCE ANALYSIS ******************************************/
+// counter of membership query
+var mqcounter int = 0
+var rdcounter int = 0
+
+func CounterReset() {
+	mqcounter = 0
+	rdcounter = 0
+}
+
+func Counter() (int, int) {
+	return mqcounter, rdcounter
+}
+
+// time-cost analysis
+var mquerytime float64 = 0
+
+func MembershipTime() float64 {
+	return mquerytime
+}
+
+// tree-optimization switch
+var treeopt = true
+
+func ToggleTreeOptimization() {
+	treeopt = !treeopt
+}
+
+/************************************************************************************************/
+
 // NOTE this function is used to process directly simultion on suls
 func (self *Oracle) SeqSimulateIteration(ins InputSeq) OutputSeq {
 	inst := self.GenerateInst()
@@ -322,6 +352,7 @@ func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
 	var count = 0
 	var seq OutputSeq
 	var rec OutputSeq = OutputSeq{}
+	starttime := time.Now()
 
 	for ct <= ibound {
 		count++
@@ -341,19 +372,9 @@ func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
 			}
 		}
 	}
+
+	mquerytime += time.Now().Sub(starttime).Seconds()
 	return seq
-}
-
-var mqcounter int = 0
-var rdcounter int = 0
-
-func CounterReset() {
-	mqcounter = 0
-	rdcounter = 0
-}
-
-func Counter() (int, int) {
-	return mqcounter, rdcounter
 }
 
 func (self *Oracle) MQuery(in InputSeq) Output {
@@ -369,11 +390,14 @@ func (self *Oracle) MQuery(in InputSeq) Output {
 			return *r
 		}
 	}
+
 	logger.Println("[MQUERY]", in.String(), "COUNTER: ", mqcounter)
 	mqcounter++
 
 	seq := self.SeqSimulate(in)
-	self.Cache.insert(in, seq)
+	if treeopt {
+		self.Cache.insert(in, seq)
+	}
 	return seq[len(seq)-1]
 }
 

### 2016-01-09 paper/paper.tex
.

@@
 
+\todo{modify this image}
 \begin{figure}[h]
@@
 \subsection{Perfomance Optimization}
+In the learning algorithm, the most time-consuming operations are membership queries and
+equivanlence queries.
+
+\todo{analysis table}
 
@@
 
-\section{Case Studies}
-\subsection{Alternator}
-\subsection{Timed TODO}
+\section{Experiments}
+Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in Golang.
+\todo{cite}
+Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
+known for its elegant design and impressive efficiency. Moreover, the concurrency model of Golang
+comes from CSP\cite{DBLP:books/ph/Hoare85}. As a channel-based model, CSP shares a similar idea with
+Reo and makes our implementation much more natural.
+
+We have programmed Reo channels as a new package in Golang. The package is well-written for not only
+formal verification but also practical use.
+
+All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
+of RAM and a Core i7-3630 CPU.
+
+\subsection{Case Studies}
+\subsection{Performance Optimization}
+As a well-known learning algorithm, L* has proved its efficiency in models without time.
+However, when dealing with timed connectors, the algorithm failed to meet our expectation.
+
+\begin{table}[h]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Time-Cost Analysis}
+  \label{tabel:timecost}
+  \centering
+  \begin{tabular}{l||rrr}
+    \hline
+    & FIFO & Alternator & Gate \\
+    \hline\hline
+    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
+    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
+    Total Time(s) & 41.715 & 165.114 & 247.098\\
+    Membership Query(\%) & 99.6 & 76.6 & 68.5\\
+    \hline
+  \end{tabular}
+\end{table}
+
+As shown in Table \ref{tabel:timecost}, time comsumption mainly comes from membership queries.
+Since time is involved in our model, it's inevitably that simulation takes time to behave normally.
+Even worse, since our models are treated as blackbox, there's little room for optimization. The only
+way to reduce time cost is trying not to call the simulation process. Basic ideas are listed as
+follows:
+
+\begin{itemize}
+  \item When constructing \emph{Obs} tables, there are lots of redundant calls to membership
+    queries. For example, a sequence with prefix 'aa' and suffix 'b' is exactly same as another one
+    with prefix 'a' and suffix 'ab'.
+  \item Simulation on mealy machines can provide multi-step output. Consequently, if we has
+    simulated an 'abc' sequence, there's no reason to perform simulation on an 'ab' sequence.
+\end{itemize}
+
+To reduce these repeated simulation, we use a cache to save all simulation results. 
+\begin{table}[h]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Reduction of Membership Queries}
+  \label{tabel:cacheoptimization}
+  \centering
+  \begin{tabular}{l||rrr}
+    \hline
+    & FIFO & Alternator & Gate \\
+    \hline\hline
+    Before & 41.571 & 126.468 & 169.161 \\
+    After & 41.571 & 126.468 & 169.161 \\
+    \hline
+  \end{tabular}
+\end{table}
 

### 2016-01-09 sultest.go

@@ -29,11 +29,12 @@ func main() {
 	sul.SetReoDelay(10)
 	sul.SetBound(2)
 	// logs on/off
-	// sul.CloseLog()
+	sul.CloseLog()
 	sul.CloseReoLog()
 	// learn.CloseLog()
+	// sul.ToggleTreeOptimization()
 	// -------------- CONFIGURATION END --------------------
-	var sulname = "time"
+	var sulname = "fifo"
 	var s *sul.Oracle
 	switch sulname {
 	case "buf2":
@@ -73,4 +74,6 @@ func main() {
 	obs := learn.LStar(s)
 	logger.Println(obs.GetHypoStr())
 	logger.Println(sul.Counter())
+	logger.Println("Time Cost in [SeqSimulate]:", sul.MembershipTime())
+	logger.Println("Time Cost in [SeqRun]:", learn.RunTime())
 }

### 2016-01-09 lib/sul/interface.go
new tree optimization tactic

@@ -348,6 +348,22 @@ func (self *Oracle) SeqSimulateIteration(ins InputSeq) OutputSeq {
 }
 
 func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
+	// we use cache technique to improve the effiency of MQuery,
+	// otherwise this would make it really slow
+	if self.Cache == nil {
+		self.Cache = makenode()
+	} else {
+		r, ok := self.Cache.search(ins)
+		if ok {
+			rdcounter++
+			logger.Println("[SEQSIMULATE]", ins.String(), "REDUCE: ", rdcounter)
+			return r
+		}
+	}
+
+	logger.Println("[SEQSIMULATE]", ins.String(), "COUNTER: ", mqcounter)
+	mqcounter++
+
 	var ct = 0
 	var count = 0
 	var seq OutputSeq
@@ -373,31 +389,17 @@ func (self *Oracle) SeqSimulate(ins InputSeq) OutputSeq {
 		}
 	}
 
+	// save simulation result to cache
+	if treeopt {
+		self.Cache.insert(ins, seq)
+	}
+
 	mquerytime += time.Now().Sub(starttime).Seconds()
 	return seq
 }
 
 func (self *Oracle) MQuery(in InputSeq) Output {
-	// we use cache technique to improve the effiency of MQuery,
-	// otherwise this would make it really slow
-	if self.Cache == nil {
-		self.Cache = makenode()
-	} else {
-		r := self.Cache.search(in)
-		if r != nil {
-			rdcounter++
-			logger.Println("[MQUERY]", in.String(), "REDUCE: ", rdcounter)
-			return *r
-		}
-	}
-
-	logger.Println("[MQUERY]", in.String(), "COUNTER: ", mqcounter)
-	mqcounter++
-
 	seq := self.SeqSimulate(in)
-	if treeopt {
-		self.Cache.insert(in, seq)
-	}
 	return seq[len(seq)-1]
 }
 
@@ -436,7 +438,8 @@ func (self Oracle) EQuery(hypo Executable) (InputSeq, bool) {
 	}
 	// existing-check and generation of it's corresponding execution under hypothesis
 	for i := 0; i < len(seqs); i++ {
-		if self.Cache.search(seqs[i]) == nil {
+		_, ok := self.Cache.search(seqs[i])
+		if !ok {
 			_, hypout := hypo.SeqRun(seqs[i])
[…]

### 2016-01-09 lib/sul/tree.go

@@ -25,16 +25,18 @@ func (self *tnode) insert(iseq InputSeq, oseq OutputSeq) {
 	}
 }
 
-func (self *tnode) search(iseq InputSeq) *Output {
+func (self *tnode) search(iseq InputSeq) (OutputSeq, bool) {
 	p := self
+	rel := OutputSeq{}
 	for i := 0; i < len(iseq); i++ {
 		index := iseq[i].String()
 		next, ok := p.child[index]
 		if !ok {
-			return nil
+			return rel, false
 		} else {
 			p = next
+			rel = append(rel, p.result)
 		}
 	}
-	return &p.result
+	return rel, true
 }

### 2016-01-09 paper/paper.tex
.

@@
 \usepackage{reotex}
+
+% package url is used when citing a website
+\usepackage{url}
 
@@
 \subsection{Time Domain}
-Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.
+Time is involved in several extension version of Reo. For example, Timed
+Reo\cite{DBLP:conf/sefm/ArbabBBR04}, Hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
 Generally, these models are designed to handle real-time behavior where time is defined in
 $\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
-easier\todo{citations}.
+easier.
 
@@
 \begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
-  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
+  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows.
   \begin{itemize}
@@
 
-\todo{modify this image}
+Besides, the concrete mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo}.
 \begin{figure}[h]
@@
   \end{center}
-  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
+  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a\}$}
   \label{fig:pmmfifo}
 \end{figure}
+
+Similarly, we can use parameterized mealy machines to define the semantics of other basic timed Reo
+channels. Now we're going to show how to compose these channels into complicated connectors.
 
@@
 \subsection{Closeness}
-
-\subsection{Perfomance Optimization}
-In the learning algorithm, the most time-consuming operations are membership queries and
-equivanlence queries.
-
-\todo{analysis table}
 
@@
 \section{Experiments}
-Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in Golang.
-\todo{cite}
+Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
+Golang\cite{golang}.
+
 Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
@@
     \hline\hline
-    Before & 41.571 & 126.468 & 169.161 \\
-    After & 41.571 & 126.468 & 169.161 \\
+    Before & 41.571 &  & 1034 \\
+    After & 41.571 &  & 707 \\
+    Reduction Rate & & & 31.6\% \\
     \hline

### 2016-01-09 sultest.go

@@ -34,7 +34,7 @@ func main() {
 	// learn.CloseLog()
 	// sul.ToggleTreeOptimization()
 	// -------------- CONFIGURATION END --------------------
-	var sulname = "fifo"
+	var sulname = "buf2"
 	var s *sul.Oracle
 	switch sulname {
 	case "buf2":

### 2016-01-09 paper/paper.tex
.

@@
 \begin{abstract}
-  Coordination is becoming more and more important, especially in concurrent programming and
-  distributed systems. More and more tools are built to verify coordination models while most of
-  them are facing the same problem: \emph{lack of models}. In many cases, somehow we need to check a
-  connector with nothing more than a binary file. In this paper, we present a learning-based
-  framework to formally verify a Reo connector in case there is no source code. From some practical
-  cases, we've shown the effciency of our approach. Both the algorithm and Reo itself have been
-  ported to \emph{Golang}, making it fully-prepared for parallel programming.
+  % reo coordination models
+  Coordination languages provide a mean to formally specify the communication and
+  reaction between different components. Such models play key roles in concurrent programming and
+  large-scale distributed systems.
+  % algorithms
+  In this paper, an active learning framework is proposed to extract timed connectors from black-box
+  systems.
+  First of all, we introduce parameterized mealy machine as an operational semantics for
+  channel-based coordination language Reo.
+  Parameterized mealy machine serves as a bridge between Reo connectors and mealy machines. With
+  production operator, complex connectors can be composed by basic channels and transformed into
+  mealy machines. 
+  Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in form of mealy
+  machines). The new algorithm has shown its efficiency in multiple cases.
+  % implementation
+  Implementations of this framework is provided as a package in \texttt{Golang}.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  active learning, coordination, formal method.
+  Active Learning, Coordination Languages, Formal Methods
 \end{IEEEkeywords}
@@
 \begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
+  \label{example:pmmfifo}
   The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows.
@@
 
-As shown in Table \ref{tabel:timecost}, time comsumption mainly comes from membership queries.
+As shown in Table \ref{tabel:timecost}, time consumption mainly comes from membership queries.
 Since time is involved in our model, it's inevitably that simulation takes time to behave normally.
-Even worse, since our models are treated as blackbox, there's little room for optimization. The only
-way to reduce time cost is trying not to call the simulation process. Basic ideas are listed as
-follows:
+Even worse, since our models are treated as blackbox. With no access to inner behaviour of the
+connectors, it's almost impossible to accelerate the simulation process.
+
+Fortunately, there are still other optimization solutions. After reviewing our algorithm, we found
+that simulations on similar sequences were invoked frequently:
 
@@
 
-To reduce these repeated simulation, we use a cache to save all simulation results. 
+If previous simulation results are stored in a well-maintained cache, the time-cost in
+simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
+these results. A brief example of such trees can be found in Example \ref{example:tree}.
+
+\begin{example}[Multiway-Tree Cache]
+  \label{example:tree}
+  Considering the FIFO channel presented in Example \ref{example:pmmfifo}. 
+  \todo{draw a graph for multiway-tree cache}
+\end{example}
+
 \begin{table}[h]
@@
     \hline\hline
-    Before & 41.571 &  & 1034 \\
-    After & 41.571 &  & 707 \\
-    Reduction Rate & & & 31.6\% \\
+    Before & 93 & 880 & 1034 \\
+    After & 90 & 725 & 707 \\
+    Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
     \hline

### 2016-01-09 sultest.go

@@ -34,7 +34,7 @@ func main() {
 	// learn.CloseLog()
 	// sul.ToggleTreeOptimization()
 	// -------------- CONFIGURATION END --------------------
-	var sulname = "buf2"
+	var sulname = "altn"
 	var s *sul.Oracle
 	switch sulname {
 	case "buf2":

### 2016-01-10 paper/paper.tex
new example

@@
 \usepackage{tikz}
+\usepackage{tikz-qtree}
 \usepackage{reotex}
@@
 
-\title{Active Learning : From Blackbox To Timed Connectors}
+\title{Active Learning from Blackbox to Timed Connectors}
 \author{
@@
 \IEEEauthorblockA{
-  \IEEEauthorrefmark{1}DI, School of Mathematical Sciences, Peking University,
+\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
 Beijing, China\\
@@
 \begin{abstract}
-  % reo coordination models
-  Coordination languages provide a mean to formally specify the communication and
-  reaction between different components. Such models play key roles in concurrent programming and
-  large-scale distributed systems.
-  % algorithms
-  In this paper, an active learning framework is proposed to extract timed connectors from black-box
-  systems.
-  First of all, we introduce parameterized mealy machine as an operational semantics for
-  channel-based coordination language Reo.
-  Parameterized mealy machine serves as a bridge between Reo connectors and mealy machines. With
-  production operator, complex connectors can be composed by basic channels and transformed into
-  mealy machines. 
-  Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in form of mealy
-  machines). The new algorithm has shown its efficiency in multiple cases.
-  % implementation
+  Coordination models and languages play a key role in formally specifying the communication and
+  interaction among different components in large-scale distributed and concurrent systems. In this
+  paper, we propose an active learning framework to extract timed connector models from black-box
+  system implementation. 
+  We first introduce parameterized mealy machine as an operational semantic
+  model for channel-based coordination language Reo. Parameterized mealy machine serves as a bridge
+  between Reo connectors and mealy machines. With the product operator, complex connectors can be
+  constructed by joining basic channels and transformed into mealy machines. Moreover, we adapt L*,
+  a well-known learning algorithm, to timed connectors (in the form of mealy machines). The new
+  algorithm has shown its efficiency in multiple case studies. 
   Implementations of this framework is provided as a package in \texttt{Golang}.
@@
   \label{fig:basic}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/reoextend.tex}
+  \end{center}
+  \caption{Merger and Replicator}
+  \label{fig:reoextend}
 \end{figure}
@@
 simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
-these results. A brief example of such trees can be found in Example \ref{example:tree}.
+these results. A brief example of such trees can be found in Figure \ref{fig:multiway}.
 
+\todo{the graph need further details}
 \begin{example}[Multiway-Tree Cache]
@@
   Considering the FIFO channel presented in Example \ref{example:pmmfifo}. 
-  \todo{draw a graph for multiway-tree cache}
+  \begin{figure}[h]
+    \begin{center}
+      \input{./images/cache.tex}
+    \end{center}
+    \caption{Multiway-Tree Cache}
+    \label{fig:multiway}
+  \end{figure}
+  Note that in this figure, only the edge information is stored. States like $q_0,q_a$ are written
+  here only to make it clear.
 \end{example}
@@
     \hline\hline
-    Before & 93 & 880 & 1034 \\
-    After & 90 & 725 & 707 \\
+    Original Algorithm & 93 & 880 & 1034 \\
+    Cached Algorithm & 90 & 725 & 707 \\
     Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
@@
 \end{table}
+
+With cache applied, we have made a good reduction on the calls of membership queries. The results
+can be found in Table \ref{tabel:cacheoptimization}.
 

### 2016-01-10 example/expfifo/oracle.go

@@ -3,11 +3,17 @@ package expfifo
 import "../../lib/sul"
 import "../../lib/reo"
 import "time"
+import "strconv"
 
 func GetOracle() *sul.Oracle {
 	o := new(sul.Oracle)
 	o.InPorts = []string{"A"}
-	o.MidPorts = []string{"M0", "M1", "M2", "M3", "M4", "M5"}
+	// dynamically generate the MidPorts
+	o.MidPorts = []string{}
+	for i := 0; i < 14; i++ {
+		o.MidPorts = append(o.MidPorts, "M"+strconv.Itoa(i))
+	}
+
 	o.OutPorts = []string{"B"}
 	o.TimeUnit = 40 * time.Millisecond
 	o.GenerateInst = func() *sul.SulInst {
@@ -20,13 +26,21 @@ func GetOracle() *sul.Oracle {
 		// generating stop ports
 		r.StopPorts = reo.GenerateStopPort(7)
 		r.Start = func() {
+			// Input & Output
 			go reo.BufferChannel(1, r.InPorts["A"], r.MidPorts["M0"], r.StopPorts[0])
-			go reo.BufferChannel(1, r.InPorts["B"], r.MidPorts["M1"], r.StopPorts[1])
-			go reo.OutputChannel(r.MidPorts["M5"], r.OutPorts["C"], r.StopPorts[2])
-			go reo.FifoChannel(r.MidPorts["M0"], r.MidPorts["M2"], r.StopPorts[3])
-			go reo.FifoChannel(r.MidPorts["M2"], r.MidPorts["M3"], r.StopPorts[4])
-			go reo.SyncdrainChannel(r.MidPorts["M1"], r.MidPorts["M4"], r.StopPorts[5])
-			go reo.ReplicatorChannel(r.MidPorts["M3"], r.MidPorts["M4"], r.MidPorts["M5"], r.StopPorts[6])
+			go reo.OutputChannel(r.MidPorts["M12"], r.OutPorts["B"], r.StopPorts[1])
+			// Function Channels
+			go reo.SyncChannel(r.MidPorts["M0"], r.MidPorts["M1"], r.StopPorts[2])
+			go reo.ReplicatorChannel(r.MidPorts["M1"], r.MidPorts["M2"], r.MidPorts["M3"], r.StopPorts[3])
[…]

### 2016-01-10 sultest.go

@@ -12,6 +12,7 @@ import buf2 "./example/2-buffer"
 import altn "./example/alternator"
 import fifo "./example/fifo"
 import timer "./example/timer"
+import expfifo "./example/expfifo"
 
 import "./lib/learn"
 import "./lib/sul"
@@ -29,12 +30,12 @@ func main() {
 	sul.SetReoDelay(10)
 	sul.SetBound(2)
 	// logs on/off
-	sul.CloseLog()
+	// sul.CloseLog()
 	sul.CloseReoLog()
 	// learn.CloseLog()
 	// sul.ToggleTreeOptimization()
 	// -------------- CONFIGURATION END --------------------
-	var sulname = "altn"
+	var sulname = "expfifo"
 	var s *sul.Oracle
 	switch sulname {
 	case "buf2":
@@ -48,6 +49,8 @@ func main() {
 		break
 	case "time":
 		s = timer.GetOracle()
+	case "expfifo":
+		s = expfifo.GetOracle()
 	}
 	// -------------- ACTIVE LEARNING START --------------------
 	// following are test code for MQuery
@@ -71,6 +74,7 @@ func main() {
 		}
 		return
 	}
+
 	obs := learn.LStar(s)
 	logger.Println(obs.GetHypoStr())
 	logger.Println(sul.Counter())

### 2016-01-10 paper/paper.tex
.

@@
 \usepackage{wasysym}
-% FIXME finally no todos should exist in this draft
-\usepackage[textsize=tiny]{todonotes}
+% listing for codes
+\usepackage{listings}
+
 % positioning is used for below lef = of
@@
 
+% FIXME finally no todos should exist in this draft
+\usepackage[textsize=tiny]{todonotes}
+
+% -------------------------------------- configurations -----------------------------------------
 % declaration of environments
@@
 
+% --------------------------------------- information -------------------------------------------
 \title{Active Learning from Blackbox to Timed Connectors}
@@
 \label{sec:reo}
-Reo Coordination Language\cite{DBLP:journals/mscs/Arbab04}
+Reo is a channel based exogenous coordination language proposed by F. Arbab. in
+\cite{DBLP:journals/mscs/Arbab04}. A Reo model, also called \emph{connector}, provides the protocol
+that formalizes the communication, synchronization and cooperation among the components which
+communicate through the connector. Connectors can be defined with no knowledge of the components,
+which makes Reo a powerful ``glue language'' in component-based
+development\cite{DBLP:journals/sigsoft/Gill03}.
+
+In Reo, complex connectors are made up of simpler ones, where the atomic connectors are called
+\emph{channels}. Each channel has two \emph{channel ends}. There are two type of channel ends:
+\emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
+channels ends release them out of the channel. Channels are attached on component instances
+or \emph{nodes}.
+
+The behavior of some channels are informally described as follows. (Graphical representations
+can be found in Figure \ref{fig:basic}).
+
+\begin{itemize}
+  \item [-] A \emph{Sync} channel accepts a data item from its source end iff. the data item can be
+    dispensed to its sink end simultaneously.
+  \item [-] A \emph{LossySync} channel is always prepared to accept data items. These items will be
+    send to its sink end simutaneously if possible, otherwise they will be dropped.
+  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
+    item through one of its source end iff. a data item is also available for it to simultaneously
+    accept through the other end. Then both two data items will be lost.
+  \item [-] 
+\end{itemize}
 
@@
 
+\todo{do we need to remove this graph?}
 \begin{figure}[h]
@@
 
-\subsection{Active Learning and Mealy Machines}
+\subsection{Mealy Machines}
+
+As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
+in \cite{George1955A}. Compared with other variants, Mealy machines are designed to model
+reactive systems, where outputs are determined not only by its current state but also the current
+inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means that all
+possible inputs should be acceptable in all states. In other words, if an input is invalid for some
+state, we need to manually use an additional state to describe such exceptions.
+
+As far as we can see, various forms of Mealy machines are defined in different works. In this paper,
+we give the formal definition of Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.
+
+\todo{why we choose this version}
+
+\begin{definition}[Mealy machine]
+  A Mealy machine is a 6-tuple $(S, s_0, I, O, T, G)$ consisting of the following:
+  \begin{itemize}
+    \item[-] a finite set of states $S$
+    \item[-] a start state (also called initial state) $s_0$ which is an element of $S$
+    \item[-] a finite set called the input alphabet $I$
+    \item[-] a finite set called the output alphabet $O$
+    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping pairs of a
+      state and an input symbol to the corresponding next state.
+    \item[-] an output function $\lambda : S \times I \rightarrow O$ mapping pairs
+      of a state and an input symbol to the corresponding output symbol.
+  \end{itemize}
+\end{definition}
+
+\subsection{Active Learning}
 
@@
 All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
-of RAM and a Core i7-3630 CPU.
+of RAM and a Core i7-3630 CPU. The source code is available at
+\url{https://github.com/liyi-david/reo-learn}.
 
 \subsection{Case Studies}
+
 \subsection{Performance Optimization}
@@
 
+\subsection{An Example of the Reo Package}
+As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
+but also for practical concurrent programming.
+
+\todo{modify the listings package}
+\begin{lstlisting}
+int main(int argc, char ** argv)
+{
+  printf(``Hello world!n'');
+  return 0;
+}
+\end{lstlisting}
+
 \section{Conclusion and Future Work}

### 2016-01-11 paper/paper.tex
.

@@
 \usepackage{listings}
+% listing for golang
+% NOTE listings-golang.sty is required
+\usepackage{listings-golang}
 
@@
 \newcommand{\rnoread}[0]{\frownie}
+
+% style of source code environment listings
+\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
+\lstset{framextopmargin=50pt,frame=bottomline, language=Golang}
 
@@
 \label{sec:reo}
-Reo is a channel based exogenous coordination language proposed by F. Arbab. in
-\cite{DBLP:journals/mscs/Arbab04}. A Reo model, also called \emph{connector}, provides the protocol
+We provide here a brief overview of the main concepts of Reo, more details can be found in
+\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.
+
+Reo is a channel based exogenous coordination language proposed by F. Arbab. 
+A Reo model, also called \emph{connector}, provides the protocol
 that formalizes the communication, synchronization and cooperation among the components which
@@
 \emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
-channels ends release them out of the channel. Channels are attached on component instances
-or \emph{nodes}.
+channels ends release them out of the channel.
 
@@
     accept through the other end. Then both two data items will be lost.
-  \item [-] 
+  \item [-] A A \emph{FIFO1} channel is an asychronous channel with one buffer cell. It accepts a
+    data item whenever the buffer is empty.  
 \end{itemize}
@@
 
-\todo{do we need to remove this graph?}
+Channels are attached on component instances or \emph{nodes}. There are three types of nodes:
+\emph{source}, \emph{sink} and \emph{mixed node}, depending on whether all channel ends that
+coincide on a node are source ends, sink ends or both. (see in Figure \ref{fig:node})
+
 \begin{figure}[h]
   \begin{center}
-    \input{./images/reoextend.tex}
+    \input{./images/nodes.tex}
   \end{center}
-  \caption{Merger and Replicator}
-  \label{fig:reoextend}
+  \caption{Source, Sink and Mixed Nodes in Reo}
+  \label{fig:node}
 \end{figure}
+
+With definition of more basic channels, it's easy to extend Reo to formalize coordination in
+different areas. In this paper, we take timed Reo\cite{DBLP:conf/sefm/ArbabBBR04} as our formal
+model. Timed Reo includes several timed channels, where the most commonly-used one, called
+\emph{timer}, is also shown in Figure \ref{fig:basic}. A t-timer channel accepts any data item from
+its source end and returns on its sink end a timeout signal after a delay of t time units.
+
+Components can be linked to source nodes or sink nodes. A component can write data items to its
+corresponding source node only if the data item can be dispensed simultaneously to all source ends
+on this node. Meanwhile, a component can read a data item only if there is at least one readable
+sink end on its corresponding node. A mixed node non-determinstically selects and takes a data item
+from one of its coincident sink channel ends and replicates it into all of its coincident source
+channel ends.
+
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/connectorexample.tex}
+  \end{center}
+  \caption{Coordination with Reo Connectors}
+  \label{fig:reoconnector}
+\end{figure}
+
+As shown in Figure \ref{fig:reoconnector}, we use a simple example to illustrate how complex
+connectors are constructed and used in coordination. In this example, COM1,COM2 and
+MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
+COM1 and COM2 alternately.
 
@@
 
-\todo{modify the listings package}
 \begin{lstlisting}

### 2016-01-11 paper/paper.tex
.

@@
 \subsection{Active Learning}
+Active learning is a special case of semi-supervised machine learning in which a learning algorithm
+is able to interactively query the user (or some other information source) to obtain the desired
+outputs at new data points.\cite{settles2010active}.
 
@@
 As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
-but also for practical concurrent programming.
+but also for practical concurrent programming. The following code shows how to compose an alternator
+connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example can be found in our github repo.
 
 \begin{lstlisting}
-int main(int argc, char ** argv)
-{
-  printf(``Hello world!n'');
-  return 0;
+  package main
+
+  import . './lib/reo'
+
+  func alternator(A, B, C reo.Port) {
+    // definition of ports
+    M0 := MakePort()
+    // similarly define M1 ... M5
+
+    // definition of channels
+    go ReplicatorChannel(A, M0, M1)
+    go ReplicatorChannel(B, M2, M3)
+    go MergerChannel(M4, M5, M6)
+
+    go SyncdrainChannel(M1, M2)
+    go SyncChannel(M0, M4)
+    go FifoChannel(M3, M5)
   }

### 2016-01-11 calltest.go

@@ -1,0 +1,57 @@
+package main
+
+import reo "./lib/reo"
+import "fmt"
+import "sync"
+
+func alternator(A, B, C reo.Port) {
+	// definition of ports
+	M0 := reo.MakePort()
+	M1 := reo.MakePort()
+	M2 := reo.MakePort()
+	M3 := reo.MakePort()
+	M4 := reo.MakePort()
+	M5 := reo.MakePort()
+	M6 := reo.MakePort()
+	StopFlag := reo.GenerateStopPort(6)
+
+	// definition of channels
+	go reo.ReplicatorChannel(A, M0, M1, StopFlag[0])
+	go reo.ReplicatorChannel(B, M2, M3, StopFlag[1])
+	go reo.MergerChannel(M4, M5, M6, StopFlag[2])
+
+	go reo.SyncdrainChannel(M1, M2, StopFlag[3])
+	go reo.SyncChannel(M0, M4, StopFlag[4])
+	go reo.FifoChannel(M3, M5, StopFlag[5])
+}
+
+func sender(port reo.Port, msg string) {
+	for {
+		port.SyncWrite(msg)
+	}
+}
+
+func monitor(port reo.Port) {
+	for {
+		fmt.Println("[MONITOR]", port.SyncRead())
+	}
+}
+
+func main() {
+	// configurations
+	//reo.CloseLog()
+
+	var wg sync.WaitGroup
+	A := reo.MakePort()
+	B := reo.MakePort()
+	C := reo.MakePort()
+
+	// connector startup
+	alternator(A, B, C)
+	// running components
+	wg.Add(1)
+	go sender(A, "MSG A")
+	go sender(B, "MSG B")
+	go monitor(C)
+	wg.Wait()
+}

### 2016-01-11 calltest.go
bugs fixed

@@ -12,13 +12,12 @@ func alternator(A, B, C reo.Port) {
 	M3 := reo.MakePort()
 	M4 := reo.MakePort()
 	M5 := reo.MakePort()
-	M6 := reo.MakePort()
 	StopFlag := reo.GenerateStopPort(6)
 
 	// definition of channels
 	go reo.ReplicatorChannel(A, M0, M1, StopFlag[0])
 	go reo.ReplicatorChannel(B, M2, M3, StopFlag[1])
-	go reo.MergerChannel(M4, M5, M6, StopFlag[2])
+	go reo.MergerChannel(M4, M5, C, StopFlag[2])
 
 	go reo.SyncdrainChannel(M1, M2, StopFlag[3])
 	go reo.SyncChannel(M0, M4, StopFlag[4])
@@ -39,7 +38,7 @@ func monitor(port reo.Port) {
 
 func main() {
 	// configurations
-	//reo.CloseLog()
+	reo.CloseLog()
 
 	var wg sync.WaitGroup
 	A := reo.MakePort()

### 2016-01-11 paper/paper.tex
.

--- 2016-01-11 paper/paper.tex
@@
 % style of source code environment listings
-\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
-\lstset{framextopmargin=50pt,frame=bottomline, language=Golang}
+\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true, frame=shadowbox}
+\lstset{numbers=left}
+\lstset{xleftmargin=2em, xrightmargin=2em}
+\lstset{language=Golang}
 
@@
 
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/basic.tex}
+  \end{center}
+  \caption{Basic Reo Channels}
+  \label{fig:basic}
+\end{figure}
+
 The behavior of some channels are informally described as follows. (Graphical representations
@@
 \end{itemize}
-
-\begin{figure}[h]
-  \begin{center}
-    \input{./images/basic.tex}
-  \end{center}
-  \caption{Basic Reo Channels}
-  \label{fig:basic}
-\end{figure}
 
@@
 MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
-COM1 and COM2 alternately.
+COM1 and COM2 alternately. The \emph{alternator} example has been implemented in \texttt{Golang} as
+shown in Section \ref{sec:reolib}.
 
@@
 
-As far as we can see, various forms of Mealy machines are defined in different works. In this paper,
-we give the formal definition of Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.
-
-\todo{why we choose this version}
+As far as we can see, various forms of Mealy machines are defined in different works, wherein some
+are deterministic and some are not. Since active automata learning very much depends on the system
+under learning to be deterministic, in this paper we formally define a deterministic version of
+Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.
 
@@
 \subsection{Active Learning}
+In this section, we briefly introduce the main ideas of active automata learning.
+
+Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
+a learning algorithm is able to interactively query the target systems to obtain the desired outputs
+on certain inputs. With such flexibility, active learning makes it able to use targeted and efficient
+queries to obtain more accurate models with smaller dataset.
+
+\todo{a figure illustrating the framework of active learning}
+
+Figure shows a sketch of active learning, wherein
+\begin{itemize}
+  \item[-]
+\end{itemize}
+
+More details on the algorithm will be presented in Section \ref{sec:activelearning}.
 
@@
 \section{From Blackbox to Timed Connectors} 
+\label{sec:activelearning}
 
@@
 
-\subsection{An Example of the Reo Package}
+\subsection{An Example of the Reo Package }
+\label{sec:reolib}
+
 As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
-but also for practical concurrent programming.
+but also for practical concurrent programming. The following code shows how to compose an alternator
+connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example can be found in our github repo.
 
 \begin{lstlisting}
-int main(int argc, char ** argv)
-{
-  printf(``Hello world!n'');
-  return 0;
+package main
+
+import . './lib/reo'
+
+func alternator(A, B, C Port) {
+  // definition of ports
+  M0 := MakePort()
+  // M1 ... M5 defined similarly
+
+  // definition of channels
+  /* NOTE
+  go function() means that the function would
+  be executed as a new parallel task
+  */
+  go ReplicatorChannel(A, M0, M1)
+  go ReplicatorChannel(B, M2, M3)
+  go MergerChannel(M4, M5, C)
+
+  go SyncdrainChannel(M1, M2)
+  go SyncChannel(M0, M4)
+  go FifoChannel(M3, M5)
 }
 \end{lstlisting}
+
+Provided with the source and sink nodes, \emph{alternator} function creates a series of basic
+channels and mixed nodes (named \emph{Port}) to serve as the alternator connector we need. Now we
+can activate the components and using \emph{alternator} function to coordinate them.
+
+\begin{lstlisting}
+A := MakePort()
+B := MakePort()
+C := MakePort()
+alternator(A, B, C)
+
+go sender(A, "MSG A")
+go sender(B, "MSG B")
+go monitor(C)
+\end{lstlisting}
+
+In this case, \emph{sender} are goroutines (basic parallel units in \texttt{Golang}) that keep
+sending certain messages to some given port (A and B). A \emph{monitor} keep trying to read data
+items from the sink end C and print them on the screen. Finally we have a interleaved sequence of
+``MSG\_A'' and ``MSG\_B''.
 

### 2016-01-11 paper/paper.tex
.

@@
 \documentclass[conference, a4paper]{IEEEtran}
+
+\usepackage{graphicx}
 
@@
 \usepackage{listings-golang}
+% to support flow graphs
+\usepackage{textcomp}
 
 % positioning is used for below lef = of
-\usetikzlibrary{shapes,arrows,automata,positioning}
+\usetikzlibrary{shapes,shadows,arrows,automata,positioning}
 % some tikz-styles on reo channels, not required in papers that have nothing to do with Reo
@@
 \begin{IEEEkeywords}
-  Active Learning, Coordination Languages, Formal Methods
+  Active Learning, Coordination Languages, Timed Connectors
 \end{IEEEkeywords}
@@
 
-\todo{a figure illustrating the framework of active learning}
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=.4\textwidth]{./images/activelearning.png}
+  \end{center}
+  \caption{Active Automata Learning}
+  \label{fig:activelearning}
+\end{figure}
 
-Figure shows a sketch of active learning, wherein
+Figure \ref{fig:activelearning} shows a sketch of active learning, wherein:
 \begin{itemize}

### 2016-01-12 paper/paper.tex
.

@@
 \author{
-\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
+\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1}, Yiwu Wang\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
 \IEEEauthorblockA{
@@
 Beijing, China\\
-liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn
+liyi\_math@pku.edu.cn, yiwuwang@126.com, summeng@math.pku.edu.cn
 }
@@
   \begin{center}
-    \includegraphics[width=.4\textwidth]{./images/activelearning.png}
+    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
   \end{center}
@@
 
-Figure \ref{fig:activelearning} shows a sketch of active learning, wherein:
+Figure \ref{fig:activelearning} shows the sketch of active automata learning, wherein:
 \begin{itemize}
-  \item[-]
+  \item[-] \emph{Teacher} and \emph{Student}. Active learning is an interactive process where
+    students ask questions and teachers answer. Here learning algorithm plays the role of student.
+  \item[-] \emph{Oracles} is an interface specifying which kind of questions can be answered by the
+    teacher.
+  \item[-] \emph{SUL} is an abbreviation of System Under Learn. The name comes from a well-known
+    concept SUT (System Under Test) in software testing. In this case, we use blackbox models as our
+    SULs.
+  \item[-] \emph{CEGAR} indicates Counter-Example Guided Abstraction
+    Refinement\cite{DBLP:conf/cav/ClarkeGJLV00}. In active learning, we need counter-examples to
+    guide us on further quries and cover the undistinguished states.
 \end{itemize}
 
-More details on the algorithm will be presented in Section \ref{sec:activelearning}.
+When applying active automata learning on some model, firstly we assume that it should be equivalent
+to some \emph{Mealy machine}. In other words, a deterministic model accepting a finite set of input
+symbols and mapping them to a finite set of output symbols.
+
+Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
+all communication with the model, both providing input and obtaining output. Also, it serves as a
+so-called \emph{Minimal Adequate Teacher} interface, which is responsible for two types of
+queries.
+
+\begin{itemize}
+  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) The name comes from
+    some grammar-learning papers (e.g. \cite{DBLP:journals/iandc/Angluin87}), where \emph{mq} checks
+    if a word is a member of certain language defined by the given grammar. When it comes to
+    automata learning, \emph{mq} is supposed to provide simulation results for given input
+    sequences.
+    \todo{example, also a mealy-machine example}
+  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
+    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
+    equivalent to the system-under-learn and generates a counter-example if needed.
+\end{itemize}
+
+These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Figure
+\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm should construct a
+\emph{hypothesis} and check it with \emph{eq}. If counter-examples are found, we turn back and
+repeat the hypothesis construction until the equivalence query returns \emph{true}.
+
+More details on the active automata learning algorithm will be presented in Section
+\ref{sec:activelearning}.
 

### 2016-01-12 paper/paper.tex
.

@@
 
-In the past few years, researchers have been focusing on this area, and come up with a
-series of impressive works. 
+Distributed real-time embedded system (DRES) is reforming our lives with the name \emph{IoT}, the
+internet of things, wherein systems are usually composed of individual components and a middleware
+serving as a \emph{connector}. Such systems could be distributed logically or physically, which
+makes the coordination even more complicated. In this case, we need to specify these coordination
+processes with so-called \emph{coordination languages}, so that formal techniques can be applied to
+guarantee their reliability.
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.45\textwidth]{./images/IoT.png}
+  \end{center}
+  \caption{Inter of Things in Our Life}
+  \label{fig:IoT}
+\end{figure}
+
+researchers have been focusing on this area, and come up with a series of impressive works.
 \todo{a list}
@@
 problem: \emph{how can we obtain these models?}
+
+\emph{Correctness} of connectors is very much related to some low-level implementation details.
+For example, well-writen code may behave dramatically weird with an improper set of concurrency
+primitives. Such things happen frequently in embedded systems with different hardware platforms or
+operating systems. Consequently, manually modeling a existing connector seems rather unreliable,
+even with reference to its source code.
+
+In this paper, we proposed a active learning framework to automatically extract timed connectors
+from blackbox models.
 
@@
 \todo{better graph}
-\input{images/flow.tex}
+% \input{images/flow.tex}
 
@@
 
-Reo is a channel based exogenous coordination language proposed by F. Arbab. 
+Reo is a channel based exogenous coordination language proposed by F. Arbab in
+\cite{DBLP:journals/mscs/Arbab04}. 
 A Reo model, also called \emph{connector}, provides the protocol
@@
 As far as we can see, various forms of Mealy machines are defined in different works, wherein some
-are deterministic and some are not. Since active automata learning very much depends on the system
-under learning to be deterministic, in this paper we formally define a deterministic version of
+are deterministic and some are not. Since active automata learning very much depends on the
+system-under-learn to be deterministic, in this paper we formally define a deterministic version of
 Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.
@@
 Generally, these models are designed to handle real-time behavior where time is defined in
-$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
-easier.
-
-In this paper, we choose the rational number field $\mathbb{Q}$ as our time domain, which simplifies
-discretization of timed behaviors greatly.
+$\mathbb{R}$. Besides, we also found some works\cite{DBLP:journals/fmsd/PrabhakarDM015} rational
+time is chosen to make things easier. In this paper, we choose the rational number field
+$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behaviors greatly.
 

### 2016-01-12 paper/paper.tex
.

@@
 
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.45\textwidth]{./images/IoT.png}
-  \end{center}
-  \caption{Inter of Things in Our Life}
-  \label{fig:IoT}
-\end{figure}
+\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}. With timeline
+involved, coordination process in DRES can be depicted clearly and intuitively. Different formal
+semantics are proposed to specify the behavior of timed Reo.
+For example, in \cite{DBLP:conf/tase/Meng12}, a UTP-based
+(\emph{Unifying Theories of Programming}) semantics is provided to verify connectors as
+\emph{designs}. An operational semantics based on \emph{constraint automata} was raised by Baier et
+al., where a variant of LTL was also proposed to describe the properties of timed connectors.
 
-researchers have been focusing on this area, and come up with a series of impressive works.
-\todo{a list}
-However, most of these works are based on models, instead of binaries. Then it comes a well-known
-problem: \emph{how can we obtain these models?}
+Formal verification techniques have also been proved applicable in timed connectors.
+\cite{DBLP:conf/tase/LiCWS15} has shown us a comformance testing method on timed connectors.
+Bounded model checking methods were also adapted in \cite{DBLP:journals/scp/Kemper12}, based on SAT
+solvers. All these solutions seem practical and impressive, however, a common question is faced by
+most of them, which is: \emph{How to obtain these formal models?}
 
@@
 primitives. Such things happen frequently in embedded systems with different hardware platforms or
-operating systems. Consequently, manually modeling a existing connector seems rather unreliable,
+operating systems. Consequently, manually modeling an existing connector seems rather unreliable,
 even with reference to its source code.
 
-In this paper, we proposed a active learning framework to automatically extract timed connectors
-from blackbox models.
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=.4\textwidth]{./images/howto.png}
+  \end{center}
+  \caption{The Active Learning Framework}
+  \label{fig:howto}
+\end{figure}
+
+In this paper, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
+automatically extract timed connectors from blackbox models.
 
@@
 
-% it seems that we need a graph to describe how we're doing this work
-\todo{better graph}
-% \input{images/flow.tex}
+\todo{finish this part!}
 
-In this paper, we presented an adapted active learning algorithm to extract timed Reo connectors
-from binaries with no source code needed.
+The paper is structured as follows. After this general introduction, in Section
+\ref{sec:preliminaries} we briefly illustrate some basic concepts, including Reo the coordination
+language, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines the
+Mealy-machine-based operational semantics of Reo, which is used in Section \ref{sec:activelearning}
+to show how to extract Reo models from blackboxes by means of active learning. Finally, in Section
+\ref{sec:experiment}, we discuss the optimization and implementation in \texttt{Golang}.
 
 \section{Preliminaries} 
-
+\label{sec:preliminaries}
 \subsection{Reo Coordination Language} 
@@
 
+\todo{supplementation}
+
 \subsection{Active Learning}
@@
     if a word is a member of certain language defined by the given grammar. When it comes to
-    automata learning, \emph{mq} is supposed to provide simulation results for given input
+    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
     sequences.
-    \todo{example, also a mealy-machine example}
   \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
     (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
-    equivalent to the system-under-learn and generates a counter-example if needed.
+    equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
+    \emph{equivalence query} is irrealizable when SUT is a blackbox. So we tactically use membership
+    queries to achieve the approximate results.
 \end{itemize}
@@
 \section{Timed Connectors as Mealy Machines}
-
+\label{sec:semantics}
 \subsection{External Behavior of Reo Connectors}
@@
 \section{Experiments} 
+\label{sec:experiment}
+
 Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in

### 2016-01-13 paper/paper.tex
.

@@
 
-To solve this problem, many techniques in model constructing were proposed, for instance in
-\cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.
+As a branch of \emph{machine learning} technique, active learning directly applies queries to a
+low-level blackbox model and construct hypothesis according to the results.
+There're already several works like \cite{DBLP:journals/mt/Daelemans10,
+DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06} where active learning is used to extract
+\emph{finite state automatas} or \emph{grammars}.
 
-\todo{finish this part!}
+We present \emph{Parameterized Mealy machine} provide a parametierized semantics for timed Reo
+channels, which enables us to generate Mealy machines with a given alphabet. Then the $L*$ algorithm
+is adapted and optimized to handle Mealy machines with time action.
 
@@
 
-\section{Preliminaries} 
+\section{Preliminar ies} 
 \label{sec:preliminaries}
@@
 
+In this paper, we use \emph{Mealy machine} to model SUTs.
 As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
@@
 
-\todo{supplementation}
+We say that a Mealy machine is \emph{finite} if the set $S$ of states and the set $I$ of inputs are
+finite. Hereinafter, Mealy machines are always supposed to be finite.
+
+A Mealy machine is in some state $q\in S$ is always ready for inputs at any time. If an input symbol
+$i\in I$ is provided, the Mealy machine generates output $\lambda(q,i)$ and jumps to state
+$\delta(q,i)$.
 

### 2016-01-13 paper/paper.tex
.

@@
 \newcommand{\rblock}[0]{\circleddash}
-\newcommand{\rread}[0]{\smiley}
-\newcommand{\rnoread}[0]{\frownie}
+\newcommand{\rread}[0]{\rhd}
+\newcommand{\rnoread}[0]{\oslash}
+\newcommand{\smap}[1]{[{#1}]}
 
@@
 
+As a branch of \emph{machine learning} technique, active learning offers a way to obtain models from
+low-level blackboxes. Works in \cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87,
+DBLP:conf/fase/RaffeltS06} shows impressive examples where active learning is used to extract
+\emph{finite state automatas} or \emph{grammars}.
+
+\todo{better expressions!}
+
 \begin{figure}[h]
@@
 In this paper, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
-automatically extract timed connectors from blackbox models.
+automatically extract timed connectors from blackbox models. We present \emph{Parameterized Mealy
+machine} as a parametierized semantics for timed Reo channels, which enables us to generate Mealy
+machines with a given alphabet. Then the $L*$ algorithm is adapted and optimized to extract Mealy
+machines with time action from the \emph{connectors in blackboxes}.
 
-As a branch of \emph{machine learning} technique, active learning directly applies queries to a
-low-level blackbox model and construct hypothesis according to the results.
-There're already several works like \cite{DBLP:journals/mt/Daelemans10,
-DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06} where active learning is used to extract
-\emph{finite state automatas} or \emph{grammars}.
-
-We present \emph{Parameterized Mealy machine} provide a parametierized semantics for timed Reo
-channels, which enables us to generate Mealy machines with a given alphabet. Then the $L*$ algorithm
-is adapted and optimized to handle Mealy machines with time action.
-
-The paper is structured as follows. After this general introduction, in Section
+The rest of the paper is organized as follows. After this general introduction, in Section
 \ref{sec:preliminaries} we briefly illustrate some basic concepts, including Reo the coordination
@@
 
-\section{Preliminar ies} 
+\section{Preliminaries} 
 \label{sec:preliminaries}
@@
 \begin{definition}[Mealy machine]
-  A Mealy machine is a 6-tuple $(S, s_0, I, O, T, G)$ consisting of the following:
+  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of the following:
   \begin{itemize}
@@
 \label{sec:semantics}
-\subsection{External Behavior of Reo Connectors}
-So far as we can tell, most
-works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
-capable of infinite models. \todo{reason?} Considering the semantics defined in section
-\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
-automata, and the automata is also finite. Unfortunately, when checking the further definition of
-Reo connectors' input, we find that it's not the case.
+In this section, we show how a timed connector be transformed into a Mealy machine with time action.
 
-\todo{an example as graph}
-
-\begin{figure}[h]
-  \caption{Infinite States in a Reo Model}
-  \label{fig:reoinfinite}
-\end{figure}
-
-While focusing on behavior of connectors, Reo doesn't give detail depiction on behavior of
-components. As shown in \figurename \ref{fig:reoinfinite}, connectors are able to reject any datum
-if they are not ready. But what will happen outside the connector, if the datum is rejected? This
-question deserves careful consideration if we are taking an external view.
+Since time is not involed in original Mealy machine, we first discuss how to formalize the time
+dimension in Mealy machine and timed Connectors. After that, we present a \emph{parameterized Mealy
+machine} as a bridge between connectors and Mealy machines.
 
@@
 Generally, these models are designed to handle real-time behavior where time is defined in
-$\mathbb{R}$. Besides, we also found some works\cite{DBLP:journals/fmsd/PrabhakarDM015} rational
-time is chosen to make things easier. In this paper, we choose the rational number field
+$\mathbb{R}$. Besides, we also found some works like \cite{DBLP:journals/fmsd/PrabhakarDM015} where
+rational time indeed  makes things easier. In this paper, we choose the rational number field
 $\mathbb{Q}$ as our time domain, which simplifies discretization of timed behaviors greatly.
@@
 \subsection{Parameterized Mealy Machine}
-We present a model named \emph{parameterized mealy machine} to represent timed connectors
-(hereinafter referred to as PMM).
+We present a model named \emph{parameterized Mealy machine} (hereinafter referred to as PMM)
+to represent timed connectors. PMM is supposed to behave as a middle representation. Connectors are
+defined as parameterized mealy machines, and composed via its production operator. Then original
+mealy-machine model will be taken as semantics of PMM model.
 
-This model is supposed to behave as a middle representation. Connectors are defined as parameterized
-mealy machines, and composed via its production operator. Then original mealy-machine model will be
-taken as semantics of PMM model.
+Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we present the
+definition of \emph{parameterized Mealy machine} as follows.
 
 \begin{definition}[Parameterized Mealy Machine]
-  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
-  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
-  alphabet to its corresponding Mealy Machine. 
+  A \emph{Parameterized Mealy Machine} is defined as a 6-tuple $\mathcal{PM}=\langle
+  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ where 
   \begin{itemize}
@@
 
-In the definition above, \emph{Input} and \emph{Output} are used to generate input actions and output actions by the corresponding alphabets and ends.
+In the definition above, \emph{Input} and \emph{Output} are used to generate a set of input actions
+and output actions from the corresponding alphabets and ends. For example, if we have a alphabet
+consisting of two items $d_0$ and one source-end named $A$, the input actions would be
+\begin{eqnarray*}
+  Input(\{d_0\},\{A\}) &=& \{\{A:d_0,B:\rread\},\{A:d_0,B:\rnoread\}, \\
+  & & \{A:\bot,B:\rread\},\{A:\bot,B:\rnoread\},T\}
+\end{eqnarray*}
+where we use $\rread$ to indicate that a end-sink is ready for write, and $\rnoread$ otherwise.
+
 \todo{How to say?}
@@
 
-Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
-\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
+Parameterized Mealy machines can be seen as an abstract form of Mealy machines, which means that we
+still need a convert function between the two models.
+
+\begin{definition}[Concretize Mapping]
+  We use $\smap{\mathcal{PM}}_{\Sigma}$ to denote the concrete Mealy machine which is determined by
+  an abstract parameterized Mealy machine $\mathcal{PM}$ and the alphabet $\Sigma$. Apparently
+  $\smap{\mathcal{PM}}_{\Sigma}$ can be described as
+  \begin{eqnarray*}
+    \smap{\mathcal{PM}}_{\Sigma} &=& 
+    \langle
+    \mathcal{PM}.S(\Sigma), \mathcal{PM}.s_0, \\
+    & & Input(\Sigma, \mathcal{PM}.I), Output(\Sigma, \mathcal{PM}.O), \\
+    & & \mathcal{PM}.\delta(\Sigma), \mathcal{PM}.\lambda(\Sigma),
+    \rangle
+  \end{eqnarray*}
+\end{definition}
+
+Now we can use Parameterized Mealy Machines to define a new semantics for timed Reo. Here we
+take one asynchronous channel (FIFO1), one asynchronous channel (Sync) and one timed channel (Timer)
+as examples.
+
+\begin{example}[PMM Semantics of FIFO1 channel]
   \label{example:pmmfifo}
@@
     \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
-    \item[-] $I=\{A\}$
-    \item[-] $O=\{B\}$
-    \item[-] $s_0=q_0$
+    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
     \item[-] output function
@@
   \end{center}
-  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a\}$}
+  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{a\}$}
   \label{fig:pmmfifo}
 \end{figure}
+
+\begin{example}[PMM Semantics of Sync channel]
+  The PMM-based semantics of a Sync channel with a source-end A and a sink-end B can be defined as:
+  \begin{itemize}
+    \item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
+    \item[-] output function
+      \begin{displaymath}
+        \delta(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          (B:\bot) & s=q_0\land i=(A:\bot,B:\rnoread) \\
+          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
+          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
+          \rblock & s=q_0\land i=(A:d,B:\rnoread) \\
+        \end{array}
+        \right.
+      \end{displaymath}
+    \item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
+  \end{itemize}
+\end{example}
+
+\begin{example}[PMM Semantics of n-Timer channel]
+  Considering a n-Timer channel with a source-end A and a sink-end B, we define its PMM-based
+  semantics as:
+  \begin{itemize}
+    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
+    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
+    \item[-] output function
+      \begin{displaymath}
+        \delta(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
+          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
+          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
+          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
+          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
+          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
+        \end{array}
+        \right.
+      \end{displaymath}
+    \item[-] transition function
+      \begin{displaymath}
+        \lambda(\Sigma)(s,i)=\left\{
+        \begin{array}[h]{ll}
+          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
+          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
+          q_0 & otherwise \\
+        \end{array}
+        \right.
+      \end{displaymath}
+  \end{itemize}
+\end{example}
 
@@
 \label{sec:activelearning}
+In this section, we will show how to use L* algorithm to extract models from blackboxes. Firstly, we
+presents the definition of \emph{Observation Table}, which is used to describe the hypothesis.
 
@@
 \subsection{Case Studies}
+A simple example of timed connector is presented to show how L* works.
+\begin{figure}[h]
+  \begin{center}
+    \input{./images/expfifo.tex}
+  \end{center}
+  \caption{Expiring FIFO1 Channel}
+  \label{fig:expfifo}
+\end{figure}
 
@@
 \section{Conclusion and Future Work}
+Future work should focus on better representation on timed connectors and implementation of
+equivanlence query.
 

### 2016-01-14 paper/paper.tex
.

@@
 As a branch of \emph{machine learning} technique, active learning offers a way to obtain models from
-low-level blackboxes. Works in \cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87,
+low-level models. Works in \cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87,
 DBLP:conf/fase/RaffeltS06} shows impressive examples where active learning is used to extract
-\emph{finite state automatas} or \emph{grammars}.
-
-\todo{better expressions!}
+\emph{Mealy machines} or \emph{regular languages} without time domain.
 
@@
     accept through the other end. Then both two data items will be lost.
-  \item [-] A A \emph{FIFO1} channel is an asychronous channel with one buffer cell. It accepts a
+  \item [-] A \emph{FIFO1} channel is an asychronous channel with one buffer cell. It accepts a
     data item whenever the buffer is empty.  
@@
     \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
-      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
+      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,I,O)$ to denote the
+      output function.
     \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
-      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
+      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow S(\Sigma)$ to denote the transiton
       function.
@@
 In the definition above, \emph{Input} and \emph{Output} are used to generate a set of input actions
-and output actions from the corresponding alphabets and ends. For example, if we have a alphabet
-consisting of two items $d_0$ and one source-end named $A$, the input actions would be
+and output actions from the corresponding alphabets and ends. The value of $Input(\Sigma,I,O)$ is
+defined as a set of functions with on $I\cup O$ where $forall f\in Input(\Sigma,I,O)$, we have
+\[
+\forall i\in I, f(i)\in \Sigma\cup\{\bot\}\land \forall o\in
+O,f(o)\in\{\rread, \rnoread\}
+\]
+where we use $\rread$ to indicate that a end-sink is ready for write, and $\rnoread$ otherwise. Note
+that a $\bot$ means that there is \emph{no} data items on a source (or sink) end. In the same way,
+$Output(\Sigma,I,O)$ is defined as a set of functions on domain $O$, with an additional symbol
+$\rblock$ indicating an input failure. Similarly, $\forall f\in Output(\Sigma,I,O), f\neq \rblock$
+implies
+\[
+\forall o\in O, f(o)\in \Sigma\cup\{\bot\}
+\]
+
+\begin{example}[Input and Output]
+  If we have a simple alphabet with only one item $d_0$, a source-end named $A$, and a
+  sink-end named $B$, the input actions would be
+  \begin{small}
     \begin{eqnarray*}
-  Input(\{d_0\},\{A\}) &=& \{\{A:d_0,B:\rread\},\{A:d_0,B:\rnoread\}, \\
+      Input(\{d_0\},\{A\},\{B\}) &=& \{\{A:d_0,B:\rread\},\{A:d_0,B:\rnoread\}, \\
       & & \{A:\bot,B:\rread\},\{A:\bot,B:\rnoread\},T\}
     \end{eqnarray*}
-where we use $\rread$ to indicate that a end-sink is ready for write, and $\rnoread$ otherwise.
+  \end{small}
+  and its output actions
+  \[
+  Output(\{d_0\},\{A\},\{B\}) =\{\{B:d_0\},\{B:\bot\}, \rblock\}
+  \]
+\end{example}
 
-\todo{How to say?}
-\[
-Input(\Sigma,I)=\{\}\cup\{T\}
-\]
-where we use $T$ to denote the time action.
-\[
-Output(\Sigma,I)=\{\}
-\]
+If there no data item written to all sink ends, we use $\varnothing$ to denote the empty output. For
+example, in the case given above, $\{B:\bot\}$ can be briefly rewritten as $\varnothing$.
 
@@
           (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
+          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
           (B:d) & s=q_0\land i=(A:d,B:\rread)\\
-          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
           (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
           \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
-          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
+          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
         \end{array}
@@
   \begin{itemize}
-    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
+    \item[-] $S(\Sigma)=\{q_{i,d}|1\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
     \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
@@
         \begin{array}[h]{ll}
-          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
-          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
-          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
-          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
-          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
-          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
+          (B:d) & s=q_{n,d}\land i=(A:d,B:\rread)\\
+          \rblock & s=q_{n,d}\:\land \\
+          & (i=T\lor i=(A:\_,B:\rnoread) \\
+          \rblock & s=q_{j,d}\land 1 \leq j < n\land \\
+          & (i=(A:\_,B:\rread)\lor \\
+          & i=(A:d,B:\_))\\
+          (B:\bot) & otherwise\\
         \end{array}
@@
         \begin{array}[h]{ll}
-          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
-          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
-          q_0 & otherwise \\
+          q_{j+1,d} & s=q_{j,d}\land i=T\land0 < j < n\\
+          q_0 & s=q_{n,d}\land i=(A:\bot,B:\rread) \\
+          q_{1,d} & s=q_{n,d'}\land i=(A:d,B:\rread) \\
+          q_{1,d} & s=q_0 \land i=(A:d,B:\_) \\
+          s & otherwise \\
         \end{array}
@@
 
-\begin{definition}[Production of Parameterized Mealy Machines]
-  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
+\todo{check the timed behavior}
+\begin{definition}[Production Operator]
+  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines as,
   \[
@@
     \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
+  \end{itemize}
+  \emph{(Here we assume that sink ends of $PM_1$ can be connected to source ends $PM_2$, but not
+  vise versa)}
+  \begin{itemize}
     \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
@@
         \begin{array}[h]{ll}
-          (Out_1 + Out_2)|_{PM_3.O} & \rblock\land Out_2\neq\rblock \\
+          (Out_1 + Out_2)|_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
           \rblock & otherwise \\
@@
       \end{itemize}
-    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
+    \item[-] $\forall\Sigma, PM_3. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
       where we have
@@
 
-\todo{example of production, maybe fifo+timer}
+The idea in \emph{production} is quite simple. The output of $PM_1$ would be provided as part of the
+input of $PM_2$. Time actions T is only executed simutaneously betwenn $PM_1$ and $PM_2$.
+
+As mentioned in the notation above, we cannot connect a sink end of $PM_2$ and a source end of
+$PM_1$, which makes it difficult to construct connectors like alternator in Figure
+\ref{fig:reoconnector}. Now we define a \emph{link} operation to connect sink ends and source ends
+in the same connector.
+
+\begin{definition}[Link Operator]
+  The \emph{link} operation constructs connector by linking a sink end $OUT$ to a source end $IN$
+  within the same connector.   
+  \[
+  PM' = link(PM, OUT, IN)
+  \]
+  Here we asuume that $IN\in PM.I$ and $OUT\in PM.O$.
+
+  \begin{itemize}
+  	\item[-] $\forall\Sigma, PM'.S(\Sigma)=PM.S(\Sigma)$
+    \item[-] $PM'.I=PM.I-\{IN\}$
+    \item[-] $PM'.O=PM.O-\{OUT\}$
+    \item[-] $PM'.s=PM.s$
+    \item[-] $\forall\Sigma, i\in Input(\Sigma,PM'.I,PM'.O)$, $PM'.\delta(\Sigma)(s, i)=$
+      \begin{equation}
+        \label{equ:existd}
+        PM.\delta(\Sigma)(s,T)|_{PM'.O}
+      \end{equation}
+      if $i=T$. When $i$ is a non-time action, we need to check whether there's a data item
+      $d\in\Sigma$
+      satiefies
+      \[
+      PM.\delta(\Sigma)(s,i\cup\{IN:d\})|_{OUT} = d
+      \]
+      if \emph{true}, we have $PM'.\delta(\Sigma)(s, i)=$
+      \[
+      PM.\delta(\Sigma)(s,i\cup\{IN:d\})|_{PM'.O}
+      \]
+      otherwise $PM'.\delta(\Sigma)(s, i)=\rblock$
+    \item[-] $\forall\Sigma, i\in Input(\Sigma,PM'.I,PM'.O).'$ the transition
+      function can be defined as $PM.\lambda(\Sigma)(s,i)=$
+      \begin{displaymath}
+        \left\{
+        \begin{array}[h]{ll}
+          PM.\lambda(\Sigma,T) & i=T \\
+          PM.\lambda(\Sigma,i\cup\{IN:d\}) & \exists d\in\Sigma \mbox{ satisfes Equation
+          \ref{equ:existd}} \\
+          s & otherwise \\
+        \end{array}
+        \right.
+      \end{displaymath}
+  \end{itemize}
+\end{definition}
+
+With \emph{link} and \emph{prop} defined, complex connectors can be formed by simple channels in
+form of \emph{parameterized mealy machines}. It will be transformed into a concrete Mealy machine
+once the alphabet $\Sigma$ is provided.
 
@@
 \label{sec:activelearning}
-In this section, we will show how to use L* algorithm to extract models from blackboxes. Firstly, we
-presents the definition of \emph{Observation Table}, which is used to describe the hypothesis.
+In this section, we will show how to use L* algorithm to extract models from blackboxes, which
+mainly includes 3 steps: \emph{constructing hypothesis}, \emph{enclosing hypothesis} and
+\emph{checking hypothesis}.
 
@@
   \end{center}
-  \caption{Expiring FIFO1 Channel}
+  \caption{Expiring FIFO1 Channel (ExpFIFO1)}
   \label{fig:expfifo}
 \end{figure}
+
+Informally speaking, an expiring FIFO1 channel with \emph{timeout} $n$ is able to accept a data item
+and stored it in the buffer cell for $n$ time units. If a read operation on $B$ is performed within
+$n$ time units, it will obtain the data item successfully and clear the buffer. However, the data
+item would be dropped if no read operation comes.
 
@@
   \centering
-  \begin{tabular}{l||rrr}
+  \begin{tabular}{l||rrrr}
     \hline
-    & FIFO & Alternator & Gate \\
+    & FIFO & Alternator & Gate & ExpFIFO1\\
     \hline\hline
-    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
-    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
-    Total Time(s) & 41.715 & 165.114 & 247.098\\
-    Membership Query(\%) & 99.6 & 76.6 & 68.5\\
+    Membership Query(s) & 41.571 & 126.468 & 169.161 &\\
+    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 &\\
+    Total Time(s) & 41.715 & 165.114 & 247.098 &\\
+    Membership Query(\%) & 99.6 & 76.6 & 68.5 &\\
     \hline

### 2016-01-14 example/expfifo/oracle.go

@@ -4,15 +4,17 @@ import "../../lib/sul"
 import "../../lib/reo"
 import "time"
 import "strconv"
+import "fmt"
 
 func GetOracle() *sul.Oracle {
 	o := new(sul.Oracle)
 	o.InPorts = []string{"A"}
 	// dynamically generate the MidPorts
 	o.MidPorts = []string{}
-	for i := 0; i < 14; i++ {
+	for i := 0; i < 11; i++ {
 		o.MidPorts = append(o.MidPorts, "M"+strconv.Itoa(i))
 	}
+	fmt.Println(o.MidPorts)
 
 	o.OutPorts = []string{"B"}
 	o.TimeUnit = 40 * time.Millisecond
@@ -24,23 +26,20 @@ func GetOracle() *sul.Oracle {
 		// are closed
 		r.GeneratePort(o)
 		// generating stop ports
-		r.StopPorts = reo.GenerateStopPort(7)
+		r.StopPorts = reo.GenerateStopPort(10)
 		r.Start = func() {
 			// Input & Output
 			go reo.BufferChannel(1, r.InPorts["A"], r.MidPorts["M0"], r.StopPorts[0])
-			go reo.OutputChannel(r.MidPorts["M12"], r.OutPorts["B"], r.StopPorts[1])
+			go reo.OutputChannel(r.MidPorts["M10"], r.OutPorts["B"], r.StopPorts[1])
 			// Function Channels
-			go reo.SyncChannel(r.MidPorts["M0"], r.MidPorts["M1"], r.StopPorts[2])
-			go reo.ReplicatorChannel(r.MidPorts["M1"], r.MidPorts["M2"], r.MidPorts["M3"], r.StopPorts[3])
-			go reo.FifoChannel(r.MidPorts["M2"], r.MidPorts["M4"], r.StopPorts[4])
-			go reo.TimerChannel(r.MidPorts["M3"], r.MidPorts["M5"], 40*time.Millisecond, r.StopPorts[5])
-			go reo.LossysyncChannel(r.MidPorts["M5"], r.MidPorts["M6"], r.StopPorts[6])
-			go reo.ReplicatorChannel(r.MidPorts["M4"], r.MidPorts["M7"], r.MidPorts["M8"], r.StopPorts[7])
[…]

### 2016-01-15 paper/paper.tex
.

@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{cite}
@@
 \usepackage{textcomp}
+% highlight in tables
+\usepackage{xcolor}
+\usepackage{colortbl}
+
+\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
 
@@
 \newcommand{\smap}[1]{[{#1}]}
+\newcommand{\rempty}[0]{\varnothing}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{center}
@@
 \emph{timer}, is also shown in Figure \ref{fig:basic}. A t-timer channel accepts any data item from
-its source end and returns on its sink end a timeout signal after a delay of t time units.
+its source end, and later dispense it to its sink end after a delay of t time units.
 
@@
 A Mealy machine is in some state $q\in S$ is always ready for inputs at any time. If an input symbol
-$i\in I$ is provided, the Mealy machine generates output $\lambda(q,i)$ and jumps to state
-$\delta(q,i)$.
+$i\in I$ is provided, the Mealy machine generates output $o=\lambda(q,i)$ and jumps to state
+$q'=\delta(q,i)$. Such an edge is also denoted as $q\xrightarrow[]{i/o}q'$.
 
@@
         \delta(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
@@
         \lambda(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           q_d & s=q_0\land i=(A:d,B:\rnoread) \\
@@
 
-Besides, the concrete mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo}.
-\begin{figure}[h]
+Besides, the concrete mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo},
+where labels of edges are in form of $\frac{input}{output}$.
+\begin{figure}[ht]
   \begin{center}
@@
         \delta(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           (B:\bot) & s=q_0\land i=(A:\bot,B:\rnoread) \\
@@
   \begin{itemize}
-    \item[-] $S(\Sigma)=\{q_{i,d}|1\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
+    \item[-] $S(\Sigma)=\{q_{i,d}|0\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
     \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
@@
         \delta(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           (B:d) & s=q_{n,d}\land i=(A:d,B:\rread)\\
@@
         \lambda(\Sigma)(s,i)=\left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           q_{j+1,d} & s=q_{j,d}\land i=T\land0 < j < n\\
           q_0 & s=q_{n,d}\land i=(A:\bot,B:\rread) \\
-          q_{1,d} & s=q_{n,d'}\land i=(A:d,B:\rread) \\
-          q_{1,d} & s=q_0 \land i=(A:d,B:\_) \\
+          q_{0,d} & s=q_{n,d'}\land i=(A:d,B:\rread) \\
+          q_{0,d} & s=q_0 \land i=(A:d,B:\_) \\
           s & otherwise \\
@@
         \left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           (Out_1 + Out_2)|_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
@@
         \left\{
-        \begin{array}[h]{ll}
+        \begin{array}[ht]{ll}
           PM.\lambda(\Sigma,T) & i=T \\
@@
 mainly includes 3 steps: \emph{constructing hypothesis}, \emph{enclosing hypothesis} and
-\emph{checking hypothesis}.
+\emph{checking hypothesis}. Besides, we assume that input symbols and output symbols of the blackbox
+have been provided as $\mathcal{I}$ and $\mathcal{O}$.
 
 \subsection{Observation Table}
+As mentioned above, membership queries provide us information with the form $mq(s)=o$, where $s$ is
+an input sequence in $\Sigma^{+}$. Now the question is, \emph{how to find the connection between
+such query results and Mealy machines?}
 
-\subsection{Closeness}
+Generally, Mealy machines are composed of \emph{states} and \emph{transitions}.
+Provided with a Mealy machine $m$, any input sequence in $m.I^+$ leads to a unique state. 
+Such a sequence is called an \emph{access sequence} of this state.
+Specially, we use $\varepsilon$, the \emph{empty sequnce}, to denote the initial state.
+Similarly, if a blackbox model has the same bahavior with a Mealy machine, we can use access
+sequences to label its states and, in the same way, input actions to label its transitions.
+For example, we consider a Mealy machine stays is staying in some state labelled by $s$. With an
+action $a$ provided, the Mealy machine will jump to a new state labelled by $s'=sa$ and generate a
+output $mq(sa)$.
 
-\subsection{Counter-Examples}
-Generally, equivalence query has been proved impossible in blackbox
-models\cite{DBLP:journals/iandc/Angluin87}. However, in this
-section, we're showing that in certain circumstances, equivalence query can be implemented with
-no approximation.
+Different access sequences may lead to similar states. For example, a 2-Timer channel will dispense
+any accepted data item in 2 time units. After that, the state of this channel is exactly same as its
+initial state. Here \emph{suffixes} are used to distinguish different states as shown in the
+following definition, where $D$ is initialized as $\mathcal{I}$. Under such a suffix set, two states
+are considered different only when they have different one-step behaviors.
 
-Equivalence queries are used to search for counter-examples. But what makes counter-examples even
-existing? In Reo models, we believe that \emph{FIFO} channels and \emph{Timer} channels are to
-blame. Here we present a brief example. To make things eaiser, we have only untimed Reo here.
+\begin{definition}[Equivalence under Suffixes]
+  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
+  the corresponding states of $s_1$ and $s_2$ are equivalent under $D$ (denoted as $s_1\sim_D s_2$)
+  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
+\end{definition}
 
-\begin{figure}[h]
+Since all this \emph{inputs} and \emph{outputs} can be observed outside the
+model, we can use the same notations to describe a black box as a hypothetical Mealy machine.
+Following this idea, \emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87},
+shows a tabular form of such hypothetical models. In observation tables, rows represent states with
+label of their access sequences and columns are labelled suffixes. Successors of a state $s$ is,
+intuitively, denoted as extended access sequences $sa$ where $a$ is a single input action. 
+A cell with column-label $d$ and row-label $s$ should contain the value $mq(sd)$. Algorithm
+\ref{alg:buildtable} shows how to build such an observation table.
+
+\begin{algorithm} 
+  \caption{BuildTable} 
+  \label{alg:buildtable}
+  \KwIn{Oracle interface $mq$, Input actions $\mathcal{I}$, suffix set $D$}
+  \KwOut{Observation table $obs$} 
+  $obs$ initialized as empty\;
+  $unclosed=\{\varepsilon\}$\;
+  \Repeat{$unclosed=\varnothing$}
+  {
+    $next=\{st|\forall s\in unclosed,\forall t\in \mathcal{I}\}$\;
+    append $unclosed$ to $obs$\;
+    $unclosed=\{seq\in next|\forall a\in obs, seq \not\sim_D a\}$\;
+  }
+  \Return $obs$\; 
+\end{algorithm}
+
+Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
+We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$ and the alphabet
+is $\{a\}$. We briefly denote $\{A:a,B:\rnoread\}$ and other input/output actions in form of
+$a,\rnoread$.
+
+Firstly, $obs$ is initialized as empty and the empty sequence $\varepsilon$ is pushed in $unclosed$.
+Then we will explore all the access sequences in $unclosed$ and calculate its successors. Here the
+$unclosed$ set consists of access sequences that has no equivalent fellow with less length. 
+For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
+iteration. The five successors of $\varepsilon$ is presented as the bottom part of the table, where
+four are equivalent with $\varepsilon$ but $a,\rnoread$ is not. Therefore, we take $a,\rnoread$ as a
+brand-new state and all of its successors need further exploration (see in the hypothesis Mealy
+machine presented in the following figure).
+
+\begin{figure}[ht]
   \begin{center}
-    \input{./images/3buf.tex}
+    \begin{displaymath}
+      \begin{array}{l||ccccc}
+        \hline
+        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T\\
+        \hline\hline
+        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \hline
+        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \rowcolor[gray]{.9}
+        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty  \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \hline
+      \end{array}
+    \end{displaymath}
+    \input{./images/hypo.tex}
   \end{center}
-  \caption{A Switching Connector $S$ with Three Buffers}
-  \label{fig:buf3}
+  \caption{Observation Table and Corresponding Hypothesis}
+  \label{fig:hypo}
 \end{figure}
 
-A \emph{Switching} connector in \figurename \ref{fig:buf3} has two source-ends $A,B$ and one
-sink-end $C$. In a nutshell, datum come from $A$ and be stored temporarily in buffers. These datum
-will never flow out until signals come to $B$. With the Mealy-Machine semantics given, the semantics
-of \emph{Switching} connectors can be defined as following \figurename \ref{fig:buf3semantics}.
+In the second iteration, we explore the successors of $a,\rnoread$. Fortunately we find that every
+successor has a shorted equivalence fellow (\emph{itself}). Consequently, the algorithm terminates
+with a closed hypothesis where all the unclosed edge shown in Figure \ref{fig:hypo} turn into
+self-loop.
 
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{center}
-    \input{./images/3bufsemantics.tex}
+    \begin{displaymath}
+      \begin{array}{l||ccccc}
+        \hline
+        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T\\
+        \hline\hline
+        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \hline
+        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty  \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \hline
+        a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        \hline
+      \end{array}
+    \end{displaymath}
   \end{center}
-  \caption{\emph{Gate} as Mealy Machine $\mathcal{M}(S)$}
-  \label{fig:buf3semantics}
+  \caption{A Closed Observation Table}
+  \label{fig:hypo2}
 \end{figure}
 
-According to the production of Mealy-Machines, 8 different states should be found in
-$\mathcal{M}(S)$. We use $q_{abc}$ to denote them. $q_{001}$ indicates that the last buffer is
-filled and others are empty, and $q_{111}$ means that there are no space in any buffer. It's
-obvious that some states like $q_{100}$ is unreachable.
+\subsection{Counter-Examples' Analysis} 
+In our framework, the oracle function $eq$ is used to check the equivalence between hypothesis
+models and blackboxes. It is also responsible for generating counter-examples.
+Generally, as mentioned in \cite{DBLP:journals/iandc/Angluin87,DBLP:conf/sfm/SteffenHM11},
+equivalence query has been proved impossible in blackbox models.
 
-We say if two states are \emph{similiar} iff. they have the same output signature.
-
-\begin{theorem}[Bound of Counter-Example]
-  \label{the:cebound} Assume that an observation table has already been closed with maximum
-  query length \todo{find a better phrase?} $l$. An counter-example of length $l+2$ would be
-  found iff. there're possible counter-examples.
-\end{theorem}
-\begin{IEEEproof}
-  Sketch of this proof are shown in several points:
-  \begin{enumerate}
-    \item Hypothesises are subgraphs of the semantics graph.
-    \item Inputs on reverse edges are complementary.
-    \item 
-  \end{enumerate}
-\end{IEEEproof}
+Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not equal to the 2-Timer
+channel. It's easy to find a counter-example $s=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
+according to the hypothesis, the result shoud have been $\rempty$. As mentioned above, we use a
+suffix set $D$ to distinguish different states. The existance of counter-examples shows that the
+current suffix set $D$ is not powerful enough to distinguish all different states. We need to analyze
+the counter-example and in turn append more elements to $D$.
 
@@
 A simple example of timed connector is presented to show how L* works.
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{center}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
   \renewcommand{\arraystretch}{1.3}
@@
 simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
-these results. A brief example of such trees can be found in Figure \ref{fig:multiway}.
+these results.
 
-\todo{the graph need further details}
-\begin{example}[Multiway-Tree Cache]
-  \label{example:tree}
-  Considering the FIFO channel presented in Example \ref{example:pmmfifo}. 
-  \begin{figure}[h]
-    \begin{center}
-      \input{./images/cache.tex}
-    \end{center}
-    \caption{Multiway-Tree Cache}
-    \label{fig:multiway}
-  \end{figure}
-  Note that in this figure, only the edge information is stored. States like $q_0,q_a$ are written
-  here only to make it clear.
-\end{example}
-
-\begin{table}[h]
+\begin{table}[ht]
   \renewcommand{\arraystretch}{1.3}
@@
 
-With cache applied, we have made a good reduction on the calls of membership queries. The results
+With cache applied, we have made considerable reduction on the calls of membership queries. The results
 can be found in Table \ref{tabel:cacheoptimization}.

### 2016-01-15 paper/paper.tex
.

@@
 
-% FIXME finally no todos should exist in this draft
-\usepackage[textsize=tiny]{todonotes}
+% finally no todos should exist in this draft
+% \usepackage[textsize=tiny]{todonotes}
 
@@
 Distributed real-time embedded system (DRES) is reforming our lives with the name \emph{IoT}, the
-internet of things, wherein systems are usually composed of individual components and a middleware
-serving as a \emph{connector}. Such systems could be distributed logically or physically, which
-makes the coordination even more complicated. In this case, we need to specify these coordination
+internet of things, wherein systems are usually composed of individual components and a
+\emph{connector}. Such systems could be distributed logically or physically, which
+makes coordination processes even more complicated. In this case, we need to specify these coordination
 processes with so-called \emph{coordination languages}, so that formal techniques can be applied to
@@
 
-\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}. With timeline
-involved, coordination process in DRES can be depicted clearly and intuitively. Different formal
+\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, by which
+coordination process in DRES can be depicted clearly and intuitively. Different formal
 semantics are proposed to specify the behavior of timed Reo.
@@
 \emph{designs}. An operational semantics based on \emph{constraint automata} was raised by Baier et
-al., where a variant of LTL was also proposed to describe the properties of timed connectors.
+al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the properties of timed connectors.
 
-Formal verification techniques have also been proved applicable in timed connectors.
+Formal verification techniques have also been proved applicable in timed connectors, e.g.
 \cite{DBLP:conf/tase/LiCWS15} has shown us a comformance testing method on timed connectors.
-Bounded model checking methods were also adapted in \cite{DBLP:journals/scp/Kemper12}, based on SAT
-solvers. All these solutions seem practical and impressive, however, a common question is faced by
-most of them, which is: \emph{How to obtain these formal models?}
+Bounded model checking methods based on SAT solvers were also adapted in
+\cite{DBLP:journals/scp/Kemper12}.
+All these solutions seem practical and impressive, however, a common question is faced by
+most of them: \emph{how to obtain these formal models?}
 
@@
 low-level models. Works in \cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87,
-DBLP:conf/fase/RaffeltS06} shows impressive examples where active learning is used to extract
+DBLP:conf/fase/RaffeltS06} shows interesting examples where active learning is used to extract
 \emph{Mealy machines} or \emph{regular languages} without time domain.
@@
 
-In this paper, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
-automatically extract timed connectors from blackbox models. We present \emph{Parameterized Mealy
-machine} as a parametierized semantics for timed Reo channels, which enables us to generate Mealy
-machines with a given alphabet. Then the $L*$ algorithm is adapted and optimized to extract Mealy
-machines with time action from the \emph{connectors in blackboxes}.
+To address the problem, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
+automatically extract timed connectors from blackbox models. To achieve this goal, firstly we
+present \emph{parameterized Mealy machine} as a parametierized semantics for timed Reo channels,
+which is able to generate concrete Mealy machines with a given alphabet. Then the $L*$ algorithm
+\cite{DBLP:journals/iandc/Angluin87}
+is adapted and optimized to extract Mealy machines with time action from the \emph{connectors in
+blackboxes}.
 
@@
 \ref{sec:preliminaries} we briefly illustrate some basic concepts, including Reo the coordination
-language, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines the
-Mealy-machine-based operational semantics of Reo, which is used in Section \ref{sec:activelearning}
-to show how to extract Reo models from blackboxes by means of active learning. Finally, in Section
-\ref{sec:experiment}, we discuss the optimization and implementation in \texttt{Golang}.
+language, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines an
+operational semantics of Reo, which is used in Section \ref{sec:activelearning} to show how to
+extract Reo models from blackboxes by means of active learning. Finally, in Section
+\ref{sec:experiment}, we discuss the implementation and optimization in \texttt{Golang}.
 
@@
 \label{sec:reo}
-We provide here a brief overview of the main concepts of Reo, more details can be found in
+We provide here a brief overview of the main concepts in Reo. Further details can be found in
 \cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.
@@
 that formalizes the communication, synchronization and cooperation among the components which
-communicate through the connector. Connectors can be defined with no knowledge of the components,
+communicate through the connector. Connectors can be defined without dependence on components,
 which makes Reo a powerful ``glue language'' in component-based
@@
 
-In Reo, complex connectors are made up of simpler ones, where the atomic connectors are called
-\emph{channels}. Each channel has two \emph{channel ends}. There are two type of channel ends:
+In Reo, complex connectors are made up of simpler ones. The atomic connectors are called
+\emph{channels}, and each of them has two \emph{channel ends}. There are two type of channel ends:
 \emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
-channels ends release them out of the channel.
+channels ends dispense them out of the channel.
 
@@
 \begin{itemize}
-  \item [-] A \emph{Sync} channel accepts a data item from its source end iff. the data item can be
+  \item [-] A \emph{Sync} channel accepts a data item from its source end iff the data item can be
     dispensed to its sink end simultaneously.
@@
   \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
-    item through one of its source end iff. a data item is also available for it to simultaneously
-    accept through the other end. Then both two data items will be lost.
-  \item [-] A \emph{FIFO1} channel is an asychronous channel with one buffer cell. It accepts a
+    item through one of its source end iff a data item is also available to accept simultaneously
+    through the other end. Then both items will be dropped.
+  \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
     data item whenever the buffer is empty. 
@@
 corresponding source node only if the data item can be dispensed simultaneously to all source ends
-on this node. Meanwhile, a component can read a data item only if there is at least one readable
+on this node. Similarly, a component can read a data item only if there is at least one readable
 sink end on its corresponding node. A mixed node non-determinstically selects and takes a data item
-from one of its coincident sink channel ends and replicates it into all of its coincident source
-channel ends.
+from one of its coincident sink ends and replicates it into all of its coincident source ends.
 
@@
 connectors are constructed and used in coordination. In this example, COM1,COM2 and
-MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
+MONITOR are components. With an \emph{alternator} connector, MONITOR can obtain data items from
 COM1 and COM2 alternately. The \emph{alternator} example has been implemented in \texttt{Golang} as
 shown in Section \ref{sec:reolib}.
+Besides, all the connectors are supposed to be \emph{deterministic} hereinafter to meet the
+requirement of active learning algorithm L*.
 
@@
 
-In this paper, we use \emph{Mealy machine} to model SUTs.
+In this work, we use \emph{Mealy machines} to model Reo connectors.
 As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
@@
 possible inputs should be acceptable in all states. In other words, if an input is invalid for some
-state, we need to manually use an additional state to describe such exceptions.
+state, we need to manually define an additional state to describe such exceptions.
 
-As far as we can see, various forms of Mealy machines are defined in different works, wherein some
-are deterministic and some are not. Since active automata learning very much depends on the
-system-under-learn to be deterministic, in this paper we formally define a deterministic version of
-Mealy machine following \cite{DBLP:conf/sfm/SteffenHM11}.
+Various forms of Mealy machines are defined in different works. 
+Since active automata learning very much depends on the system-under-learn to be deterministic, in
+this paper we formally define a deterministic Mealy machine following
+\cite{DBLP:conf/sfm/SteffenHM11}.
 
@@
 a learning algorithm is able to interactively query the target systems to obtain the desired outputs
-on certain inputs. With such flexibility, active learning makes it able to use targeted and efficient
-queries to obtain more accurate models with smaller dataset.
+under certain inputs. By well-designed query strategy, active learning is able to obtain more
+accurate models with smaller dataset.
 
@@
 
-Figure \ref{fig:activelearning} shows the sketch of active automata learning, wherein:
+Figure \ref{fig:activelearning} shows the sketch of active learning, wherein:
 \begin{itemize}
-  \item[-] \emph{Teacher} and \emph{Student}. Active learning is an interactive process where
+  \item[-] \emph{Teacher} and \emph{Student}: Active learning is an interactive process where
     students ask questions and teachers answer. Here learning algorithm plays the role of student.
@@
   \item[-] \emph{SUL} is an abbreviation of System Under Learn. The name comes from a well-known
-    concept SUT (System Under Test) in software testing. In this case, we use blackbox models as our
+    concept SUT (System Under Test) in software testing. In this case, we take blackbox models as our
     SULs.
@@
 When applying active automata learning on some model, firstly we assume that it should be equivalent
-to some \emph{Mealy machine}. In other words, a deterministic model accepting a finite set of input
+to some \emph{Mealy machine}, in other words, a deterministic model accepting a finite set of input
 symbols and mapping them to a finite set of output symbols.
@@
 Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
-all communication with the model, both providing input and obtaining output. Also, it serves as a
-so-called \emph{Minimal Adequate Teacher} interface, which is responsible for two types of
-queries.
+all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate Teacher}
+interface, which is responsible for two types of queries.
 
@@
     equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
-    \emph{equivalence query} is irrealizable when SUT is a blackbox. So we tactically use membership
+    \emph{equivalence query} is irrealizable when SUL is a blackbox. So we tactically use membership
     queries to achieve the approximate results.
@@
 These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Figure
-\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm should construct a
-\emph{hypothesis} and check it with \emph{eq}. If counter-examples are found, we turn back and
+\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm constructs a
+\emph{hypothesis} and then check it with \emph{eq}. If counter-examples are found, we turn back and
 repeat the hypothesis construction until the equivalence query returns \emph{true}.
@@
 \label{sec:semantics}
-In this section, we show how a timed connector be transformed into a Mealy machine with time action.
-
+In this section, we illustrate how to transform a timed connector into a Mealy machine with time
+action.
 Since time is not involed in original Mealy machine, we first discuss how to formalize the time
-dimension in Mealy machine and timed Connectors. After that, we present a \emph{parameterized Mealy
+dimension in Mealy machine. After that, we present a \emph{parameterized Mealy
 machine} as a bridge between connectors and Mealy machines.
@@
 \subsection{Time Domain}
-Time is involved in several extension version of Reo. For example, Timed
-Reo\cite{DBLP:conf/sefm/ArbabBBR04}, Hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
+Time is involved in several extensions of Reo. For example, timed
+Reo\cite{DBLP:conf/sefm/ArbabBBR04}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
 Generally, these models are designed to handle real-time behavior where time is defined in
-$\mathbb{R}$. Besides, we also found some works like \cite{DBLP:journals/fmsd/PrabhakarDM015} where
+$\mathbb{R}$. However, we also found some works like \cite{DBLP:journals/fmsd/PrabhakarDM015} where
 rational time indeed  makes things easier. In this paper, we choose the rational number field
@@
 
-In real systems, the concept \emph{time precision} is widely used with the name ``clock-period''.
-Most of the time, we know the clock-cycle of some hardware components, even without any idea of its
-structure. With such precision $T$ given, it's reasonable to assume that all $t$-timers are actually
-$nT$-timers. In following sections, we'll use $n$-timers instead.
+In real systems, the concept \emph{time precision} is well known with other names like ``clock-period''.
+Most of the time, we know the clock-period of some hardware components, even without any idea of its
+structure. With such precision $dt$ given, it's reasonable to assume that all $t$-timers are actually
+$ndt$-timers. In following sections, we'll use $n$-Timers instead.
 
-Besides, we're going to add a ``T'' action in mealy machines. It indicates that a transition
-will take a time unit to finish, and all outputs would come out after that.
+Besides, we're going to add a ``T'' action in Mealy machines. It indicates that a transition
+will take a time unit to finish.
 
@@
 We present a model named \emph{parameterized Mealy machine} (hereinafter referred to as PMM)
-to represent timed connectors. PMM is supposed to behave as a middle representation. Connectors are
-defined as parameterized mealy machines, and composed via its production operator. Then original
-mealy-machine model will be taken as semantics of PMM model.
-
-Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we present the
-definition of \emph{parameterized Mealy machine} as follows.
+to model timed connectors. PMM is supposed to behave as a middle representation between Mealy
+machines and timed connectors. Connectors are firstly defined as parameterized Mealy machines, and
+composed by production operator and link operator. Then, concrete Mealy-machine model can be
+generated from the PMM model.
+Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the
+\emph{parameterized Mealy machine} as follows.
 
@@
   A \emph{Parameterized Mealy Machine} is defined as a 6-tuple $\mathcal{PM}=\langle
-  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ where 
+  S, s_0, I, O, \delta, \lambda\rangle$ with a parameter named $\Sigma$ where 
   \begin{itemize}
-    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereinafter referred to as an alphabet)
+    \item[-] $\Sigma$, the parameter, is a \emph{finite} datum alphabet
     \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
@@
 
-In the definition above, \emph{Input} and \emph{Output} are used to generate a set of input actions
-and output actions from the corresponding alphabets and ends. The value of $Input(\Sigma,I,O)$ is
-defined as a set of functions with on $I\cup O$ where $forall f\in Input(\Sigma,I,O)$, we have
+In the definition above, \emph{Input} and \emph{Output} are used to generate input actions
+and output actions from the corresponding alphabets and source/sink ends. The value of $Input(\Sigma,I,O)$ is
+defined as a set of functions on $I\cup O$ where $\forall f\in Input(\Sigma,I,O)$ and an additional
+\emph{time action} T, we have
 \[
-\forall i\in I, f(i)\in \Sigma\cup\{\bot\}\land \forall o\in
+\forall i\in I\backslash\{T\}, f(i)\in \Sigma\cup\{\bot\}\land \forall o\in
 O,f(o)\in\{\rread, \rnoread\}
 \]
-where we use $\rread$ to indicate that a end-sink is ready for write, and $\rnoread$ otherwise. Note
+where we use $\rread$ to indicate that an end-sink is ready for write, and $\rnoread$ otherwise. Note
 that a $\bot$ means that there is \emph{no} data items on a source (or sink) end. In the same way,
@@
 
-If there no data item written to all sink ends, we use $\varnothing$ to denote the empty output. For
-example, in the case given above, $\{B:\bot\}$ can be briefly rewritten as $\varnothing$.
+If there is no data item written to any sink ends, we use $\varnothing$ to denote such an empty
+output. For example, in the case given above, $\{B:\bot\}$ can be briefly rewritten as $\varnothing$.
 
@@
 
-Now we can use Parameterized Mealy Machines to define a new semantics for timed Reo. Here we
+Now we can use parameterized Mealy Machines to define a new semantics for timed Reo. Here we
 take one asynchronous channel (FIFO1), one asynchronous channel (Sync) and one timed channel (Timer)
@@
 
-Besides, the concrete mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo},
+Besides, the concrete Mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo},
 where labels of edges are in form of $\frac{input}{output}$.
@@
 \begin{example}[PMM Semantics of n-Timer channel]
-  Considering a n-Timer channel with a source-end A and a sink-end B, we define its PMM-based
+  Considering an n-Timer channel with a source-end A and a sink-end B, we define its PMM-based
   semantics as:
@@
 
-\todo{check the timed behavior}
 \begin{definition}[Production Operator]
@@
         \begin{array}[ht]{ll}
-          (Out_1 + Out_2)|_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
+          (Out_1 + Out_2)\downarrow_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
+          \rempty & i = T \\
           \rblock & otherwise \\
@@
       \begin{itemize}
-        \item[*] $In_1 = i|_{PM_1.I}$
+        \item[*] $In_1 = i\downarrow_{PM_1.I}$
         \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
-        \item[*] $In_2 = (Out_1 + i)|_{PM_2.I}$
+        \item[*] $In_2 = (Out_1 + i)\downarrow_{PM_2.I}$
         \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
@@
 The idea in \emph{production} is quite simple. The output of $PM_1$ would be provided as part of the
-input of $PM_2$. Time actions T is only executed simutaneously betwenn $PM_1$ and $PM_2$.
+input of $PM_2$. Time actions T is only executed simutaneously between $PM_1$ and $PM_2$.
 
-As mentioned in the notation above, we cannot connect a sink end of $PM_2$ and a source end of
+As mentioned in the notation above, we cannot connect a sink end of $PM_2$ to a source end of
 $PM_1$, which makes it difficult to construct connectors like alternator in Figure
-\ref{fig:reoconnector}. Now we define a \emph{link} operation to connect sink ends and source ends
-in the same connector.
+\ref{fig:reoconnector}. To address the problem, we define a \emph{link} operation to connect sink
+ends and source ends in the same connector.
 
 \begin{definition}[Link Operator]
-  The \emph{link} operation constructs connector by linking a sink end $OUT$ to a source end $IN$
+  The \emph{link} operation constructs connector by connecting a sink end $OUT$ to a source end $IN$
   within the same connector.   
@@
         \label{equ:existd}
-        PM.\delta(\Sigma)(s,T)|_{PM'.O}
+        PM.\delta(\Sigma)(s,T)\downarrow_{PM'.O}
       \end{equation}
@@
       $d\in\Sigma$
-      satiefies
+      satisfies
       \[
-      PM.\delta(\Sigma)(s,i\cup\{IN:d\})|_{OUT} = d
+      PM.\delta(\Sigma)(s,i\cup\{IN:d\})\downarrow_{OUT} = d
       \]
-      if \emph{true}, we have $PM'.\delta(\Sigma)(s, i)=$
+      if the formula is satisfied, we have $PM'.\delta(\Sigma)(s, i)=$
       \[
-      PM.\delta(\Sigma)(s,i\cup\{IN:d\})|_{PM'.O}
+      PM.\delta(\Sigma)(s,i\cup\{IN:d\})\downarrow_{PM'.O}
       \]
@@
 With \emph{link} and \emph{prop} defined, complex connectors can be formed by simple channels in
-form of \emph{parameterized mealy machines}. It will be transformed into a concrete Mealy machine
-once the alphabet $\Sigma$ is provided.
+form of \emph{parameterized Mealy machines}. It will be transformed into a concrete Mealy machine
+later once the alphabet $\Sigma$ is provided.
 
@@
 \label{sec:activelearning}
-In this section, we will show how to use L* algorithm to extract models from blackboxes, which
-mainly includes 3 steps: \emph{constructing hypothesis}, \emph{enclosing hypothesis} and
-\emph{checking hypothesis}. Besides, we assume that input symbols and output symbols of the blackbox
-have been provided as $\mathcal{I}$ and $\mathcal{O}$.
+In this section, we show how to use L* algorithm to extract models from blackboxes in  3 steps:
+\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{checking hypothesis}. Besides,
+we assume that input symbols and output symbols of the blackbox have been provided as $\mathcal{I}$
+and $\mathcal{O}$.
 
@@
 Such a sequence is called an \emph{access sequence} of this state.
-Specially, we use $\varepsilon$, the \emph{empty sequnce}, to denote the initial state.
+Particularly, we use $\varepsilon$, the \emph{empty sequnce}, to denote the initial state.
 Similarly, if a blackbox model has the same bahavior with a Mealy machine, we can use access
 sequences to label its states and, in the same way, input actions to label its transitions.
-For example, we consider a Mealy machine stays is staying in some state labelled by $s$. With an
-action $a$ provided, the Mealy machine will jump to a new state labelled by $s'=sa$ and generate a
+For example, we consider a Mealy machine which is staying in some state labelled by $s$. With an
+action $a$ provided, the Mealy machine will jump to a new state labelled by $s'=sa$ and generate an
 output $mq(sa)$.
@@
 shows a tabular form of such hypothetical models. In observation tables, rows represent states with
-label of their access sequences and columns are labelled suffixes. Successors of a state $s$ is,
+label of their access sequences and columns are labelled with suffixes. Successors of a state $s$ is,
 intuitively, denoted as extended access sequences $sa$ where $a$ is a single input action. 
@@
     with prefix 'a' and suffix 'ab'.
-  \item Simulation on mealy machines can provide multi-step output. Consequently, if we has
+  \item Simulation on mealy machines can provide multi-step output. Consequently, if we have
     simulated an 'abc' sequence, there's no reason to perform simulation on an 'ab' sequence.
@@
 but also for practical concurrent programming. The following code shows how to compose an alternator
-connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example can be found in our github repo.
+connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
+can be found in our github repo.
 
 \begin{lstlisting}
-package main
-
-import . './lib/reo'
-
 func alternator(A, B, C Port) {
-  // definition of ports
-  M0 := MakePort()
-  // M1 ... M5 defined similarly
+  M := MakePorts(6)
 
   // definition of channels
-  /* NOTE
-  go function() means that the function would
-  be executed as a new parallel task
-  */
-  go ReplicatorChannel(A, M0, M1)
-  go ReplicatorChannel(B, M2, M3)
-  go MergerChannel(M4, M5, C)
+  go ReplicatorChannel(A, M[0], M[1])
+  go ReplicatorChannel(B, M[2], M[3])
+  go MergerChannel(M[4], M[5], C)
 
-  go SyncdrainChannel(M1, M2)
-  go SyncChannel(M0, M4)
-  go FifoChannel(M3, M5)
+  go SyncdrainChannel(M[1], M[2])
+  go SyncChannel(M[0], M[4])
+  go FifoChannel(M[3], M[5])
 }
@@
 \begin{lstlisting}
-A := MakePort()
-B := MakePort()
-C := MakePort()
+A,B,C := MakePorts(3)
 alternator(A, B, C)
@@
 sending certain messages to some given port (A and B). A \emph{monitor} keep trying to read data
-items from the sink end C and print them on the screen. Finally we have a interleaved sequence of
+items from the sink end C and print them on the screen. Finally, we have an interleaved sequence of
 ``MSG\_A'' and ``MSG\_B''.
@@
 \section{Conclusion and Future Work}
-Future work should focus on better representation on timed connectors and implementation of
-equivanlence query.
+In this paper, we come up with an approach to learn timed connectors from blackboxes. We define
+the \emph{parameterized Mealy machine} to serve as an operational semantics of Reo. Then we
+describe a set of basic channels with parameterized Mealy machine, which can be used to construct
+complex connectors by means of the production operator and link operator.
+Besides, we show that every connector can be transformed into a Mealy
+machine with time action T, and such Mealy machines can be extracted by an improved version of
+well-knwon active learning algorithm L*.
 
+The original L* algorithm run into the bottleneck when time is involved. By a tree-style cache, we
+make significant reduction on membership queries and, in turn, improve the performance of learning
+algorithm. As a by-product, we also encapsulate the Reo connector as a distributable package which
+could contribute to concurrent programming.
+
+Our future works would mainly focus on better support of dense time. To describe dense
+time behavior, the Mealy machine model needs a lot of changes instead of a simple T action. Besides,
+we will also try to improve our algorithm to handle non-deterministic behaviors. This is not a brand
+new topic \cite{DBLP:journals/eceasst/VolpatoT15}, but we believe that there is still room for
+improvement.  
 \bibliographystyle{abbrv}
@@
 
-% FIXME remove this
-\listoftodos
-
 \end{document}

### 2016-01-16 lib/reo/reolib.go
bugs fixed in lossysync

@@ -113,8 +113,9 @@ func TimerChannel(in, out Port, t time.Duration, stop Port) {
 			Operation{"write", in.Slave, "read"},
 			Operation{"read", in.Main, "datum"},
 			Operation{"write", c, "datum"},
-			Operation{"debug", c, "[FIFO] BUFFERED"},
+			Operation{"debug", c, "[Timer] BUFFERED"},
 			Operation{"read", timer(t), ""},
+			Operation{"debug", c, "[Timer] TRY TO PUSH"},
 			// following are the syncwrite part
 			Operation{"write", out.Slave, "write"},
 			Operation{"read", out.Slave, ""},
@@ -129,22 +130,40 @@ func TimerChannel(in, out Port, t time.Duration, stop Port) {
 }
 
 func LossysyncChannel(in, out, stop Port) {
+	defer close(stop.Slave)
+	c := make(chan string, 1)
 	for {
-		select {
-		case <-stop.Main:
-			close(stop.Slave)
+		// try to read a data item
+		status := StepExec(
+			stop.Main,
+			Operation{"read", in.Slave, ""},
+			Operation{"write", in.Slave, "read"},
+			Operation{"read", in.Main, "datum"},
+			Operation{"write", c, "datum"},
+			Operation{"debug", c, "[LossySync] data found."},
+		)
+		if !status {
 			return
-		}
-		// FIXME the SyncRead operation may blocks this channel
-		// and hence it cannot be closed by stop Port
-		c := in.SyncRead()
-		select {
-		// try WaitWrite
-		case out.Slave <- "write":
-			out.ConfirmWrite()
-			out.Write(c)
-		default:
-			// do nothing
+		} else {
+			// try to dipense the data
+			select {
+			case <-stop.Main:
+				return
+			case <-time.After(1 * time.Millisecond):
+				logger.Println("[LossySync] data dropped")
+			case out.Slave <- "write":
+				data := <-c
+				status := StepExec(
+					stop.Main,
+					Operation{"read", out.Slave, ""},
+					Operation{"write", out.Main, data},
+				)
+				if !status {
+					return
+				} else {
+					logger.Println("[LossySync] data pushed", data)
+				}
+			}
 		}
 	}
 }
@@ -272,46 +291,7 @@ func MergerChannel(in1, in2, out, stop Port) {
 	wg.Wait()
 }
 
-//func NMergerChannel(in1, in2, out, stop Port) {
[…]

### 2016-01-16 example/expfifo/oracle.go
.

@@ -4,7 +4,6 @@ import "../../lib/sul"
 import "../../lib/reo"
 import "time"
 import "strconv"
-import "fmt"
 
 func GetOracle() *sul.Oracle {
 	o := new(sul.Oracle)
@@ -14,7 +13,6 @@ func GetOracle() *sul.Oracle {
 	for i := 0; i < 11; i++ {
 		o.MidPorts = append(o.MidPorts, "M"+strconv.Itoa(i))
 	}
-	fmt.Println(o.MidPorts)
 
 	o.OutPorts = []string{"B"}
 	o.TimeUnit = 40 * time.Millisecond
@@ -34,12 +32,12 @@ func GetOracle() *sul.Oracle {
 			// Function Channels
 			go reo.ReplicatorChannel(r.MidPorts["M0"], r.MidPorts["M1"], r.MidPorts["M2"], r.StopPorts[2])
 			go reo.FifoChannel(r.MidPorts["M1"], r.MidPorts["M3"], r.StopPorts[3])
-			go reo.TimerChannel(r.MidPorts["M2"], r.MidPorts["M4"], 80*time.Millisecond, r.StopPorts[4])
+			go reo.TimerChannel(r.MidPorts["M2"], r.MidPorts["M4"], 40*time.Millisecond, r.StopPorts[4])
 			go reo.LossysyncChannel(r.MidPorts["M4"], r.MidPorts["M5"], r.StopPorts[5])
-			go reo.ReplicatorChannel(r.MidPorts["M3"], r.MidPorts["M6"], r.MidPorts["M7"], r.StopPorts[6])
-			go reo.ReplicatorChannel(r.MidPorts["M5"], r.MidPorts["M8"], r.MidPorts["M9"], r.StopPorts[7])
-			go reo.SyncdrainChannel(r.MidPorts["M7"], r.MidPorts["M8"], r.StopPorts[8])
-			go reo.ReplicatorChannel(r.MidPorts["M6"], r.MidPorts["M10"], r.MidPorts["M9"], r.StopPorts[9])
+			go reo.ReplicatorChannel(r.MidPorts["M3"], r.MidPorts["M7"], r.MidPorts["M6"], r.StopPorts[6])
+			go reo.MergerChannel(r.MidPorts["M5"], r.MidPorts["M9"], r.MidPorts["M8"], r.StopPorts[7])
[…]

### 2016-01-16 sultest.go

@@ -29,6 +29,7 @@ func main() {
 	// configurations in simulation
 	sul.SetReoDelay(10)
 	sul.SetBound(2)
+	sul.SetEquivBound(4)
 	// logs on/off
 	// sul.CloseLog()
 	sul.CloseReoLog()
@@ -59,18 +60,16 @@ func main() {
 		counter := 0
 		for {
 			var tin sul.InputSeq = sul.InputSeq{
-				&sul.Input{map[string]bool{"A": false, "B": false}, false},
-				&sul.Input{map[string]bool{"A": false, "B": true}, false},
-				&sul.Input{map[string]bool{"A": false, "B": false}, false},
-				&sul.Input{map[string]bool{"A": true, "B": false}, false},
+				&sul.Input{map[string]bool{"A": true}, false},
+				&sul.Input{map[string]bool{"A": false}, true},
+				&sul.Input{map[string]bool{"A": false}, true},
+				&sul.Input{map[string]bool{"A": false}, true},
 			}
 			r := s.SeqSimulate(tin)
 			logger.Println("RESULT:", r, counter)
 			counter++
 
-			if len(r[3]) == 0 {
-				break
-			}
+			break
 		}
 		return
 	}

### 2016-01-16 paper/paper.tex
.

@@
 \subsection{Counter-Examples' Analysis} 
-In our framework, the oracle function $eq$ is used to check the equivalence between hypothesis
-models and blackboxes. It is also responsible for generating counter-examples.
-Generally, as mentioned in \cite{DBLP:journals/iandc/Angluin87,DBLP:conf/sfm/SteffenHM11},
-equivalence query has been proved impossible in blackbox models.
-
 Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not equal to the 2-Timer
 channel. It's easy to find a counter-example $s=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
-according to the hypothesis, the result shoud have been $\rempty$. As mentioned above, we use a
-suffix set $D$ to distinguish different states. The existance of counter-examples shows that the
-current suffix set $D$ is not powerful enough to distinguish all different states. We need to analyze
-the counter-example and in turn append more elements to $D$.
+according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
+find and analyze counter-examples, which is mainly based on \cite{DBLP:conf/sfm/SteffenHM11}.
+
+Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
+a sequence $s$, we use $acc(s)$ to denote the access sequence of $obs\xrightarrow{s}$ and $hq(s)$ to
+denote the corresponding output.
+
+\begin{definition}[Counter-Example]
+  We use $hq$ to denote execution result of the hypothetical Mealy machine, sequence $s$ is called a
+  counter-example iff $mq(s)\neq hq(s)$.
+\end{definition}
+
+Now we consider the reason that lead to existance of counter examples. Since
+the suffix set $D$ is used to distinguish different states, the existance of counter-examples
+shows that the current suffix set $D$ is not powerful enough to distinguish all different states.
+
+Considering a counter example $s$, we have
+\[
+\mbox{MaxSuffix}(s)=\max_d\{s=s'd, mq(acc(s')d)\neq mq(s)\}
+\]
+Since $mq(acc(s))=hq(s)\neq mq(s)$ and $mq(s) = mq(s)$, the existance of such $d$ is easy to prove.
+After appending $d$ in $D$, we explain the closedness will be violated.
+
+The whole L* algorithm can be concluded as follows.
+\begin{algorithm} 
+  \caption{L*} 
+  \label{alg:lstar}
+  \KwIn{Oracle interface $mq,eq$, Input actions $\mathcal{I}$}
+  \KwOut{Observation table $obs$} 
+  $D=I$\;
+  \Repeat{$ce=true$}{
+    $obs$ = BuildTable($mq$, $\mathcal{I}$, $D$)\;
+    $ce=eq(obs)$\;
+    \If {$ce!=true$} {
+      D.append(MaxSuffix(s))\;
+    }
+  }
+  \Return $obs$\; 
+\end{algorithm}
 
@@
 
-We have programmed Reo channels as a new package in Golang. The package is well-written for not only
-formal verification but also practical use.
-
 All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
@@
 
-\subsection{Case Studies}
+\subsection{Case Study}
 A simple example of timed connector is presented to show how L* works.
@@
 
+\begin{figure}[ht]
+  \begin{center}
+    \input{./images/expfifosemantics.tex}
+  \end{center}
+  \caption{Learn Result of The ExpFIFO1 where $n=2,\Sigma=\{a\}$}
+  \label{fig:expfifosemantics}
+\end{figure}
+
+Figure \ref{fig:expfifosemantics} shows the learning result of this example.
+To simplify the graph, we ignore the all the trivial transitions $\frac{\bot,\rnoread}{\rempty}$
+and block transitions. More details of this case can be found in our \emph{github repo}.
+
 \subsection{Performance Optimization}
@@
   \centering
-  \begin{tabular}{l||rrrr}
+  \begin{tabular}{l||rrr}
     \hline
-    & FIFO & Alternator & Gate & ExpFIFO1\\
+    & FIFO & Alternator & Gate \\
     \hline\hline
-    Membership Query(s) & 41.571 & 126.468 & 169.161 &\\
-    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 &\\
-    Total Time(s) & 41.715 & 165.114 & 247.098 &\\
-    Membership Query(\%) & 99.6 & 76.6 & 68.5 &\\
+    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
+    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
+    Total Time(s) & 41.715 & 165.114 & 247.098 \\
+    Membership Query(\%) & 99.6 & 76.6 & 68.5 \\
     \hline
@@
 
-As mentioned above, our implementation in \texttt{Golang} is well-prepared not only for academic use
+Our implementation in \texttt{Golang} is well-prepared not only for academic use
 but also for practical concurrent programming. The following code shows how to compose an alternator
-connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
+connector (see in Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
 can be found in our github repo.

### 2016-01-16 paper/paper.tex
.

@@
 \usepackage{colortbl}
-
+% used to encode algorithms
 \usepackage[linesnumbered, ruled, vlined]{algorithm2e}
+\usepackage{array}
 
@@
 \begin{algorithm} 
-  \caption{BuildTable} 
+  \caption{CloseTable} 
   \label{alg:buildtable}
@@
     \begin{displaymath}
-      \begin{array}{l||ccccc}
+      \begin{array}{l||ccccc||c}
         \hline
-        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T\\
+        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
         \hline\hline
-        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
         \hline
-        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
-        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         \rowcolor[gray]{.9}
-        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty  \\
-        T & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & \mbox{NO MATCH}\\
+        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty \varepsilon & \varepsilon \\
         \hline
@@
     \end{displaymath}
-    \input{./images/hypo.tex}
+    % \input{./images/hypo.tex}
   \end{center}
@@
     \begin{displaymath}
-      \begin{array}{l||ccccc}
+      \small
+      \begin{array}{l||ccccc||c}
         \hline
-        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T\\
+        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
         \hline\hline
-        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         \hline
-        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
-        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty \\
-        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty  \\
-        T & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         \hline
-        a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty \\
-        a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
         \hline
@@
 according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
-find and analyze counter-examples, which is mainly based on \cite{DBLP:conf/sfm/SteffenHM11}.
+find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.
 
@@
 Since $mq(acc(s))=hq(s)\neq mq(s)$ and $mq(s) = mq(s)$, the existance of such $d$ is easy to prove.
-After appending $d$ in $D$, we explain the closedness will be violated.
+After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
+counter-example.
 
@@
   \Repeat{$ce=true$}{
-    $obs$ = BuildTable($mq$, $\mathcal{I}$, $D$)\;
+    $obs$ = CloseTable($mq$, $\mathcal{I}$, $D$)\;
     $ce=eq(obs)$\;
@@
 Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
-Golang\cite{golang}.
-
-Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
-known for its elegant design and impressive efficiency. Moreover, the concurrency model of Golang
-comes from CSP\cite{DBLP:books/ph/Hoare85}. As a channel-based model, CSP shares a similar idea with
-Reo and makes our implementation much more natural.
+Golang\cite{golang}, which is widely known for its elegant design and impressive efficiency.
+Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model,\texttt{Golang} shares many
+similar ideas with Reo, and in turn makes our implementation much more natural.
 
@@
 As shown in Table \ref{tabel:timecost}, time consumption mainly comes from membership queries.
-Since time is involved in our model, it's inevitably that simulation takes time to behave normally.
-Even worse, since our models are treated as blackbox. With no access to inner behaviour of the
-connectors, it's almost impossible to accelerate the simulation process.
-
-Fortunately, there are still other optimization solutions. After reviewing our algorithm, we found
-that simulations on similar sequences were invoked frequently:
+With time involved, every single membership query takes a lot of time inevitably.
+After reviewing our algorithm, we found that simulations on similar sequences were invoked frequently:
 

### 2016-01-17 paper/paper.tex
.

@@
   system implementation. 
-  We first introduce parameterized mealy machine as an operational semantic
-  model for channel-based coordination language Reo. Parameterized mealy machine serves as a bridge
+  We first introduce parameterized Mealy machine(PMM) as an operational semantic
+  model for channel-based coordination language Reo. Parameterized Mealy machine serves as a bridge
   between Reo connectors and mealy machines. With the product operator, complex connectors can be
@@
 
-Distributed real-time embedded system (DRES) is reforming our lives with the name \emph{IoT}, the
-internet of things, wherein systems are usually composed of individual components and a
-\emph{connector}. Such systems could be distributed logically or physically, which
-makes coordination processes even more complicated. In this case, we need to specify these coordination
-processes with so-called \emph{coordination languages}, so that formal techniques can be applied to
+Distributed real-time embedded systems (DRES) are reforming our lives with the
+Internet of Things(IoT), wherein individual components are composed via a
+\emph{connector} to build a system. Such systems could be distributed logically or physically, which
+makes coordination processes even more complicated. In this case, we need to specify the coordination
+processes with \emph{coordination languages}, such that formal techniques can be applied to
 guarantee their reliability.
@@
 
-Formal verification techniques have also been proved applicable in timed connectors, e.g.
-\cite{DBLP:conf/tase/LiCWS15} has shown us a comformance testing method on timed connectors.
-Bounded model checking methods based on SAT solvers were also adapted in
-\cite{DBLP:journals/scp/Kemper12}.
-All these solutions seem practical and impressive, however, a common question is faced by
-most of them: \emph{how to obtain these formal models?}
+Formal verification and validation techniques have also been proved applicable for timed connectors, 
+e.g. a comformance testing framework on timed connectors in \cite{DBLP:conf/tase/LiCWS15}.
+A SAT-based bounded model checking approach was adapted in \cite{DBLP:journals/scp/Kemper12} for
+verifying connectors. Although these solutions are practical and impressive, there is one important
+question faced by most of them: \emph{how to obtain the formal models?}
 
-\emph{Correctness} of connectors is very much related to some low-level implementation details.
-For example, well-writen code may behave dramatically weird with an improper set of concurrency
-primitives. Such things happen frequently in embedded systems with different hardware platforms or
+\emph{Correctness} of connectors is closely related to some low-level implementation details.
+For example, well-written code may behave dramatically weird with an improper set of concurrency
+primitives. Such senarios happen frequently in embedded systems with different hardware platforms or
 operating systems. Consequently, manually modeling an existing connector seems rather unreliable,
@@
 
-To address the problem, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
-automatically extract timed connectors from blackbox models. To achieve this goal, firstly we
-present \emph{parameterized Mealy machine} as a parametierized semantics for timed Reo channels,
-which is able to generate concrete Mealy machines with a given alphabet. Then the $L*$ algorithm
-\cite{DBLP:journals/iandc/Angluin87}
-is adapted and optimized to extract Mealy machines with time action from the \emph{connectors in
-blackboxes}.
+In this paper we address this question by proposing a active learning framework as shown in Figure
+\ref{fig:howto}) to automatically extract timed connector models from blackbox implementations. 
+To achieve this goal, we first introduce \emph{parameterized Mealy machine} as a parametierized
+semantics for timed Reo connectors, which can be transformed intoe concrete Mealy machines with a
+given alphabet. Then the $L*$ algorithm \cite{DBLP:journals/iandc/Angluin87} is adapted and
+optimized to extract Mealy machines with timed action from the connector implementations as
+blackboxes.
 
-The rest of the paper is organized as follows. After this general introduction, in Section
-\ref{sec:preliminaries} we briefly illustrate some basic concepts, including Reo the coordination
-language, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines an
+The rest of the paper is organized as follows: In Section
+\ref{sec:preliminaries} we briefly illustrate some basic concepts, including the coordination
+language Reo, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines an
 operational semantics of Reo, which is used in Section \ref{sec:activelearning} to show how to
-extract Reo models from blackboxes by means of active learning. Finally, in Section
-\ref{sec:experiment}, we discuss the implementation and optimization in \texttt{Golang}.
+extract Reo models from blackboxes by means of active learning. In Section
+\ref{sec:experiment}, we discuss the implementation and optimization of the approach in
+\texttt{Golang}.
 
@@
 \cite{DBLP:journals/mscs/Arbab04}. 
-A Reo model, also called \emph{connector}, provides the protocol
-that formalizes the communication, synchronization and cooperation among the components which
+A coordinator in Reo, also called \emph{connector}, provides the protocol that controls and
+organizes the communication, synchronization and cooperation among the components which
 communicate through the connector. Connectors can be defined without dependence on components,
@@
 In Reo, complex connectors are made up of simpler ones. The atomic connectors are called
-\emph{channels}, and each of them has two \emph{channel ends}. There are two type of channel ends:
-\emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
-channels ends dispense them out of the channel.
+\emph{channels}, and each of them has two \emph{channel ends}. There are two types of channel ends:
+\emph{source} and \emph{sink}. Source channel ends accept data into the channel, while sink
+channel ends dispense data out of the channel.
 
@@
 
-The behavior of some channels are informally described as follows. (Graphical representations
-can be found in Figure \ref{fig:basic}).
+Figure \ref{fig:basic} shows the graphical representation of some basic channel types in Reo, whose
+behavior are described as follows:
 
@@
   \item [-] A \emph{Sync} channel accepts a data item from its source end iff the data item can be
-    dispensed to its sink end simultaneously.
-  \item [-] A \emph{LossySync} channel is always prepared to accept data items. These items will be
-    send to its sink end simutaneously if possible, otherwise they will be dropped.
+    dispensed through its sink end simultaneously.
+  \item [-] A \emph{Lo ssySync} channel is always ready to accept data items. These items will be
+    dispensed through its sink end if possible, otherwise they will be lost.
   \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
-    item through one of its source end iff a data item is also available to accept simultaneously
-    through the other end. Then both items will be dropped.
+    item through one of its source end iff a data item is also available to be accepted
+    simultaneously through the other end. Then both items will be dropped.
   \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
     data item whenever the buffer is empty. 
+  \item [-] A t-timer channel accepts any data item from its source end, and later dispense it to
+    its sink end after a delay of $t$ time units.
+
 \end{itemize}
 
-Channels are attached on component instances or \emph{nodes}. There are three types of nodes:
-\emph{source}, \emph{sink} and \emph{mixed node}, depending on whether all channel ends that
-coincide on a node are source ends, sink ends or both. (see in Figure \ref{fig:node})
+Channels are joint together in \emph{nodes}. There are three types of nodes:
+\emph{source}, \emph{sink} and \emph{mixed} nodes, depending on whether all channel ends that
+coincide on a node are source ends, sink ends or a combination of both.
+(see in Figure \ref{fig:node})
 
@@
 \end{figure}
-
-With definition of more basic channels, it's easy to extend Reo to formalize coordination in
-different areas. In this paper, we take timed Reo\cite{DBLP:conf/sefm/ArbabBBR04} as our formal
-model. Timed Reo includes several timed channels, where the most commonly-used one, called
-\emph{timer}, is also shown in Figure \ref{fig:basic}. A t-timer channel accepts any data item from
-its source end, and later dispense it to its sink end after a delay of t time units.
 
@@
 
-As shown in Figure \ref{fig:reoconnector}, we use a simple example to illustrate how complex
-connectors are constructed and used in coordination. In this example, COM1,COM2 and
-MONITOR are components. With an \emph{alternator} connector, MONITOR can obtain data items from
-COM1 and COM2 alternately. The \emph{alternator} example has been implemented in \texttt{Golang} as
-shown in Section \ref{sec:reolib}.
-Besides, all the connectors are supposed to be \emph{deterministic} hereinafter to meet the
-requirement of active learning algorithm L*.
+Figure \ref{fig:reoconnector} provides a simple example to illustrate how complex
+connectors are constructed and used in coordination. In this example, we have three components
+COM1,COM2 and MONITOR. With an \emph{alternator} connector as shown in Figure
+\ref{fig:reoconnector}, MONITOR can obtain data items from COM1 and COM2 alternately. This example
+has been implemented in \texttt{Golang} as shown in Section \ref{sec:reolib}.
+Besides, all the connectors are supposed to have \emph{deterministic} behavior hereinafter to meet
+the requirement of active learning algorithm L*.
 
@@
 In this work, we use \emph{Mealy machines} to model Reo connectors.
-As an extension of \emph{finite state machine}, Mealy machine was first proposed by George. H. Mealy
-in \cite{George1955A}. Compared with other variants, Mealy machines are designed to model
-reactive systems, where outputs are determined not only by its current state but also the current
-inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means that all
-possible inputs should be acceptable in all states. In other words, if an input is invalid for some
-state, we need to manually define an additional state to describe such exceptions.
+Mealy machine was first proposed by George. H. Mealy in \cite{George1955A} as an extension of finite
+state machine. Compared with other variants, Mealy machines are designed to model
+reactive systems, where outputs of a machine are determined by not only its current state but also
+the current inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means
+that all possible inputs should be acceptable in all states. In other words, if an input is invalid
+for some state, we need to manually define an additional state to describe such exceptions.
 
-Various forms of Mealy machines are defined in different works. 
-Since active automata learning very much depends on the system-under-learn to be deterministic, in
-this paper we formally define a deterministic Mealy machine following
+Various forms of Mealy machines have been defined in the literature. 
+Since active automata learning requires the system-under-learn to be deterministic, in
+this paper we take the deterministic Mealy machine model as defined in 
 \cite{DBLP:conf/sfm/SteffenHM11}.
@@
 \begin{definition}[Mealy machine]
-  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of the following:
+  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of:
   \begin{itemize}
     \item[-] a finite set of states $S$
-    \item[-] a start state (also called initial state) $s_0$ which is an element of $S$
-    \item[-] a finite set called the input alphabet $I$
-    \item[-] a finite set called the output alphabet $O$
-    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping pairs of a
-      state and an input symbol to the corresponding next state.
-    \item[-] an output function $\lambda : S \times I \rightarrow O$ mapping pairs
-      of a state and an input symbol to the corresponding output symbol.
+    \item[-] an initial $s_0\in S$
+    \item[-] a finite set of inputs $I$
+    \item[-] a finite set of outputs $O$
+    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping a pair of a
+      state and an input to the corresponding next state.
+    \item[-] an output function $\lambda : S \times  I \rightarrow O$ mapping a pair
+      of a state and an input to the corresponding output.
   \end{itemize}
@@
 We say that a Mealy machine is \emph{finite} if the set $S$ of states and the set $I$ of inputs are
-finite. Hereinafter, Mealy machines are always supposed to be finite.
+both finite. Hereinafter, Mealy machines are always supposed to be finite in this paper.
 
@@
     teacher.
-  \item[-] \emph{SUL} is an abbreviation of System Under Learn. The name comes from a well-known
-    concept SUT (System Under Test) in software testing. In this case, we take blackbox models as our
-    SULs.
+  \item[-] \emph{SUL} is an abbreviation of System Under Learn. In this paper, we take blackbox
+    models as our SULs.
   \item[-] \emph{CEGAR} indicates Counter-Example Guided Abstraction
     Refinement\cite{DBLP:conf/cav/ClarkeGJLV00}. In active learning, we need counter-examples to
-    guide us on further quries and cover the undistinguished states.
+    guide us on further queries and cover the undistinguished states.
 \end{itemize}
 
-When applying active automata learning on some model, firstly we assume that it should be equivalent
-to some \emph{Mealy machine}, in other words, a deterministic model accepting a finite set of input
-symbols and mapping them to a finite set of output symbols.
+When applying active automata learning on some model, we assume that the model should be equivalent
+to some \emph{Mealy machine}, i.e., a deterministic model accepting a finite set of inputs and
+mapping them to a finite set of outputs.
 
@@
 \begin{itemize}
-  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) The name comes from
-    some grammar-learning papers (e.g. \cite{DBLP:journals/iandc/Angluin87}), where \emph{mq} checks
-    if a word is a member of certain language defined by the given grammar. When it comes to
+  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
+    \cite{DBLP:journals/iandc/Angluin87}) \emph{mq} checks if a word is a member of certain language
+    defined by the given grammar. When it comes to
     automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
@@
     equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
-    \emph{equivalence query} is irrealizable when SUL is a blackbox. So we tactically use membership
-    queries to achieve the approximate results.
+    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
+    approximate results.
 \end{itemize}
@@
 \label{sec:semantics}
-In this section, we illustrate how to transform a timed connector into a Mealy machine with time
+In this section, we illustrate how to transform a timed connector into a Mealy machine with timed
 action.
-Since time is not involed in original Mealy machine, we first discuss how to formalize the time
-dimension in Mealy machine. After that, we present a \emph{parameterized Mealy
+Since time is not involved in original Mealy machine, we first discuss how to formalize the time
+dimension in Mealy machine. After that, we present the notion of \emph{parameterized Mealy
 machine} as a bridge between connectors and Mealy machines.
@@
 \subsection{Time Domain}
-Time is involved in several extensions of Reo. For example, timed
-Reo\cite{DBLP:conf/sefm/ArbabBBR04}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
-Generally, these models are designed to handle real-time behavior where time is defined in
-$\mathbb{R}$. However, we also found some works like \cite{DBLP:journals/fmsd/PrabhakarDM015} where
+Time has been investigated in several extensions of Reo. For example, timed
+Reo\cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/fmoods/MengA07}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
+Generally, these models are designed to handle real-time behavior where time is defined on the
+real number field $\mathbb{R}$. However, there are also found some works like
+\cite{DBLP:journals/fmsd/PrabhakarDM015} where
 rational time indeed  makes things easier. In this paper, we choose the rational number field
-$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behaviors greatly.
+$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behavior greatly.
 
-As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with the
-\emph{t-timer} channels, and the number of these channels are apparently finite. We use
-$t_i\in\mathbb{Q}$ to denote the delays of these timer channels, and now we can define a precision
-function $prec$.
+As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
+of timed channels, and the number of these channels are apparently finite. We use
+$t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
+function $prec$:
 \[
-prec(t_1,\cdots,t_n) = \max_T\{\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
+prec(t_1,\cdots,t_n) = \max_T\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
 \]
-It's easy to prove that such a $T$ is always existing.
+It's easy to prove that such a $T$ always exists.
 
@@
 
-Besides, we're going to add a ``T'' action in Mealy machines. It indicates that a transition
-will take a time unit to finish.
+Besides, we're going to add a ``T'' action in Mealy machines. It indicates that the corresponding
+transition will take one time unit to finish.
 
 \subsection{Parameterized Mealy Machine}
-We present a model named \emph{parameterized Mealy machine} (hereinafter referred to as PMM)
-to model timed connectors. PMM is supposed to behave as a middle representation between Mealy
-machines and timed connectors. Connectors are firstly defined as parameterized Mealy machines, and
-composed by production operator and link operator. Then, concrete Mealy-machine model can be
-generated from the PMM model.
+We present a model named \emph{parameterized Mealy machine}to model timed connectors. PMM is
+supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
+defined as PMMs, and composed by production operator and link operator. Then, concrete Mealy-machine
+model can be generated from the PMM model.
 Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the

### 2016-01-18 paper/paper.tex
.

@@
     \item[-] a finite set of outputs $O$
-    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping a pair of a
-      state and an input to the corresponding next state.
-    \item[-] an output function $\lambda : S \times  I \rightarrow O$ mapping a pair
+    \item[-] an output function $\delta : S \times  I \rightarrow O$ mapping a pair
       of a state and an input to the corresponding output.
+    \item[-] a transition function $\lambda : S \times I \rightarrow S$ mapping a pair of a
+      state and an input to the corresponding successor state.
   \end{itemize}
@@
     sequences.
-  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
+  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
     (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
@@
 $t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
-function $prec$:
+function $prec$ which calculate a gcd-style \emph{maximal time precision}:
 \[
-prec(t_1,\cdots,t_n) = \max_T\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
+prec(t_1,\dots,t_n) = \max\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
 \]
@@
 
-In real systems, the concept \emph{time precision} is well known with other names like ``clock-period''.
-Most of the time, we know the clock-period of some hardware components, even without any idea of its
-structure. With such precision $dt$ given, it's reasonable to assume that all $t$-timers are actually
-$ndt$-timers. In following sections, we'll use $n$-Timers instead.
+In embedded systems, the maximal time precision is also called ``clock-period'', which is the basic
+time unit provided by an oscillator. For example, a widely-used Intel-80C51 microcontroller works
+under the frequency 16Mhz, where the clock-period is $62.5$ns. A resonable assumption comes that
+such a maximal time precision $dt=prec(t_1,\dots,t_n)$ should always be provided to make sure
+different components are able to work together. Then all $t_i$-Timers can be seen as $n_idt$-Timers
+for some $n_i$. In the following sections, we'll use $n_i$-Timers instead.
 
@@
 \subsection{Parameterized Mealy Machine}
-We present a model named \emph{parameterized Mealy machine}to model timed connectors. PMM is
+We present a model named \emph{parameterized Mealy machine} to model timed connectors. PMM is
 supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
@@
 \begin{definition}[Parameterized Mealy Machine]
-  A \emph{Parameterized Mealy Machine} is defined as a 6-tuple $\mathcal{PM}=\langle
-  S, s_0, I, O, \delta, \lambda\rangle$ with a parameter named $\Sigma$ where 
+  A \emph{Parameterized Mealy Machine} with a parameter $\Sigma$ is defined as a 6-tuple
+  $\mathcal{PM}=\langle S, s_0, I, O, \delta, \lambda\rangle$ where 
   \begin{itemize}
-    \item[-] $\Sigma$, the parameter, is a \emph{finite} datum alphabet
-    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
-      states. We use $S(\Sigma)$ to denote the state set.
+    \item[-] The value of $\Sigma$ is a \emph{finite} data set (hereinafter referred as
+      alphabet), e.g. $\{a,b\}$
+    \item[-] $S$ maps an alphabet to a \emph{finite} set of states.
+    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma.s_0\in S(\Sigma)$
     \item[-] $I$ is a finite set of source-ends.
     \item[-] $O$ is a finite set of sink-ends.
-    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
-    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
-      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,I,O)$ to denote the
+    \item[-] $\delta$ maps an alphabet to an \emph{output function}. We use
+      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,O)$ to denote the
       output function.
     \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
-      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow S(\Sigma)$ to denote the transiton
-      function.
+      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow S(\Sigma)$ to denote the
+      transition function.
   \end{itemize}
@@
 
-In the definition above, \emph{Input} and \emph{Output} are used to generate input actions
-and output actions from the corresponding alphabets and source/sink ends. The value of $Input(\Sigma,I,O)$ is
-defined as a set of functions on $I\cup O$ where $\forall f\in Input(\Sigma,I,O)$ and an additional
-\emph{time action} T, we have
+In the definition above, \emph{Input} and \emph{Output} are used to generate the set of input actions
+and output actions from the corresponding alphabets and source/sink ends. $Input(\Sigma,I,O)$ is
+defined as a set of functions on $I\cup O$ and an additional \emph{time action} T,  
+where for all $f\in Input(\Sigma,I,O)\backslash \{T\}$ we have
 \[
-\forall i\in I\backslash\{T\}, f(i)\in \Sigma\cup\{\bot\}\land \forall o\in
-O,f(o)\in\{\rread, \rnoread\}
+\forall i\in I.f(i)\in \Sigma\cup\{\bot\}\land \forall o\in O.f(o)\in\{\rread, \rnoread\}
 \]
-where we use $\rread$ to indicate that an end-sink is ready for write, and $\rnoread$ otherwise. Note
-that a $\bot$ means that there is \emph{no} data items on a source (or sink) end. In the same way,
-$Output(\Sigma,I,O)$ is defined as a set of functions on domain $O$, with an additional symbol
-$\rblock$ indicating an input failure. Similarly, $\forall f\in Output(\Sigma,I,O), f\neq \rblock$
-implies
+where we use $\bot$ to indicate that there is \emph{no} data item on a channel end. 
+Besides, $\rread$ means that a sink end is ready for writing, $\rnoread$ otherwise. 
+In the same way,
+$Output(\Sigma,O)$ is defined as a set of functions on $O$, with an additional symbol
+$\rblock$ indicating an input failure. Similarly, for all $f\in
+Output(\Sigma,O)\backslash\{\rblock\}$,
 \[
-\forall o\in O, f(o)\in \Sigma\cup\{\bot\}
+\forall o\in O. f(o)\in \Sigma\cup\{\bot\}
 \]
@@
   sink-end named $B$, the input actions would be
-  \begin{small}
   \begin{eqnarray*}
-      Input(\{d_0\},\{A\},\{B\}) &=& \{\{A:d_0,B:\rread\},\{A:d_0,B:\rnoread\}, \\
-      & & \{A:\bot,B:\rread\},\{A:\bot,B:\rnoread\},T\}
+    & & Input(\{d_0\},\{A\},\{B\}) \\
+    & = & \{\{A\mapsto d_0,B\mapsto\rread\},\{A\mapsto d_0,B\mapsto\rnoread\}, \\
+    & & \{A\mapsto\bot,B\mapsto\rread\}, \{A\mapsto\bot,B\mapsto\rnoread\},T\}
   \end{eqnarray*}
-  \end{small}
   and its output actions
   \[
-  Output(\{d_0\},\{A\},\{B\}) =\{\{B:d_0\},\{B:\bot\}, \rblock\}
+  Output(\{d_0\},\{A\},\{B\}) =\{\{B\mapsto d_0\},\{B\mapsto \bot\}, \rblock\}
   \]
@@
 
-If there is no data item written to any sink ends, we use $\varnothing$ to denote such an empty
-output. For example, in the case given above, $\{B:\bot\}$ can be briefly rewritten as $\varnothing$.
+We use $\varnothing$ to denote the empty output when no data item is written to any sink end.
+For example, in this case $\{B\mapsto\bot\}$ can be briefly denoted as $\rempty$.
 
-Parameterized Mealy machines can be seen as an abstract form of Mealy machines, which means that we
+Parameterized Mealy machines can be seen as an abstraction of Mealy machines, and we
 still need a convert function between the two models.
@@
     \mathcal{PM}.S(\Sigma), \mathcal{PM}.s_0, \\
-    & & Input(\Sigma, \mathcal{PM}.I), Output(\Sigma, \mathcal{PM}.O), \\
+    & & Input(\Sigma, \mathcal{PM}.I, \mathcal{PM}.O), Output(\Sigma, \mathcal{PM}.O), \\
     & & \mathcal{PM}.\delta(\Sigma), \mathcal{PM}.\lambda(\Sigma),
@@
 
-Now we can use parameterized Mealy Machines to define a new semantics for timed Reo. Here we
-take one asynchronous channel (FIFO1), one asynchronous channel (Sync) and one timed channel (Timer)
-as examples.
+Now we can use PMMs to specify timed Reo. Here we take the asynchronous channel (FIFO1), the
+synchronous channel (Sync) and the timed channel (Timer) as examples. For simplicity, we use $A=\_$
+to indicate that there is no constraint on channel end $A$.
 
-\begin{example}[PMM Semantics of FIFO1 channel]
+\begin{example}[FIFO1]
   \label{example:pmmfifo}
-  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows.
+  The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
   \begin{itemize}
@@
       \begin{displaymath}
+        \small
         \delta(\Sigma)(s,i)=\left\{
         \begin{array}[ht]{ll}
-          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
-          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
-          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
-          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
-          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
-          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
+          \rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
+          \rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
+          \rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
+          \rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
+          \{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
+          \rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
         \end{array}
@@
       \begin{displaymath}
+        \small
         \lambda(\Sigma)(s,i)=\left\{
         \begin{array}[ht]{ll}
-          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
-          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
+          q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
+          q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
+          q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
           q_0 & otherwise \\
@@
 
-Besides, the concrete Mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo},
-where labels of edges are in form of $\frac{input}{output}$.
+Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Figure \ref{fig:pmmfifo},
+where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
+clearance.
 \begin{figure}[ht]
@@
   \end{center}
-  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{a\}$}
+  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{d\}$}
   \label{fig:pmmfifo}
@@
 
-\begin{example}[PMM Semantics of Sync channel]
-  The PMM-based semantics of a Sync channel with a source-end A and a sink-end B can be defined as:
+\begin{example}[Sync]
+  The PMM of a Sync with a source-end A and a sink-end B can be defined as:
   \begin{itemize}
@@
         \begin{array}[ht]{ll}
-          (B:\bot) & s=q_0\land i=(A:\bot,B:\rnoread) \\
-          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
-          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
-          \rblock & s=q_0\land i=(A:d,B:\rnoread) \\
+          \rempty & i=\{A\mapsto\bot,B\mapsto\rnoread\} \\
+          \{B\mapsto d\} & i=\{A\mapsto d,B\mapsto\rread\}\\
+          \rblock & i=\{A\mapsto\bot,B\mapsto\rread\} \\
+          \rblock & i=\{A\mapsto d,B\mapsto\rnoread\} \\
         \end{array}
@@
 
-\begin{example}[PMM Semantics of n-Timer channel]
-  Considering an n-Timer channel with a source-end A and a sink-end B, we define its PMM-based
-  semantics as:
+\begin{example}[n-Timer]
+  The PMM of an n-Timer with a source-end A and a sink-end B can be defined as:
   \begin{itemize}
@@
       \begin{displaymath}
+        \small
         \delta(\Sigma)(s,i)=\left\{
         \begin{array}[ht]{ll}
-          (B:d) & s=q_{n,d}\land i=(A:d,B:\rread)\\
-          \rblock & s=q_{n,d}\:\land \\
-          & (i=T\lor i=(A:\_,B:\rnoread) \\
-          \rblock & s=q_{j,d}\land 1 \leq j < n\land \\
-          & (i=(A:\_,B:\rread)\lor \\
-          & i=(A:d,B:\_))\\
-          (B:\bot) & otherwise\\
+          \{B\mapsto d\} & s=q_{n,d}\land i=\{A\mapsto \_,B\mapsto \rread\}\\
+          \rblock & s=q_{n,d}\land \\
+          & (i=T\lor i=\{A\mapsto \_,B\mapsto \rnoread\}) \\
+          \rblock & s=q_{j,d}\land 0 \leq j < n\land \\
+          & (i=\{A\mapsto \_,B\mapsto \rread\}\lor \\
+          & i=\{A\mapsto d,B\mapsto \_\})\\
+          \rempty & otherwise\\
         \end{array}
@@
       \begin{displaymath}
+        \small
         \lambda(\Sigma)(s,i)=\left\{
         \begin{array}[ht]{ll}
-          q_{j+1,d} & s=q_{j,d}\land i=T\land0 < j < n\\
-          q_0 & s=q_{n,d}\land i=(A:\bot,B:\rread) \\
-          q_{0,d} & s=q_{n,d'}\land i=(A:d,B:\rread) \\
-          q_{0,d} & s=q_0 \land i=(A:d,B:\_) \\
+          q_{0,d} & s=q_0 \land i=\{A\mapsto d,B\mapsto \_\} \\
+          q_{j+1,d} & s=q_{j,d}\land i=T\land0 \leq j < n\\
+          q_0 & s=q_{n,d}\land i=\{A\mapsto \bot,B\mapsto \rread\} \\
+          q_{0,d'} & s=q_{n,d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
+          q_0 & s=q_{n,d} \land i=T \\
           s & otherwise \\
@@
 
-Similarly, we can use parameterized mealy machines to define the semantics of other basic timed Reo
-channels. Now we're going to show how to compose these channels into complicated connectors.
+Similarly, we can use PMMs to describe the behavior of other basic timed Reo
+channels. Now we show how to compose these channels into more complicated connectors.
 
-\begin{definition}[Production Operator]
-  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines as,
+\begin{definition}[Production]
+  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines
   \[
@@
   \label{alg:buildtable}
+  \small
   \KwIn{Oracle interface $mq$, Input actions $\mathcal{I}$, suffix set $D$}

### 2016-01-18 paper/paper.tex
.

@@
 \newcommand{\rempty}[0]{\varnothing}
+
+\newcommand{\OUT}[0]{\mbox{OUT}}
+\newcommand{\IN}[0]{\mbox{IN}}
 
@@
     dispensed through its sink end simultaneously.
-  \item [-] A \emph{Lo ssySync} channel is always ready to accept data items. These items will be
+  \item [-] A \emph{LossySync} channel is always ready to accept data items. These items will be
     dispensed through its sink end if possible, otherwise they will be lost.
@@
 both finite. Hereinafter, Mealy machines are always supposed to be finite in this paper.
-
-A Mealy machine is in some state $q\in S$ is always ready for inputs at any time. If an input symbol
-$i\in I$ is provided, the Mealy machine generates output $o=\lambda(q,i)$ and jumps to state
-$q'=\delta(q,i)$. Such an edge is also denoted as $q\xrightarrow[]{i/o}q'$.
 
@@
 \begin{definition}[Production]
-  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines
+  The production operator \emph{prod} of two parameterized Mealy machines
   \[
-  prod(PM_1,PM_2)=PM_3
+  \mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)\mbox{ if }\mathcal{PM}_2.O\cap
+  \mathcal{PM}_1.I=\varnothing
   \]
-  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
+  is defined as follows.
   \begin{itemize}
-  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
-    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
-    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
+  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}_1.S(\Sigma)\times \mathcal{PM}_2.S(\Sigma)$
+    \item[-] $\mathcal{PM}'.I=(\mathcal{PM}_1.I\cup \mathcal{PM}_2.I)\backslash \mathcal{PM}_1.O$
+    \item[-] $\mathcal{PM}'.O=(\mathcal{PM}_1.O\cup \mathcal{PM}_2.O)\backslash \mathcal{PM}_2.I$
   \end{itemize}
-  \emph{(Here we assume that sink ends of $PM_1$ can be connected to source ends $PM_2$, but not
+  \emph{(Here we assume that sink ends of $\mathcal{PM}_1$ can be connected to source ends $\mathcal{PM}_2$, but not
   vise versa)}
   \begin{itemize}
-    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
-    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
+    \item[-] $\mathcal{PM}'.s_0=(\mathcal{PM}_1.s_0, \mathcal{PM}_2.s_0)$
+    \item[-] $\forall\Sigma. \mathcal{PM}'.\delta(\Sigma)((s_1,s_2), i)=$
       \begin{displaymath}
@@
         \begin{array}[ht]{ll}
-          (Out_1 + Out_2)\downarrow_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
+          (Out_1 \cup Out_2)\downarrow_{\mathcal{PM}'.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
           \rempty & i = T \\
@@
       \begin{itemize}
-        \item[*] $In_1 = i\downarrow_{PM_1.I}$
-        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
-        \item[*] $In_2 = (Out_1 + i)\downarrow_{PM_2.I}$
-        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
+        \item[*] $In_1 = i\downarrow_{\mathcal{PM}_1.I}$
+        \item[*] $Out_1 = \mathcal{PM}_1.\delta(\Sigma)(s_1,In_1)$
+        \item[*] $In_2 = (Out_1 \cup i)\downarrow_{\mathcal{PM}_2.I}$
+        \item[*] $Out_2 = \mathcal{PM}_2.\delta(\Sigma)(s_2,In_2)$
       \end{itemize}
-    \item[-] $\forall\Sigma, PM_3. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
+    \item[-] $\forall\Sigma. \mathcal{PM}'. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
       where we have
       \begin{itemize}
-        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
-        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
+        \item[*] $s_1' = \mathcal{PM}_1.\lambda(\Sigma)(s_1,In_1)$
+        \item[*] $s_2' = \mathcal{PM}_2.\lambda(\Sigma)(s_2,In_2)$
       \end{itemize}
@@
 
-The idea in \emph{production} is quite simple. The output of $PM_1$ would be provided as part of the
-input of $PM_2$. Time actions T is only executed simutaneously between $PM_1$ and $PM_2$.
+The idea in \emph{production} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
+input of $\mathcal{PM}_2$. Time actions T is only executed simutaneously between $\mathcal{PM}_1$ and $\mathcal{PM}_2$.
 
-As mentioned in the notation above, we cannot connect a sink end of $PM_2$ to a source end of
-$PM_1$, which makes it difficult to construct connectors like alternator in Figure
+As mentioned in the notation above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
+$\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Figure
 \ref{fig:reoconnector}. To address the problem, we define a \emph{link} operation to connect sink
@@
 
-\begin{definition}[Link Operator]
-  The \emph{link} operation constructs connector by connecting a sink end $OUT$ to a source end $IN$
+\begin{definition}[Link]
+  The \emph{link} operator constructs connector by connecting a sink end $\OUT$ to a source end $\IN$
   within the same connector.   
   \[
-  PM' = link(PM, OUT, IN)
+  \mathcal{PM}' = link(\mathcal{PM}, \OUT, \IN)
   \]
-  Here we asuume that $IN\in PM.I$ and $OUT\in PM.O$.
+  Here we assume that $\IN\in \mathcal{PM}.I$ and $\OUT\in \mathcal{PM}.O$.
 
   \begin{itemize}
-  	\item[-] $\forall\Sigma, PM'.S(\Sigma)=PM.S(\Sigma)$
-    \item[-] $PM'.I=PM.I-\{IN\}$
-    \item[-] $PM'.O=PM.O-\{OUT\}$
-    \item[-] $PM'.s=PM.s$
-    \item[-] $\forall\Sigma, i\in Input(\Sigma,PM'.I,PM'.O)$, $PM'.\delta(\Sigma)(s, i)=$
-      \begin{equation}
-        \label{equ:existd}
-        PM.\delta(\Sigma)(s,T)\downarrow_{PM'.O}
-      \end{equation}
-      if $i=T$. When $i$ is a non-time action, we need to check whether there's a data item
-      $d\in\Sigma$
-      satisfies
+  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}.S(\Sigma)$
+    \item[-] $\mathcal{PM}'.I=\mathcal{PM}.I\backslash\{\IN\}$
+    \item[-] $\mathcal{PM}'.O=\mathcal{PM}.O\backslash\{\OUT\}$
+    \item[-] $\mathcal{PM}'.s_0=\mathcal{PM}.s_0$
+    \item[-] $\forall\Sigma, i\in
+      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
+      \begin{displaymath}
+        \small
+        \left\{
+        \begin{array}[h]{lr}
+          \rempty & i=T \\
+          \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
+          \rblock & otherwise \\
+        \end{array}
+        \right.
+      \end{displaymath}
+      where the condition (*) is defined as
       \[
-      PM.\delta(\Sigma)(s,i\cup\{IN:d\})\downarrow_{OUT} = d
+      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})(\OUT)=d
       \]
-      if the formula is satisfied, we have $PM'.\delta(\Sigma)(s, i)=$
-      \[
-      PM.\delta(\Sigma)(s,i\cup\{IN:d\})\downarrow_{PM'.O}
-      \]
-      otherwise $PM'.\delta(\Sigma)(s, i)=\rblock$
-    \item[-] $\forall\Sigma, i\in Input(\Sigma,PM'.I,PM'.O).'$ the transition
-      function can be defined as $PM.\lambda(\Sigma)(s,i)=$
+    \item[-] $\forall\Sigma, i\in
+      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
       \begin{displaymath}
+        \small
+        \mathcal{PM}.\lambda(\Sigma)(s,i)=
         \left\{
-        \begin{array}[ht]{ll}
-          PM.\lambda(\Sigma,T) & i=T \\
-          PM.\lambda(\Sigma,i\cup\{IN:d\}) & \exists d\in\Sigma \mbox{ satisfes Equation
-          \ref{equ:existd}} \\
+        \begin{array}[ht]{lr}
+          \mathcal{PM}.\lambda(\Sigma,T) & i=T \\
+          \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN:d\}) & (*)\\
           s & otherwise \\
@@
 
-With \emph{link} and \emph{prop} defined, complex connectors can be formed by simple channels in
+With \emph{link} and \emph{prop} defined, a connector can be formed by simpler ones in
 form of \emph{parameterized Mealy machines}. It will be transformed into a concrete Mealy machine
-later once the alphabet $\Sigma$ is provided.
+later, once the alphabet $\Sigma$ is provided.
 

### 2016-01-19 paper/paper.tex
.

@@
 \label{sec:activelearning}
-In this section, we show how to use L* algorithm to extract models from blackboxes in  3 steps:
-\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{checking hypothesis}. Besides,
-we assume that input symbols and output symbols of the blackbox have been provided as $\mathcal{I}$
+In this section, we use L* algorithm to extract Reo coordinators from blackbox
+implementations in 3 steps:
+\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
+Here the input symbols and output symbols of the blackbox are supposed to be provided as $\mathcal{I}$
 and $\mathcal{O}$.
@@
 \subsection{Observation Table}
-As mentioned above, membership queries provide us information with the form $mq(s)=o$, where $s$ is
-an input sequence in $\Sigma^{+}$. Now the question is, \emph{how to find the connection between
-such query results and Mealy machines?}
+Results of membership queries come out as $mq(s)=o$, where $s\in\mathcal{I}+$.
+Now the question is, \emph{how to find the connection betweensuch query results and Mealy machines?}
 
@@
 
-Different access sequences may lead to similar states. For example, a 2-Timer channel will dispense
-any accepted data item in 2 time units. After that, the state of this channel is exactly same as its
-initial state. Here \emph{suffixes} are used to distinguish different states as shown in the
-following definition, where $D$ is initialized as $\mathcal{I}$. Under such a suffix set, two states
-are considered different only when they have different one-step behaviors.
-
+Different access sequences may lead to similar states. Here we use \emph{suffixes} set $D$ to
+distinguish states where $D\subseteq \mathcal{I}^+$ is initialized as $\{d=\{i\}|i\in\mathcal{I}\}$. 
 \begin{definition}[Equivalence under Suffixes]

### 2016-01-19 paper/paper.tex
.

@@
     \item[-] output function
+      \begin{small}
         \begin{displaymath}
-        \small
           \delta(\Sigma)(s,i)=\left\{
@@
         \end{displaymath}
+      \end{small}
     \item[-] transition function
+      \begin{small}
         \begin{displaymath}
-        \small
           \lambda(\Sigma)(s,i)=\left\{
@@
         \end{displaymath}
+      \end{small}
   \end{itemize}
@@
         \end{displaymath} 
+      \end{small}
     \item[-] transition function
+      \begin{small}
         \begin{displaymath}
-        \small
           \lambda(\Sigma)(s,i)=\left\{
@@
       Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
+      \begin{small}
         \begin{displaymath}
-        \small
           \left\{
@@
         \end{displaymath}
+      \end{small}
       where the condition (*) is defined as
@@
       Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
+      \begin{small}
         \begin{displaymath}
-        \small
           \mathcal{PM}.\lambda(\Sigma)(s,i)=
@@
 \emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
-Here the input symbols and output symbols of the blackbox are supposed to be provided as $\mathcal{I}$
-and $\mathcal{O}$.
+here the input and output symbols of the blackbox are provided as $\mathcal{I}$ and $\mathcal{O}$,
+and the blackbox implementation is supposed to be equivalent to a Mealy machine where all states are
+reachable.
 
 \subsection{Observation Table}
-Results of membership queries come out as $mq(s)=o$, where $s\in\mathcal{I}+$.
-Now the question is, \emph{how to find the connection betweensuch query results and Mealy machines?}
+\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, is used to construct
+a hypothetical Mealy machine from results membership queries.
 
-Generally, Mealy machines are composed of \emph{states} and \emph{transitions}.
-Provided with a Mealy machine $m$, any input sequence in $m.I^+$ leads to a unique state. 
-Such a sequence is called an \emph{access sequence} of this state.
-Particularly, we use $\varepsilon$, the \emph{empty sequnce}, to denote the initial state.
-Similarly, if a blackbox model has the same bahavior with a Mealy machine, we can use access
-sequences to label its states and, in the same way, input actions to label its transitions.
-For example, we consider a Mealy machine which is staying in some state labelled by $s$. With an
-action $a$ provided, the Mealy machine will jump to a new state labelled by $s'=sa$ and generate an
-output $mq(sa)$.
+Generally, a Mealy machines is determined by its \emph{states} and \emph{transitions}.
+As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
+after execution of $s$. Similarly, for all $a\in\mathcal{I}$, $sa$ indicates the successor
+state of $s$ after execution of $a$.
+However, under such notations, there are \emph{infinite} number of states where most are
+reduplicate.
 
-Different access sequences may lead to similar states. Here we use \emph{suffixes} set $D$ to
-distinguish states where $D\subseteq \mathcal{I}^+$ is initialized as $\{d=\{i\}|i\in\mathcal{I}\}$. 
-\begin{definition}[Equivalence under Suffixes]
+States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
+\mathcal{I}^*$, the corresponding of $s_1$ and $s_2$ are exactly the same iff $\forall d\in
+\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
+alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
+\begin{definition}[$D$-Equivalence]
   provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
-  the corresponding states of $s_1$ and $s_2$ are equivalent under $D$ (denoted as $s_1\sim_D s_2$)
+  the corresponding states of $s_1$ and $s_2$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
   iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
 \end{definition}
+\begin{definition}[Access Sequence]
+  Given an input sequence $s$, we define the access sequence of $s$ as
+  \[
+  acc(s,D)=\min\{s'\in\mathcal{I}^*|s'\sim_D s\}
+  \]
+\end{definition}
 
-Since all this \emph{inputs} and \emph{outputs} can be observed outside the
-model, we can use the same notations to describe a black box as a hypothetical Mealy machine.
-Following this idea, \emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87},
-shows a tabular form of such hypothetical models. In observation tables, rows represent states with
-label of their access sequences and columns are labelled with suffixes. Successors of a state $s$ is,
-intuitively, denoted as extended access sequences $sa$ where $a$ is a single input action. 
-A cell with column-label $d$ and row-label $s$ should contain the value $mq(sd)$. Algorithm
-\ref{alg:buildtable} shows how to build such an observation table.
+Formally, an observation table is defined as a tuple $(S,D)$ where $S\subset\mathcal{I}^*$ indicates
+the access sequences of states and $D\subset\mathcal{I}^*$ indicates the suffixes. Its
+tabular form can be found in Figure \ref{fig:hypo}. In such tables, columns are labelled with
+$d\in D$, and rows are labelled with input sequences. Rows are divided into two parts. The upper
+part, labelled with $s\in S$, shows the states in current hypothesis (in form of access sequences).
+The lower part, labelled with $sa$ (where $s\in S,a\in\mathcal{I}$) indicates all the transitions
+from $S$. A cell with row label $s$ and column label $d$ is filled with $mq(sd)$.
+
+An observation table $(S,D)$ is \emph{closed} if 
+\[
+\forall s\in S,a\in\mathcal{I}.\exists s'\in S. sa\sim_D s'
+\]
+
+Algorithm \ref{alg:buildtable} shows how to build an closed observation table.
 
@@
 Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
-We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$ and the alphabet
+We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$, and the alphabet
 is $\{a\}$. We briefly denote $\{A:a,B:\rnoread\}$ and other input/output actions in form of
@@
 Then we will explore all the access sequences in $unclosed$ and calculate its successors. Here the
-$unclosed$ set consists of access sequences that has no equivalent fellow with less length. 
+$unclosed$ set consists of access sequences that has no equivalent fellow in $S$. 
 For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
@@
   \begin{center}
+    \begin{small}
       \begin{displaymath}
-      \small
         \begin{array}{l||ccccc||c}
@@
       \end{displaymath}
+    \end{small}
   \end{center}
@@
 \subsection{Counter-Examples' Analysis} 
-Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not equal to the 2-Timer
-channel. It's easy to find a counter-example $s=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
+Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not the 2-Timer
+channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
 according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
@@
 Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
-a sequence $s$, we use $acc(s)$ to denote the access sequence of $obs\xrightarrow{s}$ and $hq(s)$ to
-denote the corresponding output.
+a sequence $s$, we use $hq(obs,s)$ to denote the execution result of $obs$ under the input sequence
+$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $a$ is the last element of $s$ and $s=s'a$.
 
 \begin{definition}[Counter-Example]
-  We use $hq$ to denote execution result of the hypothetical Mealy machine, sequence $s$ is called a
-  counter-example iff $mq(s)\neq hq(s)$.
+  sequence $s$ is called a counter-example of $obs$ iff $mq(s)\neq hq(obs,s)$.
 \end{definition}
@@
 
-Considering a counter example $s$, we have
+Considering a counter example $s$, we define the function MaxSuffix($s,obs$) as
 \[
-\mbox{MaxSuffix}(s)=\max_d\{s=s'd, mq(acc(s')d)\neq mq(s)\}
+\max\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
 \]
-Since $mq(acc(s))=hq(s)\neq mq(s)$ and $mq(s) = mq(s)$, the existance of such $d$ is easy to prove.
 After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
@@
 improvement.
-\bibliographystyle{abbrv}
+
+\bibliographystyle{IEEEtran}
+% \bibliography{IEEEabrv, bib}
 \bibliography{bib}

### 2016-01-19 paper/paper.tex
.

@@
 % finally no todos should exist in this draft
-% \usepackage[textsize=tiny]{todonotes}
+\usepackage[textsize=tiny]{todonotes}
 
@@
   We first introduce parameterized Mealy machine(PMM) as an operational semantic
-  model for channel-based coordination language Reo. Parameterized Mealy machine serves as a bridge
-  between Reo connectors and mealy machines. With the product operator, complex connectors can be
-  constructed by joining basic channels and transformed into mealy machines. Moreover, we adapt L*,
-  a well-known learning algorithm, to timed connectors (in the form of mealy machines). The new
-  algorithm has shown its efficiency in multiple case studies. 
-  Implementations of this framework is provided as a package in \texttt{Golang}.
+  model for channel-based coordination language Reo. PMM serves as a bridge
+  between Reo connectors and Mealy machines. With the product operator, complex connectors can be
+  constructed by joining basic channels and the PMM of connectors can be transformed into Mealy
+  machines. Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in the form
+  of Mealy machines). The new algorithm has shown its efficiency in multiple case studies. 
+  This framework has been implemented as a package in \texttt{Golang}.
 \end{abstract}
@@
 Distributed real-time embedded systems (DRES) are reforming our lives with the
-Internet of Things(IoT), wherein individual components are composed via a
-\emph{connector} to build a system. Such systems could be distributed logically or physically, which
+Internet of Things(IoT), wherein individual components are composed via \emph{connectors} 
+to build systems. Such systems could be distributed logically or physically, which
 makes coordination processes even more complicated. In this case, we need to specify the coordination
@@
 
-\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, by which
-coordination process in DRES can be depicted clearly and intuitively. Different formal
-semantics are proposed to specify the behavior of timed Reo.
-For example, in \cite{DBLP:conf/tase/Meng12}, a UTP-based
-(\emph{Unifying Theories of Programming}) semantics is provided to verify connectors as
-\emph{designs}. An operational semantics based on \emph{constraint automata} was raised by Baier et
-al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the properties of timed connectors.
+\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, which can be used
+to describe the coordination process in DRES clearly and intuitively. Different formal
+semantics have been proposed to specify the behavior of timed Reo.
+For example, an operational semantics based on \emph{timed constraint automata} was raised by Baier et
+al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
+properties of timed connectors.
+In \cite{DBLP:conf/tase/Meng12}, a UTP design model was proposed to specify the behavior of timed
+connectors..
 
 Formal verification and validation techniques have also been proved applicable for timed connectors, 
-e.g. a comformance testing framework on timed connectors in \cite{DBLP:conf/tase/LiCWS15}.
+e.g. a comformance testing framework on timed connectors has been proposed in \cite{DBLP:conf/tase/LiCWS15}.
 A SAT-based bounded model checking approach was adapted in \cite{DBLP:journals/scp/Kemper12} for
@@
 For example, well-written code may behave dramatically weird with an improper set of concurrency
-primitives. Such senarios happen frequently in embedded systems with different hardware platforms or
-operating systems. Consequently, manually modeling an existing connector seems rather unreliable,
-even with reference to its source code.
-
-As a branch of \emph{machine learning} technique, active learning offers a way to obtain models from
-low-level models. Works in \cite{DBLP:journals/mt/Daelemans10, DBLP:journals/iandc/Angluin87,
-DBLP:conf/fase/RaffeltS06} shows interesting examples where active learning is used to extract
-\emph{Mealy machines} or \emph{regular languages} without time domain.
+primitives. Such scenarios happen frequently in embedded systems with different hardware platforms or
+operating systems. Consequently, manually extracting a proper model for an existing connector
+implementation seems rather unreliable, even with reference to its source code.
+
+As a branch of \emph{machine learning} technique, active learning offers a means to obtain
+high-level models from low-level models. Works in \cite{de2010grammatical,
+DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06} show interesting examples where active
+learning is used to extract \emph{Mealy machines} or \emph{regular languages} without time domain.
 
@@
 In this paper we address this question by proposing a active learning framework as shown in Figure
-\ref{fig:howto}) to automatically extract timed connector models from blackbox implementations. 
-To achieve this goal, we first introduce \emph{parameterized Mealy machine} as a parametierized
-semantics for timed Reo connectors, which can be transformed intoe concrete Mealy machines with a
+\ref{fig:howto} to automatically extract timed connector models from blackbox implementations. 
+To achieve this goal, we first introduce \emph{parameterized Mealy machine} as a parameterized
+semantics for timed Reo connectors, which can be transformed to concrete Mealy machines with a
 given alphabet. Then the $L*$ algorithm \cite{DBLP:journals/iandc/Angluin87} is adapted and
@@
 \ref{sec:experiment}, we discuss the implementation and optimization of the approach in
-\texttt{Golang}.
+\texttt{Golang}. Finally, Section VI concludes the paper.
 
@@
   \item [-] A \emph{LossySync} channel is always ready to accept data items. These items will be
-    dispensed through its sink end if possible, otherwise they will be lost.
+    dispensed through its sink end simultaneously if possible, otherwise they will be lost.
   \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
@@
     its sink end after a delay of $t$ time units.
-
+    \footnote{Here the interpretation of t-Timer is a bit different as in other works like
+    \cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/tase/Meng12}, but we can easily transform between the
+    two kinds of behavior by composing with some other basic channels.}
 \end{itemize}
@@
   \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
-    \cite{DBLP:journals/iandc/Angluin87}) \emph{mq} checks if a word is a member of certain language
+    \cite{DBLP:journals/iandc/Angluin87}, \emph{mq} checks if a word is a member of certain language
     defined by the given grammar. When it comes to
@@
 Generally, these models are designed to handle real-time behavior where time is defined on the
-real number field $\mathbb{R}$. However, there are also found some works like
+real number field $\mathbb{R}$. However, there are also some works like
 \cite{DBLP:journals/fmsd/PrabhakarDM015} where
@@
 As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
-of timed channels, and the number of these channels are apparently finite. We use
+of timed channels. We use
 $t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
@@
 time unit provided by an oscillator. For example, a widely-used Intel-80C51 microcontroller works
-under the frequency 16Mhz, where the clock-period is $62.5$ns. A resonable assumption comes that
+under the frequency 16Mhz, where the clock-period is $62.5$ns. A reasonable assumption comes that
 such a maximal time precision $dt=prec(t_1,\dots,t_n)$ should always be provided to make sure
 different components are able to work together. Then all $t_i$-Timers can be seen as $n_idt$-Timers
-for some $n_i$. In the following sections, we'll use $n_i$-Timers instead.
+for some $n_i$ and we use $n_i$-Timers instead in the following sections.
 
@@
 supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
-defined as PMMs, and composed by production operator and link operator. Then, concrete Mealy-machine
-model can be generated from the PMM model.
+defined as PMMs, and composed by \emph{product} and \emph{link} operators. Then, concrete
+Mealy-machine model can be generated from the PMM model.
 Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the
@@
 
-\begin{definition}[Production]
-  The production operator \emph{prod} of two parameterized Mealy machines
+\begin{definition}[Product]
+  The product operator \emph{prod} of two PMMs
   \[
@@
 The idea in \emph{production} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
-input of $\mathcal{PM}_2$. Time actions T is only executed simutaneously between $\mathcal{PM}_1$ and $\mathcal{PM}_2$.
+input of $\mathcal{PM}_2$. Time actions T is only executed simultaneously between $\mathcal{PM}_1$ and $\mathcal{PM}_2$.
 
@@
 \emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, is used to construct
-a hypothetical Mealy machine from results membership queries.
+a hypothetical Mealy machine from the results of membership queries.
 
@@
 \]
+
+From a closed observation we can construct a hypothetical Mealy machine in a straight-forward way.
+The Mealy machine $\mathcal{H}=\langle S,s_0,\mathcal{I},\mathcal{O},\delta,\lambda\rangle$ is
+constructed from $obs$ as follows:
+\begin{itemize}
+  \item[-] Every state in $S$ corresponds to an input sequence in $obs.S$
+  \item[-] $s_0$ corresponds to the empty sequence $\varepsilon$
+
+    \emph{(we use input sequences to indicate their corresponding states in following parts)}
+    \todo{define the empty sequence}
+  \item[-] $\delta(s,a)=mq(sa)$
+  \item[-] $\lambda(s,a)=acc(sa,obs.D)$
+\end{itemize}
 
@@
 we will also try to improve our algorithm to handle non-deterministic behaviors. This is not a brand
-new topic \cite{DBLP:journals/eceasst/VolpatoT15}, but we believe that there is still room for
+new topic \cite{DBLP:conf/isola/VolpatoT14}, but we believe that there is still room for
 improvement.
 
-\bibliographystyle{IEEEtran}
-% \bibliography{IEEEabrv, bib}
+\section*{Acknowledgments}
+The work was partially supported by the National Natural Science Foundation of China under grant no.
+61202069, 61272160 and 61532019, and Research Fund for the Doctoral Program of Higher Education of
+China under grant no. 20120001120103.
+
+\bibliographystyle{abbrv}
 \bibliography{bib}

### 2016-01-20 paper/paper.tex
.

@@
 % finally no todos should exist in this draft
-\usepackage[textsize=tiny]{todonotes}
+% \usepackage[textsize=tiny]{todonotes}
 
@@
   of Mealy machines). The new algorithm has shown its efficiency in multiple case studies. 
-  This framework has been implemented as a package in \texttt{Golang}.
+  This framework has been implemented in \texttt{Golang}.
 \end{abstract}
@@
 primitives. Such scenarios happen frequently in embedded systems with different hardware platforms or
-operating systems. Consequently, manually extracting a proper model for an existing connector
+operating systems. Consequently, manually extracting a proper model from an existing connector
 implementation seems rather unreliable, even with reference to its source code.
@@
 
-Various forms of Mealy machines have been defined in the literature. 
+Various forms of Mealy machines have been defined in the
+literature\cite{George1955A,DBLP:journals/jcss/Broy14,DBLP:conf/sfm/SteffenHM11}. 
 Since active automata learning requires the system-under-learn to be deterministic, in
@@
     \item[-] a finite set of states $S$
-    \item[-] an initial $s_0\in S$
+    \item[-] an initial state $s_0\in S$
     \item[-] a finite set of inputs $I$
@@
 \label{sec:semantics}
+
 In this section, we illustrate how to transform a timed connector into a Mealy machine with timed
@@
 
-With \emph{link} and \emph{prop} defined, a connector can be formed by simpler ones in
-form of \emph{parameterized Mealy machines}. It will be transformed into a concrete Mealy machine
-later, once the alphabet $\Sigma$ is provided.
+With \emph{link} and \emph{prop} defined, connectors can be constructed by simpler ones in
+form of PMMs. It will be transformed into a concrete Mealy machine later, once the alphabet $\Sigma$
+is provided.
 
@@
 \subsection{Observation Table}
-\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, is used to construct
-a hypothetical Mealy machine from the results of membership queries.
-
-Generally, a Mealy machines is determined by its \emph{states} and \emph{transitions}.
+\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
+hypothetical Mealy machines from the results of membership queries.
+
+Mealy machines are composed of \emph{states} and \emph{transitions}.
 As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
-after execution of $s$. Similarly, for all $a\in\mathcal{I}$, $sa$ indicates the successor
-state of $s$ after execution of $a$.
-However, under such notations, there are \emph{infinite} number of states where most are
+after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
+state of $s$ after executing $a$.
+However, under such notations, there are \emph{infinite} number of states, among which most are
 reduplicate.
@@
 States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
-\mathcal{I}^*$, the corresponding of $s_1$ and $s_2$ are exactly the same iff $\forall d\in
+\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
 \mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
@@
 \begin{definition}[$D$-Equivalence]
-  provided with two access sequences $s_1,s_2$ and a set of suffixes $D\subset\mathcal{I}^+$, we say
-  the corresponding states of $s_1$ and $s_2$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
-  iff $\forall d\in D, mq(s_1d) = mq(s_2d)$.
+  provided with a set of suffixes $D\subset\mathcal{I}^+$, we say the corresponding states of
+  $s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
+  iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
 \end{definition}
-\begin{definition}[Access Sequence]
-  Given an input sequence $s$, we define the access sequence of $s$ as
+
+Now we use \emph{access sequence} to describe the states. Given an input sequence $s$, the access
+sequence of $s$ is defined as
 \[
@@
 \]
-\end{definition}
-
-Formally, an observation table is defined as a tuple $(S,D)$ where $S\subset\mathcal{I}^*$ indicates
-the access sequences of states and $D\subset\mathcal{I}^*$ indicates the suffixes. Its
-tabular form can be found in Figure \ref{fig:hypo}. In such tables, columns are labelled with
-$d\in D$, and rows are labelled with input sequences. Rows are divided into two parts. The upper
-part, labelled with $s\in S$, shows the states in current hypothesis (in form of access sequences).
-The lower part, labelled with $sa$ (where $s\in S,a\in\mathcal{I}$) indicates all the transitions
-from $S$. A cell with row label $s$ and column label $d$ is filled with $mq(sd)$.
+
+Formally, an observation table (see in Figure \ref{fig:hypo}) is determined by a tuple $(S,D)$ where
+$S\subset\mathcal{I}^*$ is a set of the access sequences of states and $D\subset\mathcal{I}^*$
+is a set of suffixes. In such tables, columns are labelled with suffixes in $D$, and rows are
+labelled with input sequences. As shown in the example, rows are divided into two parts. The upper
+part, labelled with access sequence $s\in S$, denotes the states covered in the current hypothesis.
+The lower part, labelled with sequences in $\{sa|s\in S,a\in\mathcal{I}\}\backslash S$ (representing
+any potentially unclosed transition) denotes all the transitions outside $s\in S$. A cell with row
+label $s$ and column label $d$ is filled with $mq(sd)$.
 
@@
     \emph{(we use input sequences to indicate their corresponding states in following parts)}
-    \todo{define the empty sequence}
   \item[-] $\delta(s,a)=mq(sa)$
-  \item[-] $\lambda(s,a)=acc(sa,obs.D)$
+  \item[-] $\lambda(s,a)=acc(sa,obs.D)$. Since $obs$ is closed, we always have $\lambda(s,a)\in S$.
 \end{itemize}
@@
   \small
-  \KwIn{Oracle interface $mq$, Input actions $\mathcal{I}$, suffix set $D$}
-  \KwOut{Observation table $obs$} 
-  $obs$ initialized as empty\;
-  $unclosed=\{\varepsilon\}$\;
+  \KwIn{An oracle interface $mq$, An input actions $\mathcal{I}$, An observation table $obs$}
+  \KwOut{A closed observation table $obs$} 
   \Repeat{$unclosed=\varnothing$}
   {
-    $next=\{st|\forall s\in unclosed,\forall t\in \mathcal{I}\}$\;
-    append $unclosed$ to $obs$\;
-    $unclosed=\{seq\in next|\forall a\in obs, seq \not\sim_D a\}$\;
+    $next=\{st|\forall s\in obs.S,\forall t\in \mathcal{I}\}\backslash obs.S$\;
+    $unclosed=\{seq\in next|\forall a\in obs.S, seq \not\sim_{obs.D} a\}$\;
+    $obs.S$ = $obs.S\cup unclosed$\;
   }
@@
 
-Firstly, $obs$ is initialized as empty and the empty sequence $\varepsilon$ is pushed in $unclosed$.
-Then we will explore all the access sequences in $unclosed$ and calculate its successors. Here the
-$unclosed$ set consists of access sequences that has no equivalent fellow in $S$. 
+Firstly, $obs.S$ is initialized with the initial state (denoted by $\varepsilon$), and $obs.D$ is
+initialized with all one-step suffixes.
+Then we will explore all the access sequences in $obs.S$ and calculate its successors. Here the
+$unclosed$ set consists of access sequences that has no equivalent fellow in $obs.S$. 
 For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
@@
 
-In the second iteration, we explore the successors of $a,\rnoread$. Fortunately we find that every
-successor has a shorted equivalence fellow (\emph{itself}). Consequently, the algorithm terminates
+In the second iteration, we explore the successors of $a,\rnoread$. Fortunately, now every
+successor has a equivalence fellow in $obs.S$ (\emph{itself}). Consequently, the algorithm terminates
 with a closed hypothesis where all the unclosed edge shown in Figure \ref{fig:hypo} turn into
@@
   \KwOut{Observation table $obs$} 
-  $D=I$\;
+  $obs.S$ initialized as empty\;
+  $obs.D$ initialized as $\{\{i\}|i\in\mathcal{I}\}$\;
   \Repeat{$ce=true$}{
@@
 \section{Conclusion and Future Work}
-In this paper, we come up with an approach to learn timed connectors from blackboxes. We define
-the \emph{parameterized Mealy machine} to serve as an operational semantics of Reo. Then we
-describe a set of basic channels with parameterized Mealy machine, which can be used to construct
-complex connectors by means of the production operator and link operator.
-Besides, we show that every connector can be transformed into a Mealy
-machine with time action T, and such Mealy machines can be extracted by an improved version of
-well-knwon active learning algorithm L*.
-
-The original L* algorithm run into the bottleneck when time is involved. By a tree-style cache, we
-make significant reduction on membership queries and, in turn, improve the performance of learning
-algorithm. As a by-product, we also encapsulate the Reo connector as a distributable package which
-could contribute to concurrent programming.
+In this paper, we come up with an approach to extract timed connectors from blackbox
+implementations. We propose \emph{parameterized Mealy machine} to describe the behavior of Reo
+connectors. Then we define the product operator and link operator, which can be used to
+construct complex connectors from simpler ones.
+Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
+machines with timed action T provided.
+
+We also adapt the well-knwon active learning algorithm L* to deal with time domain.
+When time is taken into consideration, the original L* algorithm run into the bottleneck.
+By a tree-style cache, we make significant reduction on membership queries and, in turn,
+improve the performance of learning algorithm. As a by-product, we also encapsulate the Reo
+connector as a distributable package which could contribute to concurrent programming.
 

### 2016-01-20 paper/paper.tex
.

@@
     its sink end after a delay of $t$ time units.
-    \footnote{Here the interpretation of t-Timer is a bit different as in other works like
+    \begin{footnote}
+      Here the interpretation of t-Timer is a bit different as in other works like
       \cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/tase/Meng12}, but we can easily transform between the
-    two kinds of behavior by composing with some other basic channels.}
+      two kinds of behavior by composing with some other basic channels.
+    \end{footnote}
 \end{itemize}
@@
 
-\subsection{Counter-Examples' Analysis} 
-Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is not the 2-Timer
+\subsection{Counter Examples' Analysis} 
+Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is different with the 2-Timer
 channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
-according to the hypothesis, the result shoud have been $\rempty$. In this section, we show how to
+according to the hypothesis, the result should be $\rempty$. In this section, we show how to
 find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.
 
-Firstly, we give a formal definition of \emph{counter-examples}. With a observation table $obs$ and
-a sequence $s$, we use $hq(obs,s)$ to denote the execution result of $obs$ under the input sequence
-$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $a$ is the last element of $s$ and $s=s'a$.
-
-\begin{definition}[Counter-Example]
-  sequence $s$ is called a counter-example of $obs$ iff $mq(s)\neq hq(obs,s)$.
+Firstly, we give a formal definition of \emph{counter examples}. With a observation table $obs$ and
+a sequence $s$, we use $hq(obs,s)$ to denote the execution result of its corresponding hypothesis
+$\mathcal{H}$ under the input sequence
+$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $s=s'a,a\in\mathcal{I}$.
+
+\begin{definition}[Counter Example]
+  an input sequence $s$ is a counter example of $obs$ iff $mq(s)\neq hq(obs,s)$.
 \end{definition}
@@
 Now we consider the reason that lead to existance of counter examples. Since
-the suffix set $D$ is used to distinguish different states, the existance of counter-examples
-shows that the current suffix set $D$ is not powerful enough to distinguish all different states.
-
-Considering a counter example $s$, we define the function MaxSuffix($s,obs$) as
+the suffix set $D$ is used to distinguish states, the existance of counter-examples
+shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
+$next$ (see in Algorithm \ref{alg:buildtable}).
+
+Considering a counter example $s$, we need a new suffix to distinguish the uncovered states, which
+can be calculated by Suffix($s,obs$):
 \[
@@
 \]
-After appending $d$ in $D$, we can rebuild a closed hypothesis where $s$ is no longer a
-counter-example.
+After appending $d$ in $D$, we can prove that at least one new state will be found.
+
+\begin{theorem}
+\end{theorem}
 
@@
   \Repeat{$ce=true$}{
-    $obs$ = CloseTable($mq$, $\mathcal{I}$, $D$)\;
+    $obs$ = CloseTable($mq$, $\mathcal{I}$, $obs$)\;
     $ce=eq(obs)$\;
-    \If {$ce!=true$} {
-      D.append(MaxSuffix(s))\;
+    \If {$ce\neq true$} {
+      D.append(Suffix(s))\;
     }

### 2016-01-20 paper/paper.tex
.

@@
 \newcommand{\rread}[0]{\rhd}
-\newcommand{\rnoread}[0]{\oslash}
+\newcommand{\rnoread}[0]{\otimes}
 \newcommand{\smap}[1]{[{#1}]}
@@
 \author{
-\IEEEauthorblockN{Yi Li\IEEEauthorrefmark{1}, Yiwu Wang\IEEEauthorrefmark{1} and Meng Sun\IEEEauthorrefmark{1}}
+\IEEEauthorblockN{Yi Li, Meng Sun and Yiwu Wang}
 \IEEEauthorblockA{
-\IEEEauthorrefmark{1}Department of Informatics, School of Mathematical Sciences, Peking University,
+LMAM \& Department of Informatics, School of Mathematical Sciences, Peking University,
 Beijing, China\\
-liyi\_math@pku.edu.cn, yiwuwang@126.com, summeng@math.pku.edu.cn
+liyi\_math@pku.edu.cn, summeng@math.pku.edu.cn, yiwuwang@126.com
 }
@@
   between Reo connectors and Mealy machines. With the product operator, complex connectors can be
-  constructed by joining basic channels and the PMM of connectors can be transformed into Mealy
+  constructed by joining basic channels and the PMMs of connectors can be transformed into Mealy
   machines. Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in the form
@@
 Internet of Things(IoT), wherein individual components are composed via \emph{connectors} 
-to build systems. Such systems could be distributed logically or physically, which
+to build complex systems. Such systems could be distributed logically or physically, which
 makes coordination processes even more complicated. In this case, we need to specify the coordination
@@
 
-In this paper we address this question by proposing a active learning framework as shown in Figure
+In this paper we address this question by proposing an active learning framework as shown in Figure
 \ref{fig:howto} to automatically extract timed connector models from blackbox implementations. 
@@
     its sink end after a delay of $t$ time units.
-    \begin{footnote}
+    \footnote{
       Here the interpretation of t-Timer is a bit different as in other works like
@@
       two kinds of behavior by composing with some other basic channels.
-    \end{footnote}
+      }
 \end{itemize}
@@
 coincide on a node are source ends, sink ends or a combination of both.
-(see in Figure \ref{fig:node})
+(see Figure \ref{fig:node})
 
@@
   \end{center}
-  \caption{Coordination with Reo Connectors}
+  \caption{An Example of Coordination with Reo Connectors}
   \label{fig:reoconnector}
@@
   \begin{itemize}
-    \item[-] a finite set of states $S$
-    \item[-] an initial state $s_0\in S$
-    \item[-] a finite set of inputs $I$
-    \item[-] a finite set of outputs $O$
+    \item[-] a finite set of states $S$,
+    \item[-] an initial state $s_0\in S$,
+    \item[-] a finite set of inputs $I$,
+    \item[-] a finite set of outputs $O$,
     \item[-] an output function $\delta :  S \times  I \rightarrow O$ mapping a pair
-      of a state and an input to the corresponding output.
+      of a state and an input to the corresponding output,
     \item[-] a transition function $\lambda : S \times I \rightarrow S$ mapping a pair of a
@@
 
-Besides, we're going to add a ``T'' action in Mealy machines. It indicates that the corresponding
+Besides, we add a timed action ``$T$'' in Mealy machines. It indicates that the corresponding
 transition will take one time unit to finish.
@@
     \item[-] The value of $\Sigma$ is a \emph{finite} data set (hereinafter referred as
-      alphabet), e.g. $\{a,b\}$
-    \item[-] $S$ maps an alphabet to a \emph{finite} set of states.
-    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma.s_0\in S(\Sigma)$
-    \item[-] $I$ is a finite set of source-ends.
-    \item[-] $O$ is a finite set of sink-ends.
+      alphabet), e.g.  $\{a,b\}$,
+    \item[-] $S$ maps an alphabet to a \emph{finite} set of states,
+    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma.s_0\in S(\Sigma)$,
+    \item[-] $I$ is a finite set of source-ends,
+    \item[-] $O$ is a finite set of sink-ends,
     \item[-] $\delta$ maps an alphabet to an \emph{output function}. We use
       $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,O)$ to denote the
-      output function.
+      output function,
     \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
@@
 \]
+
+A non-timed input action $a\in Input(\Sigma,I,O)$ can be restricted to $I'\subseteq I$, denoted by
+$a\downarrow_{I'}$ which is defined on $Input(\Sigma,I',O)$ and satisfies
+\[
+\forall i\in I'. a\downarrow_{I'}(i)=a(i)
+\]
+Restriction on output actions can be defined similarly.
 
@@
 \begin{definition}[Product]
-  The product operator \emph{prod} of two PMMs
+  For two PMMs $\mathcal{PM}_1$ and $\mathcal{PM}_2$, if
+  $\mathcal{PM}_2.O\cap\mathcal{PM}_1.I=\varnothing$, their product 
   \[
-  \mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)\mbox{ if }\mathcal{PM}_2.O\cap
-  \mathcal{PM}_1.I=\varnothing
-  \]
-  is defined as follows.
+  \mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)  \]
+  can be defined as follows.
   \begin{itemize}
@@
   \end{itemize}
-  \emph{(Here we assume that sink ends of $\mathcal{PM}_1$ can be connected to source ends $\mathcal{PM}_2$, but not
-  vise versa)}
+  \emph{(Here we assume that sink ends of $\mathcal{PM}_1$ can be connected to source ends of
+  $\mathcal{PM}_2$, but not vise versa)}
   \begin{itemize}
@@
         \begin{array}[ht]{ll}
-          (Out_1 \cup Out_2)\downarrow_{\mathcal{PM}'.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
+          (\bigcup_{j=1,2} Out_j)\downarrow_{\mathcal{PM}'.O} & i\neq T\land(\bigwedge_{j=1,2} Out_j\neq\rblock) \\
           \rempty & i = T \\
@@
       \begin{itemize}
+        \item[*] $i\in Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O)$
         \item[*] $In_1 = i\downarrow_{\mathcal{PM}_1.I}$
-        \item[*] $Out_1 = \mathcal{PM}_1.\delta(\Sigma)(s_1,In_1)$
         \item[*] $In_2 = (Out_1 \cup i)\downarrow_{\mathcal{PM}_2.I}$
-        \item[*] $Out_2 = \mathcal{PM}_2.\delta(\Sigma)(s_2,In_2)$
+        \item[*] $Out_j = \mathcal{PM}_j.\delta(\Sigma)(s_j,In_j)$ for $j=1,2$
       \end{itemize}
     \item[-] $\forall\Sigma. \mathcal{PM}'. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
-      where we have
-      \begin{itemize}
-        \item[*] $s_1' = \mathcal{PM}_1.\lambda(\Sigma)(s_1,In_1)$
-        \item[*] $s_2' = \mathcal{PM}_2.\lambda(\Sigma)(s_2,In_2)$
-      \end{itemize}
+      where for $j=1,2$, $s_j' = \mathcal{PM}_j.\lambda(\Sigma)(s_j,In_j)$.
   \end{itemize}
@@
 
-The idea in \emph{production} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
-input of $\mathcal{PM}_2$. Time actions T is only executed simultaneously between $\mathcal{PM}_1$ and $\mathcal{PM}_2$.
-
-As mentioned in the notation above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
+The idea in \emph{product} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
+input of $\mathcal{PM}_2$. Timed action $T$ is only executed simultaneously between $\mathcal{PM}_1$
+and $\mathcal{PM}_2$.
+
+As mentioned above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
 $\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Figure
-\ref{fig:reoconnector}. To address the problem, we define a \emph{link} operation to connect sink
+\ref{fig:reoconnector}. To solve the problem, we define a \emph{link} operator to connect sink
 ends and source ends in the same connector.
@@
             \rempty & i=T \\
-            \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
+            \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
             \rblock & otherwise \\
@@
       \[
-      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN:d\})(\OUT)=d
+      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})(\OUT)=d
       \]
@@
             \mathcal{PM}.\lambda(\Sigma,T) & i=T \\
-            \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN:d\}) & (*)\\
+            \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN\mapsto d\}) & (*)\\
             s & otherwise \\
@@
 
-With \emph{link} and \emph{prop} defined, connectors can be constructed by simpler ones in
-form of PMMs. It will be transformed into a concrete Mealy machine later, once the alphabet $\Sigma$
-is provided.
+With \emph{prod} and \emph{link} defined, connectors can be constructed by composing simpler ones in
+the form of PMMs. It can be transformed into a concrete Mealy machine later, once the alphabet
+$\Sigma$ is provided.
 
@@
 implementations in 3 steps:
-\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. Besides,
-here the input and output symbols of the blackbox are provided as $\mathcal{I}$ and $\mathcal{O}$,
-and the blackbox implementation is supposed to be equivalent to a Mealy machine where all states are
-reachable.
+\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. 
+The input and output symbols of the blackbox implementation are provided as $\mathcal{I}$ and
+$\mathcal{O}$, and the blackbox implementation is supposed to be equivalent to a Mealy machine where
+all states are reachable.
 
@@
 
-Mealy machines are composed of \emph{states} and \emph{transitions}.
+Mealy machines consist of \emph{states} and \emph{transitions}.
 As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
@@
 \begin{definition}[$D$-Equivalence]
-  provided with a set of suffixes $D\subset\mathcal{I}^+$, we say the corresponding states of
+  Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
   $s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
@@
 Now we use \emph{access sequence} to describe the states. Given an input sequence $s$, the access
-sequence of $s$ is defined as
-\[
-acc(s,D)=\min\{s'\in\mathcal{I}^*|s'\sim_D s\}
-\]
-
-Formally, an observation table (see in Figure \ref{fig:hypo}) is determined by a tuple $(S,D)$ where
+sequence $acc(s,D)$ of $s$ is defined as the shortest sequence in $\{s'\in\mathcal{I}^*|s'\sim_D
+s\}$\footnote{When there are multiple satisfying sequences with the same length, we use a certain tactic
+to pick up one from them determinstically.}.
+
+Formally, an observation table (see Figure \ref{fig:hypo} as an example) is determined by a tuple $(S,D)$ where
 $S\subset\mathcal{I}^*$ is a set of the access sequences of states and $D\subset\mathcal{I}^*$
 is a set of suffixes. In such tables, columns are labelled with suffixes in $D$, and rows are
-labelled with input sequences. As shown in the example, rows are divided into two parts. The upper
+labelled with input sequences. As shown in Figure \ref{fig:hypo}, rows are divided into two parts. The upper
 part, labelled with access sequence $s\in S$, denotes the states covered in the current hypothesis.
@@
 
-From a closed observation we can construct a hypothetical Mealy machine in a straight-forward way.
-The Mealy machine $\mathcal{H}=\langle S,s_0,\mathcal{I},\mathcal{O},\delta,\lambda\rangle$ is
-constructed from $obs$ as follows:
+From a closed observation table $obs$, we can construct a hypothetical Mealy machine $\mathcal{H}=\langle
+S,s_0,\mathcal{I},\mathcal{O},\delta,\lambda\rangle$ in a straight-forward way:
 \begin{itemize}
@@
 
-Algorithm \ref{alg:buildtable} shows how to build an closed observation table.
+Algorithm \ref{alg:buildtable} shows how to build a closed observation table.
 
 \begin{algorithm} 
-  \caption{CloseTable} 
+  \caption{EncloseTable} 
   \label{alg:buildtable}
@@
   \KwIn{An oracle interface $mq$, An input actions $\mathcal{I}$, An observation table $obs$}
-  \KwOut{A closed observation table $obs$} 
+  \KwOut{A closed observation table $obs'$} 
   \Repeat{$unclosed=\varnothing$}
@@
     $unclosed=\{seq\in next|\forall a\in obs.S, seq \not\sim_{obs.D} a\}$\;
-    $obs.S$ = $obs.S\cup unclosed$\;
+    $obs'.S$ = $obs.S\cup unclosed$\;
+    $obs'.D$ = $obs.D$\;
   }
-  \Return $obs$\; 
+  \Return $obs'$\; 
 \end{algorithm}
@@
 We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$, and the alphabet
-is $\{a\}$. We briefly denote $\{A:a,B:\rnoread\}$ and other input/output actions in form of
-$a,\rnoread$.
+is $\{a\}$. We briefly denote $\{A\mapsto a,B\mapsto \rnoread\}$ and other input/output actions in form of
+$(a,\rnoread)$.
 
@@
 initialized with all one-step suffixes.
-Then we will explore all the access sequences in $obs.S$ and calculate its successors. Here the
-$unclosed$ set consists of access sequences that has no equivalent fellow in $obs.S$. 
-For example, figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
-iteration. The five successors of $\varepsilon$ is presented as the bottom part of the table, where
-four are equivalent with $\varepsilon$ but $a,\rnoread$ is not. Therefore, we take $a,\rnoread$ as a
-brand-new state and all of its successors need further exploration (see in the hypothesis Mealy
-machine presented in the following figure).
+Then we explore all the access sequences in $obs.S$ and calculate its successors. Here
+$unclosed$ consists of access sequences that has no equivalent sequence in $obs.S$. 
+For example, Figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
+iteration. The five successors of $\varepsilon$ are presented at the bottom of the table, where
+four are equivalent with $\varepsilon$ but $(a,\rnoread)$ is not. Therefore, we take $(a,\rnoread)$ as a
+brand-new state and all of its successors need further exploration.
 
@@
         \hline
-        & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
+        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
         \hline\hline
@@
         \hline
-        a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         \rowcolor[gray]{.9}
-        a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & \mbox{NO MATCH}\\
-        \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        T & \rblock & \rblock & \rempty & \rempty & \rempty \varepsilon & \varepsilon \\
+        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
+        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         \hline
@@
 
-In the second iteration, we explore the successors of $a,\rnoread$. Fortunately, now every
-successor has a equivalence fellow in $obs.S$ (\emph{itself}). Consequently, the algorithm terminates
-with a closed hypothesis where all the unclosed edge shown in Figure \ref{fig:hypo} turn into
+In the second iteration, we explore the successors of $(a,\rnoread)$. Fortunately, now every
+successor has an equivalence sequence in $obs.S$, \emph{i.e.}, itself. Consequently, the algorithm terminates
+with a closed hypothesis where all the unclosed edges turn into
 self-loop.
@@
   \begin{center}
-    \begin{small}
     \begin{displaymath}
@@
         \hline
-          & a,\rread & \bot,\rread & a,\rnoread & \bot,\rnoread & T & \mbox{AccessSequence}\\
+        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
         \hline\hline
         \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
         \hline
-          a,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-          \bot,\rread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-          a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
-          \bot,\rnoread & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
         T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-          \hline
-          a,\rnoread-a,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
-          a,\rnoread-\bot,\rread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
-          a,\rnoread-a,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
-          a,\rnoread-\bot,\rnoread & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
-          a,\rnoread-T & \rblock & \rblock & \rblock & \rempty & \rempty & a,\rnoread \\
+        (a,\rnoread),(a,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        (a,\rnoread),(\bot,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        (a,\rnoread),(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        (a,\rnoread),(\bot,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty &
+        (a,\rnoread) \\
+        (a,\rnoread),T & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
         \hline
@@
     \end{displaymath}
-    \end{small}
   \end{center}
-  \caption{A Closed Observation Table}
+  \caption{A Closed Version of Figure \ref{fig:hypo}}
   \label{fig:hypo2}
@@
 Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is different with the 2-Timer
-channel. It's easy to find a counter-example $s_0=a,\rnoread-T-T-\bot,\rread$ where $mq(s)=a$ while
+channel. It's easy to find a counter-example $s_0=(a,\rnoread),T,T,(\bot,\rread)$ where $mq(s_0)=a$ while
 according to the hypothesis, the result should be $\rempty$. In this section, we show how to
@@
 
-Firstly, we give a formal definition of \emph{counter examples}. With a observation table $obs$ and
+Firstly, we give a formal definition of \emph{counter examples}. With an observation table $obs$ and
 a sequence $s$, we use $hq(obs,s)$ to denote the execution result of its corresponding hypothesis
@@
 
-Now we consider the reason that lead to existance of counter examples. Since
+Now we consider the reason that leads to existance of counter examples. Since
 the suffix set $D$ is used to distinguish states, the existance of counter-examples
 shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
-$next$ (see in Algorithm \ref{alg:buildtable}).
-
-Considering a counter example $s$, we need a new suffix to distinguish the uncovered states, which
-can be calculated by Suffix($s,obs$):
+$next$ (see Algorithm \ref{alg:buildtable}).
+
+For a counter example $s$, we need a new Suffix$(s,obs)$ to distinguish the uncovered state
+represented by $s$, which is defined as the longest sequence in
 \[
-\max\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
+\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
 \]
-After appending $d$ in $D$, we can prove that at least one new state will be found.
-
-\begin{theorem}
-\end{theorem}
+After appending Suffix$(s,obs)$ to $D$, it's obvious that at least one uncovered state will be found.
 
@@
   \label{alg:lstar}
-  \KwIn{Oracle interface $mq,eq$, Input actions $\mathcal{I}$}
+  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
   \KwOut{Observation table $obs$} 
   $obs.S$ initialized as empty\;
-  $obs.D$ initialized as $\{\{i\}|i\in\mathcal{I}\}$\;
+  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
   \Repeat{$ce=true$}{
-    $obs$ = CloseTable($mq$, $\mathcal{I}$, $obs$)\;
+    $obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
     $ce=eq(obs)$\;
     \If {$ce\neq true$} {
-      D.append(Suffix(s))\;
+      $obs.D$.append(Suffix$(ce, obs)$)\;
     }
@@
 Golang\cite{golang}, which is widely known for its elegant design and impressive efficiency.
-Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model,\texttt{Golang} shares many
+Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model, \texttt{Golang} shares many
 similar ideas with Reo, and in turn makes our implementation much more natural.
@@
   \end{center}
-  \caption{Expiring FIFO1 Channel (ExpFIFO1)}
+  \caption{Expiring FIFO1 (ExpFIFO1)}
   \label{fig:expfifo}
@@
 
-Informally speaking, an expiring FIFO1 channel with \emph{timeout} $n$ is able to accept a data item
+Informally speaking, an expiring FIFO1 with \emph{timeout} $n$ is able to accept a data item
 and stored it in the buffer cell for $n$ time units. If a read operation on $B$ is performed within
-$n$ time units, it will obtain the data item successfully and clear the buffer. However, the data
-item would be dropped if no read operation comes.
+$n$ time units, it will obtain the data item successfully and clear the buffer. Otherwise, the data
+item would be dropped if no read operation comes within $n$ time units.
 
@@
 
-Figure \ref{fig:expfifosemantics} shows the learning result of this example.
-To simplify the graph, we ignore the all the trivial transitions $\frac{\bot,\rnoread}{\rempty}$
+Figure \ref{fig:expfifosemantics} shows the learning result of this example where $n=2$ and
+$\Sigma=\{a\}$.
+To simplify the graph, we ignore all the trivial transitions $\frac{(\bot,\rnoread)}{\rempty}$
 and block transitions. More details of this case can be found in our \emph{github repo}.
@@
     \hline
-    & FIFO & Alternator & Gate \\
+    & FIFO1 & Alternator & Gate \\
     \hline\hline
@@
 \begin{itemize}
-  \item When constructing \emph{Obs} tables, there are lots of redundant calls to membership
-    queries. For example, a sequence with prefix 'aa' and suffix 'b' is exactly same as another one
-    with prefix 'a' and suffix 'ab'.
-  \item Simulation on mealy machines can provide multi-step output. Consequently, if we have
-    simulated an 'abc' sequence, there's no reason to perform simulation on an 'ab' sequence.
+  \item When constructing observation tables, there are lots of redundant calls to membership
+    queries. For example, a sequence with prefix `aa' and suffix `b' is exactly same as another one
+    with prefix `a' and suffix `ab'.
+  \item Simulation on Mealy machines can provide multi-step outputs.  Consequently, if we have
+    simulated an `abc' sequence, it's useless to perform simulation on an `ab' sequence again.
 \end{itemize}
@@
 Our implementation in \texttt{Golang} is well-prepared not only for academic use
-but also for practical concurrent programming. The following code shows how to compose an alternator
-connector (see in Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
+but also for practical concurrent programming. The following code shows how to construct an alternator
+connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
 can be found in our github repo.
@@
 
-In this case, \emph{sender} are goroutines (basic parallel units in \texttt{Golang}) that keep
-sending certain messages to some given port (A and B). A \emph{monitor} keep trying to read data
+In this case, \emph{senders} are goroutines (basic parallel units in \texttt{Golang}) that keep
+sending certain messages to some given port (A and B). A \emph{monitor} keeps trying to read data
 items from the sink end C and print them on the screen. Finally, we have an interleaved sequence of
@@
 
-We also adapt the well-knwon active learning algorithm L* to deal with time domain.
-When time is taken into consideration, the original L* algorithm run into the bottleneck.
+We also adapt the well-known active learning algorithm L* to deal with time domain.
+When time is taken into consideration, the original L* algorithm run into a performance bottleneck.
 By a tree-style cache, we make significant reduction on membership queries and, in turn,
@@
 
-Our future works would mainly focus on better support of dense time. To describe dense
+Our future work mainly focuses on better support of dense time. To describe dense
 time behavior, the Mealy machine model needs a lot of changes instead of a simple T action. Besides,
-we will also try to improve our algorithm to handle non-deterministic behaviors. This is not a brand
+we will also try to improve our algorithm to handle non-deterministic behavior. This is not a brand
 new topic \cite{DBLP:conf/isola/VolpatoT14}, but we believe that there is still room for
@@
 The work was partially supported by the National Natural Science Foundation of China under grant no.
-61202069, 61272160 and 61532019, and Research Fund for the Doctoral Program of Higher Education of
-China under grant no. 20120001120103.
-
+61202069, 61272160 and 61532019.
 \bibliographystyle{abbrv}

### 2016-01-20 paper/paper.tex
.

@@
 
-In this paper we address this question by proposing an active learning framework as shown in Figure
+In this paper we address this question by proposing an active learning framework as shown in Fig.
 \ref{fig:howto} to automatically extract timed connector models from blackbox implementations. 
@@
 
-Figure \ref{fig:basic} shows the graphical representation of some basic channel types in Reo, whose
+Fig. \ref{fig:basic} shows the graphical representation of some basic channel types in Reo, whose
 behavior are described as follows:
@@
 coincide on a node are source ends, sink ends or a combination of both.
-(see Figure \ref{fig:node})
+(see Fig. \ref{fig:node})
 
@@
 
-Figure \ref{fig:reoconnector} provides a simple example to illustrate how complex
+Fig. \ref{fig:reoconnector} provides a simple example to illustrate how complex
 connectors are constructed and used in coordination. In this example, we have three components
-COM1,COM2 and MONITOR. With an \emph{alternator} connector as shown in Figure
+COM1,COM2 and MONITOR. With an \emph{alternator} connector as shown in Fig.
 \ref{fig:reoconnector}, MONITOR can obtain data items from COM1 and COM2 alternately. This example
@@
 
-Figure \ref{fig:activelearning} shows the sketch of active learning, wherein:
+Fig. \ref{fig:activelearning} shows the sketch of active learning, wherein:
 \begin{itemize}
@@
 
-These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Figure
+These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Fig.
 \ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm constructs a
@@
 
-Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Figure \ref{fig:pmmfifo},
+Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Fig. \ref{fig:pmmfifo},
 where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
@@
 As mentioned above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
-$\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Figure
+$\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Fig.
 \ref{fig:reoconnector}. To solve the problem, we define a \emph{link} operator to connect sink
@@
 
-Formally, an observation table (see Figure \ref{fig:hypo} as an example) is determined by a tuple $(S,D)$ where
+Formally, an observation table (see Fig. \ref{fig:hypo} as an example) is determined by a tuple $(S,D)$ where
 $S\subset\mathcal{I}^*$ is a set of the access sequences of states and $D\subset\mathcal{I}^*$
 is a set of suffixes. In such tables, columns are labelled with suffixes in $D$, and rows are
-labelled with input sequences. As shown in Figure \ref{fig:hypo}, rows are divided into two parts. The upper
+labelled with input sequences. As shown in Fig. \ref{fig:hypo}, rows are divided into two parts. The upper
 part, labelled with access sequence $s\in S$, denotes the states covered in the current hypothesis.
@@
 $unclosed$ consists of access sequences that has no equivalent sequence in $obs.S$. 
-For example, Figure \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
+For example, Fig. \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
 iteration. The five successors of $\varepsilon$ are presented at the bottom of the table, where
@@
   \end{center}
-  \caption{A Closed Version of Figure \ref{fig:hypo}}
+  \caption{A Closed Version of Fig. \ref{fig:hypo}}
   \label{fig:hypo2}
@@
 \subsection{Counter Examples' Analysis} 
-Apparently, the closed hypothesis presented in Figure \ref{fig:hypo2} is different with the 2-Timer
+Apparently, the closed hypothesis presented in Fig. \ref{fig:hypo2} is different with the 2-Timer
 channel. It's easy to find a counter-example $s_0=(a,\rnoread),T,T,(\bot,\rread)$ where $mq(s_0)=a$ while
@@
 
-Figure \ref{fig:expfifosemantics} shows the learning result of this example where $n=2$ and
+Fig. \ref{fig:expfifosemantics} shows the learning result of this example where $n=2$ and
 $\Sigma=\{a\}$.
@@
 but also for practical concurrent programming. The following code shows how to construct an alternator
-connector (see Figure \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
+connector (see Fig. \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
 can be found in our github repo.

### 2016-04-03 shortpaper/images/activelearning.tex
.

\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

% Define block styles used later

\tikzstyle{sensor}=[draw, fill=blue!20, text width=2em, 
text centered, minimum height=1em,drop shadow, font=\small]
\tikzstyle{ann} = [above, text width=3em, text centered, font=\small]
\tikzstyle{wa} = [sensor, text width=4em, fill=red!20, 
minimum height=4em, rounded corners, drop shadow, font=\small]
\tikzstyle{sc} = [sensor, text width=5em, fill=red!20, 
minimum height=4em, rounded corners, drop shadow, font=\small]

\tikzstyle{every node} = [font=\small]

\begin{tikzpicture}[scale=0.7]
    \node (wa) [wa]  {System Combination};
    \path (wa.west)+(-3.2,1.5) node (asr1) [sensor] {$ASR_1$};
    \path (wa.west)+(-3.2,0.5) node (asr2)[sensor] {$ASR_2$};
    \path (wa.west)+(-3.2,-1.0) node (dots)[ann] {$\vdots$}; 
    \path (wa.west)+(-3.2,-2.0) node (asr3)[sensor] {$ASR_N$};

    \path (wa.east)+(\blockdist,0) node (vote) [sensor] {$\theta_0,\theta_1,...,\theta_M$\\Estimated Parameters};

    \path [draw, ->] (asr1.east) -- node [above] {} 
        (wa.160) ;
    \path [draw, ->] (asr2.east) -- node [above] {} 
        (wa.180);
    \path [draw, ->] (asr3.east) -- node [above] {} 
        (wa.200);
    \path [draw, ->] (wa.east) -- node [above] {} 
        (vote.west);

        \path (wa.south) +(0,-\blockdist) node (asrs) {System Under Learn - SUT};

    \begin{pgfonlayer}{background}
        \path (asr1.west |- asr1.north)+(-0.5,0.3) node (a) {};
        \path (wa.south -| wa.east)+(+0.5,-0.3) node (b) {};
        \path (vote.east |- asrs.east)+(+0.5,-0.5) node (c) {};

        \path[fill=yellow!20,rounded corners, draw=black!50, dashed]
            (a) rectangle (c);           
        \path (asr1.north west)+(-0.2,0.2) node (a) {};

    \end{pgfonlayer}

    % Validation Layer is the same except that there are a set of nodes and links which are added

    \path (wa.south)+(-2.0,-7.5) node (syscomb) [sc] {\textbf{System Combination \\Algorithm}\\Estimated Parameters\\from training};
    \path (syscomb.west)+(-2.2,1.5) node (asrt1) [sensor] {$ASR_1$};
    \path (syscomb.west)+(-2.2,0.5) node (asrt2)[sensor] {$ASR_2$};
    \path (syscomb.west)+(-2.2,-1.0) node (dots)[ann] {$\vdots$}; 
    \path (syscomb.west)+(-2.2,-2.0) node (asrt3)[sensor] {$ASR_N$};

    \path [draw, ->] (asrt1.east) -- node [above] {} 
        (syscomb.160) ;
    \path [draw, ->] (asrt2.east) -- node [above] {} 
        (syscomb.180);
    \path [draw, ->] (asrt3.east) -- node [above] {} 
        (syscomb.200);

    \path (wa.south) +(0,-\blockdist) node (sct) {System Combination - Training};

    \path (syscomb.east)+(1.0,0.0) node (bwtn) {};

    % Note how the single nodes are repeated using for loop
    \foreach \x in {0,1,...,4} 
    { 
        \draw (bwtn.east)+(\x,0) node (asr\x-2)[]{}; 
        \fill (bwtn.east)+(\x,0) circle (0.1cm); 
    }

    \path [draw, ->] (syscomb.east) -- node [above] {} 
        (bwtn.east);
	\path [draw, ->] (asr0-2) -- node [above] {@} 
        (asr1-2);
    \path [draw, -] (asr1-2) -- node [above] {b} 
        (asr2-2);
    \path [draw, -] (asr2-2) -- node [above] {z} 
        (asr3-2);
    \path [draw, -] (asr3-2) -- node [above] {} 
        (asr4-2);

    \path [draw, ->] (asr0-2) edge[bend  right]  node [below] {@} 
        (asr1-2);
    \path [draw, ->] (asr1-2) edge[bend  right]  node [below] {b} 
        (asr2-2);
    \path [draw, ->] (asr2-2) edge[bend  right]  node [below] {c} 
        (asr3-2);
    \path [draw, ->] (asr4-2) node[]{} (asr4-2)+(1.0,0);

    \begin{scope}[looseness=1.6]
        \path [draw, ->] (asr0-2) edge[bend  right=90]  node [below] {a} 
            (asr1-2);
        \path [draw, ->] (asr1-2) edge[bend  right=90]  node [below] {b} 
            (asr2-2);
        \path [draw, ->] (asr2-2) edge[bend  right=90]  node [below] {c} 
            (asr3-2);
    \end{scope}
    \path (asr3-2.east)+(1.5,0.0) node (bw)[sensor] {Best Word Sequence\\$\arg\max$};

    \path [draw, -] (asr1-2.east) node [below] {} 
        (bw.west);

    \begin{pgfonlayer}{background}
        \path (asrt1.west)+(-0.5,1.0) node (g) {};
        \path (bw.east |- syscomb.south)+(0.5,-1.5) node (h) {};

        \path[fill=yellow!20,rounded corners, draw=black!50, dashed]
            (g) rectangle (h);

        \path [draw, ->] (vote.south) edge[bend  left=90]  node [below] {Used in validation} 
            (syscomb.30);

    \end{pgfonlayer}

    \path (asr1-2.south) +(-\blockdist,-\blockdist) 
        node (asrs) {System Combination - Validation};

\end{tikzpicture}

### 2016-04-03 shortpaper/paper.tex
.

--- 2016-01-20 paper/paper.tex
@@
   interaction among different components in large-scale distributed and concurrent systems. In this
-  paper, we propose an active learning framework to extract timed connector models from black-box
+  paper, we use active learning to extract timed connector models from black-box
   system implementation. 
@@
   of Mealy machines). The new algorithm has shown its efficiency in multiple case studies. 
-  This framework has been implemented in \texttt{Golang}.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  Active Learning, Coordination Languages, Timed Connectors
+  Active Learning, Coordination, Connectors
 \end{IEEEkeywords}
@@
 \emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, which can be used
-to describe the coordination process in DRES clearly and intuitively. Different formal
-semantics have been proposed to specify the behavior of timed Reo.
-For example, an operational semantics based on \emph{timed constraint automata} was raised by Baier et
-al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
-properties of timed connectors.
-In \cite{DBLP:conf/tase/Meng12}, a UTP design model was proposed to specify the behavior of timed
-connectors..
+to describe the coordination process in DRES clearly and intuitively. 
+\todo{describe semantics in a more short way}
+%Different formal semantics have been proposed to specify the behavior of timed Reo.
+%For example, an operational semantics based on \emph{timed constraint automata} was raised by Baier et
+%al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
+%properties of timed connectors.
+%In \cite{DBLP:conf/tase/Meng12}, a UTP design model was proposed to specify the behavior of timed
+%connectors..
 
@@
 
-\begin{figure}[ht]
-  \begin{center}
-    \includegraphics[width=.4\textwidth]{./images/howto.png}
-  \end{center}
-  \caption{The Active Learning Framework}
-  \label{fig:howto}
-\end{figure}
+%\begin{figure}[ht]
+  %\begin{center}
+    %\includegraphics[width=.4\textwidth]{./images/howto.png}
+  %\end{center}
+  %\caption{The Active Learning Framework}
+  %\label{fig:howto}
+%\end{figure}
 
@@
 
+\todo{use a short paragraph to describe the preliminaries}
+
 The rest of the paper is organized as follows: In Section
@@
 \texttt{Golang}. Finally, Section VI concludes the paper.
-
-\section{Preliminaries} 
-\label{sec:preliminaries}
-\subsection{Reo Coordination Language} 
-\label{sec:reo}
-We provide here a brief overview of the main concepts in Reo. Further details can be found in
-\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.
-
-Reo is a channel based exogenous coordination language proposed by F. Arbab in
-\cite{DBLP:journals/mscs/Arbab04}. 
-A coordinator in Reo, also called \emph{connector}, provides the protocol that controls and
-organizes the communication, synchronization and cooperation among the components which
-communicate through the connector. Connectors can be defined without dependence on components,
-which makes Reo a powerful ``glue language'' in component-based
-development\cite{DBLP:journals/sigsoft/Gill03}.
-
-In Reo, complex connectors are made up of simpler ones. The atomic connectors are called
-\emph{channels}, and each of them has two \emph{channel ends}. There are two types of channel ends:
-\emph{source} and \emph{sink}. Source channel ends accept data into the channel, while sink
-channel ends dispense data out of the channel.
-
-\begin{figure}[ht]
-  \begin{center}
-    \input{./images/basic.tex}
-  \end{center}
-  \caption{Basic Reo Channels}
-  \label{fig:basic}
-\end{figure}
-
-Fig. \ref{fig:basic} shows the graphical representation of some basic channel types in Reo, whose
-behavior are described as follows:
-
-\begin{itemize}
-  \item [-] A \emph{Sync} channel accepts a data item from its source end iff the data item can be
-    dispensed through its sink end simultaneously.
-  \item [-] A \emph{LossySync} channel is always ready to accept data items. These items will be
-    dispensed through its sink end simultaneously if possible, otherwise they will be lost.
-  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
-    item through one of its source end iff a data item is also available to be accepted
-    simultaneously through the other end. Then both items will be dropped.
-  \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
-    data item whenever the buffer is empty. 
-  \item [-] A t-timer channel accepts any data item from its source end, and later dispense it to
-    its sink end after a delay of $t$ time units.
-    \footnote{
-      Here the interpretation of t-Timer is a bit different as in other works like
-      \cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/tase/Meng12}, but we can easily transform between the
-      two kinds of behavior by composing with some other basic channels.
-      }
-\end{itemize}
-
-Channels are joint together in \emph{nodes}. There are three types of nodes:
-\emph{source}, \emph{sink} and \emph{mixed} nodes, depending on whether all channel ends that
-coincide on a node are source ends, sink ends or a combination of both.
-(see Fig. \ref{fig:node})
-
-\begin{figure}[ht]
-  \begin{center}
-    \input{./images/nodes.tex}
-  \end{center}
-  \caption{Source, Sink and Mixed Nodes in Reo}
-  \label{fig:node}
-\end{figure}
-
-Components can be linked to source nodes or sink nodes. A component can write data items to its
-corresponding source node only if the data item can be dispensed simultaneously to all source ends
-on this node. Similarly, a component can read a data item only if there is at least one readable
-sink end on its corresponding node. A mixed node non-determinstically selects and takes a data item
-from one of its coincident sink ends and replicates it into all of its coincident source ends.
-
-\begin{figure}[ht]
-  \begin{center}
-    \input{./images/connectorexample.tex}
-  \end{center}
-  \caption{An Example of Coordination with Reo Connectors}
-  \label{fig:reoconnector}
-\end{figure}
-
-Fig. \ref{fig:reoconnector} provides a simple example to illustrate how complex
-connectors are constructed and used in coordination. In this example, we have three components
-COM1,COM2 and MONITOR. With an \emph{alternator} connector as shown in Fig.
-\ref{fig:reoconnector}, MONITOR can obtain data items from COM1 and COM2 alternately. This example
-has been implemented in \texttt{Golang} as shown in Section \ref{sec:reolib}.
-Besides, all the connectors are supposed to have \emph{deterministic} behavior hereinafter to meet
-the requirement of active learning algorithm L*.
-
-\subsection{Mealy Machines}
-
-In this work, we use \emph{Mealy machines} to model Reo connectors.
-Mealy machine was first proposed by George. H. Mealy in \cite{George1955A} as an extension of finite
-state machine. Compared with other variants, Mealy machines are designed to model
-reactive systems, where outputs of a machine are determined by not only its current state but also
-the current inputs. Besides, Mealy machines are supposed to be \emph{input enabled}, which means
-that all possible inputs should be acceptable in all states. In other words, if an input is invalid
-for some state, we need to manually define an additional state to describe such exceptions.
-
-Various forms of Mealy machines have been defined in the
-literature\cite{George1955A,DBLP:journals/jcss/Broy14,DBLP:conf/sfm/SteffenHM11}. 
-Since active automata learning requires the system-under-learn to be deterministic, in
-this paper we take the deterministic Mealy machine model as defined in 
-\cite{DBLP:conf/sfm/SteffenHM11}.
-
-\begin{definition}[Mealy machine]
-  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of:
-  \begin{itemize}
-    \item[-] a finite set of states $S$,
-    \item[-] an initial state $s_0\in S$,
-    \item[-] a finite set of inputs $I$,
-    \item[-] a finite set of outputs $O$,
-    \item[-] an output function $\delta :  S \times  I \rightarrow O$ mapping a pair
-      of a state and an input to the corresponding output,
-    \item[-] a transition function $\lambda : S \times I \rightarrow S$ mapping a pair of a
-      state and an input to the corresponding successor state.
-  \end{itemize}
-\end{definition}
-
-We say that a Mealy machine is \emph{finite} if the set $S$ of states and the set $I$ of inputs are
-both finite. Hereinafter, Mealy machines are always supposed to be finite in this paper.
-
-\subsection{Active Learning}
-In this section, we briefly introduce the main ideas of active automata learning.
-
-Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
-a learning algorithm is able to interactively query the target systems to obtain the desired outputs
-under certain inputs. By well-designed query strategy, active learning is able to obtain more
-accurate models with smaller dataset.
-
-\begin{figure}[ht]
-  \begin{center}
-    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
-  \end{center}
-  \caption{Active Automata Learning}
-  \label{fig:activelearning}
-\end{figure}
-
-Fig. \ref{fig:activelearning} shows the sketch of active learning, wherein:
-\begin{itemize}
-  \item[-] \emph{Teacher} and \emph{Student}: Active learning is an interactive process where
-    students ask questions and teachers answer. Here learning algorithm plays the role of student.
-  \item[-] \emph{Oracles} is an interface specifying which kind of questions can be answered by the
-    teacher.
-  \item[-] \emph{SUL} is an abbreviation of System Under Learn. In this paper, we take blackbox
-    models as our SULs.
-  \item[-] \emph{CEGAR} indicates Counter-Example Guided Abstraction
-    Refinement\cite{DBLP:conf/cav/ClarkeGJLV00}. In active learning, we need counter-examples to
-    guide us on further queries and cover the undistinguished states.
-\end{itemize}
-
-When applying active automata learning on some model, we assume that the model should be equivalent
-to some \emph{Mealy machine}, i.e., a deterministic model accepting a finite set of inputs and
-mapping them to a finite set of outputs.
-
-Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
-all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate Teacher}
-interface, which is responsible for two types of queries.
-
-\begin{itemize}
-  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
-    \cite{DBLP:journals/iandc/Angluin87}, \emph{mq} checks if a word is a member of certain language
-    defined by the given grammar. When it comes to
-    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
-    sequences.
-  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
-    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
-    equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
-    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
-    approximate results.
-\end{itemize}
-
-These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Fig.
-\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm constructs a
-\emph{hypothesis} and then check it with \emph{eq}. If counter-examples are found, we turn back and
-repeat the hypothesis construction until the equivalence query returns \emph{true}.
-
-More details on the active automata learning algorithm will be presented in Section
-\ref{sec:activelearning}.
 
@@
 
-\subsection{Time Domain}
-Time has been investigated in several extensions of Reo. For example, timed
-Reo\cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/fmoods/MengA07}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
-Generally, these models are designed to handle real-time behavior where time is defined on the
-real number field $\mathbb{R}$. However, there are also some works like
-\cite{DBLP:journals/fmsd/PrabhakarDM015} where
-rational time indeed  makes things easier. In this paper, we choose the rational number field
-$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behavior greatly.
+\todo{time domain?}
 
-As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
-of timed channels. We use
-$t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
-function $prec$ which calculate a gcd-style \emph{maximal time precision}:
-\[
-prec(t_1,\dots,t_n) = \max\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
-\]
-It's easy to prove that such a $T$ always exists.
+%\subsection{Time Domain}
+%Time has been investigated in several extensions of Reo. For example, timed
+%Reo\cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/fmoods/MengA07}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
+%Generally, these models are designed to handle real-time behavior where time is defined on the
+%real number field $\mathbb{R}$. However, there are also some works like
+%\cite{DBLP:journals/fmsd/PrabhakarDM015} where
+%rational time indeed  makes things easier. In this paper, we choose the rational number field
+%$\mathbb{Q}$ as our time domain, which simplifies discretization of timed behavior greatly.
 
-In embedded systems, the maximal time precision is also called ``clock-period'', which is the basic
-time unit provided by an oscillator. For example, a widely-used Intel-80C51 microcontroller works
-under the frequency 16Mhz, where the clock-period is $62.5$ns. A reasonable assumption comes that
-such a maximal time precision $dt=prec(t_1,\dots,t_n)$ should always be provided to make sure
-different components are able to work together. Then all $t_i$-Timers can be seen as $n_idt$-Timers
-for some $n_i$ and we use $n_i$-Timers instead in the following sections.
+%As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
+%of timed channels. We use
+%$t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
+%function $prec$ which calculate a gcd-style \emph{maximal time precision}:
+%\[
+%prec(t_1,\dots,t_n) = \max\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
+%\]
+%It's easy to prove that such a $T$ always exists.
 
-Besides, we add a timed action ``$T$'' in Mealy machines. It indicates that the corresponding
-transition will take one time unit to finish.
+%In embedded systems, the maximal time precision is also called ``clock-period'', which is the basic
+%time unit provided by an oscillator. For example, a widely-used Intel-80C51 microcontroller works
+%under the frequency 16Mhz, where the clock-period is $62.5$ns. A reasonable assumption comes that
+%such a maximal time precision $dt=prec(t_1,\dots,t_n)$ should always be provided to make sure
+%different components are able to work together. Then all $t_i$-Timers can be seen as $n_idt$-Timers
+%for some $n_i$ and we use $n_i$-Timers instead in the following sections.
+
+%Besides, we add a timed action ``$T$'' in Mealy machines. It indicates that the corresponding
+%transition will take one time unit to finish.
 
@@
 
-\begin{example}[FIFO1]
-  \label{example:pmmfifo}
-  The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
-  \begin{itemize}
-    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
-    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
-    \item[-] output function
-      \begin{small}
-        \begin{displaymath}
-          \delta(\Sigma)(s,i)=\left\{
-          \begin{array}[ht]{ll}
-            \rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
-            \rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
-            \rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
-            \rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
-            \{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
-            \rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
-          \end{array}
-          \right.
-        \end{displaymath}
-      \end{small}
-    \item[-] transition function
-      \begin{small}
-        \begin{displaymath}
-          \lambda(\Sigma)(s,i)=\left\{
-          \begin{array}[ht]{ll}
-            q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
-            q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
-            q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
-            q_0 & otherwise \\
-          \end{array}
-          \right.
-        \end{displaymath}
-      \end{small}
-  \end{itemize}
-\end{example}
+%\begin{example}[FIFO1]
+  %\label{example:pmmfifo}
+  %The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
+  %\begin{itemize}
+    %\item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
+    %\item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
+    %\item[-] output function
+      %\begin{small}
+        %\begin{displaymath}
+          %\delta(\Sigma)(s,i)=\left\{
+          %\begin{array}[ht]{ll}
+            %\rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
+            %\rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
+            %\rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
+            %\rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
+            %\{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
+            %\rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
+          %\end{array}
+          %\right.
+        %\end{displaymath}
+      %\end{small}
+    %\item[-] transition function
+      %\begin{small}
+        %\begin{displaymath}
+          %\lambda(\Sigma)(s,i)=\left\{
+          %\begin{array}[ht]{ll}
+            %q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
+            %q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
+            %q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
+            %q_0 & otherwise \\
+          %\end{array}
+          %\right.
+        %\end{displaymath}
+      %\end{small}
+  %\end{itemize}
+%\end{example}
 
-Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Fig. \ref{fig:pmmfifo},
-where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
-clearance.
-\begin{figure}[ht]
-  \begin{center}
-    \input{./images/pmmfifo.tex}
-  \end{center}
-  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{d\}$}
-  \label{fig:pmmfifo}
-\end{figure}
+%Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Fig. \ref{fig:pmmfifo},
+%where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
+%clearance.
+%\begin{figure}[ht]
+  %\begin{center}
+    %\input{./images/pmmfifo.tex}
+  %\end{center}
+  %\caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{d\}$}
+  %\label{fig:pmmfifo}
+%\end{figure}
 
-\begin{example}[Sync]
-  The PMM of a Sync with a source-end A and a sink-end B can be defined as:
-  \begin{itemize}
-    \item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
-    \item[-] output function
-      \begin{displaymath}
-        \delta(\Sigma)(s,i)=\left\{
-        \begin{array}[ht]{ll}
-          \rempty & i=\{A\mapsto\bot,B\mapsto\rnoread\} \\
-          \{B\mapsto d\} & i=\{A\mapsto d,B\mapsto\rread\}\\
-          \rblock & i=\{A\mapsto\bot,B\mapsto\rread\} \\
-          \rblock & i=\{A\mapsto d,B\mapsto\rnoread\} \\
-        \end{array}
-        \right.
-      \end{displaymath}
-    \item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
-  \end{itemize}
-\end{example}
+%\begin{example}[Sync]
+  %The PMM of a Sync with a source-end A and a sink-end B can be defined as:
+  %\begin{itemize}
+    %\item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
+    %\item[-] output function
+      %\begin{displaymath}
+        %\delta(\Sigma)(s,i)=\left\{
+        %\begin{array}[ht]{ll}
+          %\rempty & i=\{A\mapsto\bot,B\mapsto\rnoread\} \\
+          %\{B\mapsto d\} & i=\{A\mapsto d,B\mapsto\rread\}\\
+          %\rblock & i=\{A\mapsto\bot,B\mapsto\rread\} \\
+          %\rblock & i=\{A\mapsto d,B\mapsto\rnoread\} \\
+        %\end{array}
+        %\right.
+      %\end{displaymath}
+    %\item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
+  %\end{itemize}
+%\end{example}
 
@@
 
-\begin{figure}[ht]
-  \begin{center}
-    \begin{displaymath}
-      \begin{array}{l||ccccc||c}
-        \hline
-        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        \hline\hline
-        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        \hline
-        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        \rowcolor[gray]{.9}
-        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
-        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        \hline
-      \end{array}
-    \end{displaymath}
-    % \input{./images/hypo.tex}
-  \end{center}
-  \caption{Observation Table and Corresponding Hypothesis}
-  \label{fig:hypo}
-\end{figure}
+%\begin{figure}[ht]
+  %\begin{center}
+    %\begin{displaymath}
+      %\begin{array}{l||ccccc||c}
+        %\hline
+        %& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
+        %\hline\hline
+        %\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %\hline
+        %(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %\rowcolor[gray]{.9}
+        %(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
+        %(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %\hline
+      %\end{array}
+    %\end{displaymath}
+    %% \input{./images/hypo.tex}
+  %\end{center}
+  %\caption{Observation Table and Corresponding Hypothesis}
+  %\label{fig:hypo}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-  \begin{center}
-    \begin{displaymath}
-      \begin{array}{l||ccccc||c}
-        \hline
-        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        \hline\hline
-        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        \hline
-        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        (a,\rnoread),(a,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        (a,\rnoread),(\bot,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        (a,\rnoread),(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        (a,\rnoread),(\bot,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty &
-        (a,\rnoread) \\
-        (a,\rnoread),T & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        \hline
-      \end{array}
-    \end{displaymath}
-  \end{center}
-  \caption{A Closed Version of Fig. \ref{fig:hypo}}
-  \label{fig:hypo2}
-\end{figure}
+%\begin{figure}[ht]
+  %\begin{center}
+    %\begin{displaymath}
+      %\begin{array}{l||ccccc||c}
+        %\hline
+        %& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
+        %\hline\hline
+        %\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %\hline
+        %(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %(a,\rnoread),(a,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %(a,\rnoread),(\bot,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %(a,\rnoread),(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %(a,\rnoread),(\bot,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty &
+        %(a,\rnoread) \\
+        %(a,\rnoread),T & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %\hline
+      %\end{array}
+    %\end{displaymath}
+  %\end{center}
+  %\caption{A Closed Version of Fig. \ref{fig:hypo}}
+  %\label{fig:hypo2}
+%\end{figure}
 
@@
 However, when dealing with timed connectors, the algorithm failed to meet our expectation.
-
-\begin{table}[ht]
-  \renewcommand{\arraystretch}{1.3}
-  \caption{Time-Cost Analysis}
-  \label{tabel:timecost}
-  \centering
-  \begin{tabular}{l||rrr}
-    \hline
-    & FIFO1 & Alternator & Gate \\
-    \hline\hline
-    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
-    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
-    Total Time(s) & 41.715 & 165.114 & 247.098 \\
-    Membership Query(\%) & 99.6 & 76.6 & 68.5 \\
-    \hline
-  \end{tabular}
-\end{table}
+\todo{draw the two tables in github}
+%\begin{table}[ht]
+  %\renewcommand{\arraystretch}{1.3}
+  %\caption{Time-Cost Analysis}
+  %\label{tabel:timecost}
+  %\centering
+  %\begin{tabular}{l||rrr}
+    %\hline
+    %& FIFO1 & Alternator & Gate \\
+    %\hline\hline
+    %Membership Query(s) & 41.571 & 126.468 & 169.161 \\
+    %Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
+    %Total Time(s) & 41.715 & 165.114 & 247.098 \\
+    %Membership Query(\%) & 99.6 & 76.6 & 68.5 \\
+    %\hline
+  %\end{tabular}
+%\end{table}
 
@@
 
-\begin{table}[ht]
-  \renewcommand{\arraystretch}{1.3}
-  \caption{Reduction of Membership Queries}
-  \label{tabel:cacheoptimization}
-  \centering
-  \begin{tabular}{l||rrr}
-    \hline
-    & FIFO & Alternator & Gate \\
-    \hline\hline
-    Original Algorithm & 93 & 880 & 1034 \\
-    Cached Algorithm & 90 & 725 & 707 \\
-    Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
-    \hline
-  \end{tabular}
-\end{table}
+%\begin{table}[ht]
+  %\renewcommand{\arraystretch}{1.3}
+  %\caption{Reduction of Membership Queries}
+  %\label{tabel:cacheoptimization}
+  %\centering
+  %\begin{tabular}{l||rrr}
+    %\hline
+    %& FIFO & Alternator & Gate \\
+    %\hline\hline
+    %Original Algorithm & 93 & 880 & 1034 \\
+    %Cached Algorithm & 90 & 725 & 707 \\
+    %Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
+    %\hline
+  %\end{tabular}
+%\end{table}
 
@@
 can be found in Table \ref{tabel:cacheoptimization}.
-
-\subsection{An Example of the Reo Package }
-\label{sec:reolib}
-
-Our implementation in \texttt{Golang} is well-prepared not only for academic use
-but also for practical concurrent programming. The following code shows how to construct an alternator
-connector (see Fig. \ref{fig:reoconnector}) in \texttt{Golang}. An intact version of this example
-can be found in our github repo.
-
-\begin{lstlisting}
-func alternator(A, B, C Port) {
-  M := MakePorts(6)
-
-  // definition of channels
-  go ReplicatorChannel(A, M[0], M[1])
-  go ReplicatorChannel(B, M[2], M[3])
-  go MergerChannel(M[4], M[5], C)
-
-  go SyncdrainChannel(M[1], M[2])
-  go SyncChannel(M[0], M[4])
-  go FifoChannel(M[3], M[5])
-}
-\end{lstlisting}
-
-Provided with the source and sink nodes, \emph{alternator} function creates a series of basic
-channels and mixed nodes (named \emph{Port}) to serve as the alternator connector we need. Now we
-can activate the components and using \emph{alternator} function to coordinate them.
-
-\begin{lstlisting}
-A,B,C := MakePorts(3)
-alternator(A, B, C)
-
-go sender(A, "MSG A")
-go sender(B, "MSG B")
-go monitor(C)
-\end{lstlisting}
-
-In this case, \emph{senders} are goroutines (basic parallel units in \texttt{Golang}) that keep
-sending certain messages to some given port (A and B). A \emph{monitor} keeps trying to read data
-items from the sink end C and print them on the screen. Finally, we have an interleaved sequence of
-``MSG\_A'' and ``MSG\_B''.
 
@@
 We also adapt the well-known active learning algorithm L* to deal with time domain.
-When time is taken into consideration, the original L* algorithm run into a performance bottleneck.
+% When time is taken into consideration, the original L* algorithm run into a performance bottleneck.
 By a tree-style cache, we make significant reduction on membership queries and, in turn,

### 2016-04-04 paper/paper.tex
.

@@
 Distributed real-time embedded systems (DRES) are reforming our lives with the
-Internet of Things(IoT), wherein individual components are composed via \emph{connectors} 
+Internet of Things, wherein individual components are composed via \emph{connectors}
 to build complex systems. Such systems could be distributed logically or physically, which
@@
 
-\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, which can be used
+\emph{Timed Reo} \cite{DBLP:conf/sefm/ArbabBBR04} is a real-time extension of the coordination language \emph{Reo}
+\cite{DBLP:journals/mscs/Arbab04}, which can be used
 to describe the coordination process in DRES clearly and intuitively. Different formal
 semantics have been proposed to specify the behavior of timed Reo.
-For example, an operational semantics based on \emph{timed constraint automata} was raised by Baier et
-al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
+For example, an operational semantics based on \emph{timed constraint automata} was proposed in 
+\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
 properties of timed connectors.
 In \cite{DBLP:conf/tase/Meng12}, a UTP design model was proposed to specify the behavior of timed
-connectors..
+connectors.
 
 Formal verification and validation techniques have also been proved applicable for timed connectors,
-e.g. a comformance testing framework on timed connectors has been proposed in \cite{DBLP:conf/tase/LiCWS15}.
-A SAT-based bounded model checking approach was adapted in \cite{DBLP:journals/scp/Kemper12} for
-verifying connectors. Although these solutions are practical and impressive, there is one important
+e.g. a conformance testing framework on timed connectors has been proposed in \cite{DBLP:conf/tase/LiCWS15}.
+A SAT-based bounded approach was adapted in \cite{DBLP:journals/scp/Kemper12} for model checking
+connectors. Although these solutions are practical and impressive, there is one important
 question faced by most of them: \emph{how to obtain the formal models?}
@@
   \begin{center}
-    \includegraphics[width=.4\textwidth]{./images/howto.png}
+    \includegraphics[width=.45\textwidth]{./images/howto.png}
   \end{center}
@@
 The rest of the paper is organized as follows: In Section
-\ref{sec:preliminaries} we briefly illustrate some basic concepts, including the coordination
-language Reo, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines an
-operational semantics of Reo, which is used in Section \ref{sec:activelearning} to show how to
+\ref{sec:preliminaries} we illustrate some basic concepts, including the coordination
+language Reo, Mealy machine, and active automata learning. Section \ref{sec:semantics} briefly presents an
+operational semantics of Reo based on PMM, which is used in Section \ref{sec:activelearning} to show how to
 extract Reo models from blackboxes by means of active learning. In Section
@@
     simultaneously through the other end. Then both items will be dropped.
-  \item [-] A \emph{FIFO1} channel is an asychronous channel with a buffer cell. It accepts a
+  \item [-] A \emph{FIFO1} channel is an asynchronous channel with a buffer cell. It accepts a
     data item whenever the buffer is empty.
@@
 on this node. Similarly, a component can read a data item only if there is at least one readable
-sink end on its corresponding node. A mixed node non-determinstically selects and takes a data item
+sink end on its corresponding node. A mixed node non-deterministically selects and takes a data item
 from one of its coincident sink ends and replicates it into all of its coincident source ends.
@@
 under certain inputs. By well-designed query strategy, active learning is able to obtain more
-accurate models with smaller dataset.
+accurate models with smaller data-set.
 
@@
 Time has been investigated in several extensions of Reo. For example, timed
-Reo\cite{DBLP:conf/sefm/ArbabBBR04, DBLP:conf/fmoods/MengA07}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
+Reo\cite{DBLP:conf/sefm/ArbabBBR04}, resource-sensitive timed Reo\cite{DBLP:conf/fmoods/MengA07}, hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
 Generally, these models are designed to handle real-time behavior where time is defined on the
@@
 s\}$\footnote{When there are multiple satisfying sequences with the same length, we use a certain tactic
-to pick up one from them determinstically.}.
+to pick up one from them deterministically.}.
 
@@
 
-Now we consider the reason that leads to existance of counter examples. Since
-the suffix set $D$ is used to distinguish states, the existance of counter-examples
+Now we consider the reason that leads to existence of counter examples. Since
+the suffix set $D$ is used to distinguish states, the existence of counter-examples
 shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
@@
 Golang\cite{golang}, which is widely known for its elegant design and impressive efficiency.
-Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model, \texttt{Golang} shares many
+Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} concurrency model, \texttt{Golang} shares many
 similar ideas with Reo, and in turn makes our implementation much more natural.
@@
 If previous simulation results are stored in a well-maintained cache, the time-cost in
-simulation process could be reduced signficiantly. In this work, we use a multiway tree to buffer
+simulation process could be reduced significantly. In this work, we use a multiway tree to buffer
 these results.
@@
 Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
-machines with timed action T provided.
-
-We also adapt the well-known active learning algorithm L* to deal with time domain.
-When time is taken into consideration, the original L* algorithm run into a performance bottleneck.
+machines with timed action $T$ provided.
+
+We also adapt the well-known active learning algorithm $L*$ to deal with time domain.
+When time is taken into consideration, the original $L*$ algorithm run into a performance bottleneck.
 By a tree-style cache, we make significant reduction on membership queries and, in turn,

### 2016-04-04 shortpaper/paper.tex
.

@@
   Coordination models and languages play a key role in formally specifying the communication and
-  interaction among different components in large-scale distributed and concurrent systems. In this
+  interaction among different components in large-scale concurrent systems. In this
   paper, we use active learning to extract timed connector models from black-box
   system implementation. 
-  We first introduce parameterized Mealy machine(PMM) as an operational semantic
-  model for channel-based coordination language Reo. PMM serves as a bridge
-  between Reo connectors and Mealy machines. With the product operator, complex connectors can be
-  constructed by joining basic channels and the PMMs of connectors can be transformed into Mealy
-  machines. Moreover, we adapt L*, a well-known learning algorithm, to timed connectors (in the form
-  of Mealy machines). The new algorithm has shown its efficiency in multiple case studies. 
+  Firstly, parameterized Mealy machines(PMM) is introduced as an operational semantic
+  model for channel-based coordination language Reo. With product and link operators defined, we can
+  construct complex connectors by joining basic channels in form of PMM. Moreover, with a
+  concretize mapping function, PMMs can be easily transformed into Mealy machines, and the latter can be
+  extracted by an optimized L* algorithm.
 \end{abstract}
@@
 Internet of Things(IoT), wherein individual components are composed via \emph{connectors} 
-to build complex systems. Such systems could be distributed logically or physically, which
-makes coordination processes even more complicated. In this case, we need to specify the coordination
+to build complex systems. 
+%Such systems could be distributed logically or physically, which
+%makes coordination processes even more complicated. 
+In this case, we need to specify the coordination
 processes with \emph{coordination languages}, such that formal techniques can be applied to
@@
 
-\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}, which can be used
-to describe the coordination process in DRES clearly and intuitively. 
-\todo{describe semantics in a more short way}
-%Different formal semantics have been proposed to specify the behavior of timed Reo.
-%For example, an operational semantics based on \emph{timed constraint automata} was raised by Baier et
-%al.\cite{DBLP:conf/sefm/ArbabBBR04}, where a variant of LTL was also proposed to describe the
-%properties of timed connectors.
-%In \cite{DBLP:conf/tase/Meng12}, a UTP design model was proposed to specify the behavior of timed
-%connectors..
-
+As a real-time extension of \emph{Reo}, \emph{Timed
+Reo}\cite{DBLP:conf/sefm/ArbabBBR04,DBLP:conf/tase/Meng12} is used in this paper to formalize
+connectors in DRES. 
+Reo is a channel based exogenous coordination language proposed by F. Arbab in
+\cite{DBLP:journals/mscs/Arbab04}, which is a powerful ``glue language'' in component-based
+development\cite{DBLP:journals/sigsoft/Gill03}. What's more, 
 Formal verification and validation techniques have also been proved applicable for timed connectors, 
@@
 A SAT-based bounded model checking approach was adapted in \cite{DBLP:journals/scp/Kemper12} for
-verifying connectors. Although these solutions are practical and impressive, there is one important
-question faced by most of them: \emph{how to obtain the formal models?}
+verifying connectors.
 
+However, most of these tools heavily rely on manually modelling.
 \emph{Correctness} of connectors is closely related to some low-level implementation details.
@@
 
-As a branch of \emph{machine learning} technique, active learning offers a means to obtain
-high-level models from low-level models. Works in \cite{de2010grammatical,
-DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06} show interesting examples where active
-learning is used to extract \emph{Mealy machines} or \emph{regular languages} without time domain.
-
-%\begin{figure}[ht]
-  %\begin{center}
-    %\includegraphics[width=.4\textwidth]{./images/howto.png}
-  %\end{center}
-  %\caption{The Active Learning Framework}
-  %\label{fig:howto}
-%\end{figure}
-
-In this paper we address this question by proposing an active learning framework as shown in Fig.
-\ref{fig:howto} to automatically extract timed connector models from blackbox implementations. 
-To achieve this goal, we first introduce \emph{parameterized Mealy machine} as a parameterized
-semantics for timed Reo connectors, which can be transformed to concrete Mealy machines with a
-given alphabet. Then the $L*$ algorithm \cite{DBLP:journals/iandc/Angluin87} is adapted and
+In this paper we address this question by means of active learning \cite{de2010grammatical,
+DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.
+First of all, we introduce \emph{parameterized Mealy machine} as a parameterized
+semantics for timed Reo, which can be transformed to concrete Mealy machines with a
+specified alphabet. Then the $L*$ algorithm \cite{DBLP:journals/iandc/Angluin87} is adapted and
 optimized to extract Mealy machines with timed action from the connector implementations as
@@
 
-\todo{use a short paragraph to describe the preliminaries}
-
 The rest of the paper is organized as follows: In Section
-\ref{sec:preliminaries} we briefly illustrate some basic concepts, including the coordination
-language Reo, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines an
+Section \ref{sec:semantics}, we defines an
 operational semantics of Reo, which is used in Section \ref{sec:activelearning} to show how to
 extract Reo models from blackboxes by means of active learning. In Section
-\ref{sec:experiment}, we discuss the implementation and optimization of the approach in
-\texttt{Golang}. Finally, Section VI concludes the paper.
+\ref{sec:experiment}, we discuss the implementation and optimization of the approach. 
+Finally, Section VI concludes the paper. Due to the limit of space, many technical details are
+omitted in this paper.
+Please refer to \todo{github repo} for further contents.
 
@@
 However, under such notations, there are \emph{infinite} number of states, among which most are
-reduplicate.
+duplicate.
 

### 2016-04-04 shortpaper/paper.tex
.

@@
 \usepackage[textsize=tiny]{todonotes}
+\usepackage{xcolor}
+\newcommand{\liyi}[1]{\textcolor{red}{Liyi: {#1}}}
 
@@
 \cite{DBLP:journals/mscs/Arbab04}, which is a powerful ``glue language'' in component-based
-development\cite{DBLP:journals/sigsoft/Gill03}. What's more, 
-Formal verification and validation techniques have also been proved applicable for timed connectors, 
-e.g. a comformance testing framework on timed connectors has been proposed in \cite{DBLP:conf/tase/LiCWS15}.
-A SAT-based bounded model checking approach was adapted in \cite{DBLP:journals/scp/Kemper12} for
-verifying connectors.
+development\cite{DBLP:journals/sigsoft/Gill03}. 
+\begin{figure}[ht]
+  \begin{center}
+    \input{./images/basic.tex}
+  \end{center}
+  \caption{Basic Reo Channels}
+  \label{fig:basic}
+\end{figure}
 
+Formal verification and validation techniques have also been proved applicable for timed connectors
+\cite{DBLP:conf/tase/LiCWS15,DBLP:journals/scp/Kemper12} 
 However, most of these tools heavily rely on manually modelling.
@@
 
-In this paper we address this question by means of active learning \cite{de2010grammatical,
-DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.
+In this paper we address this question by means of active learning
+\cite{DBLP:journals/iandc/Angluin87, DBLP:conf/fase/RaffeltS06}.
 First of all, we introduce \emph{parameterized Mealy machine} as a parameterized
@@
 
-The rest of the paper is organized as follows: In Section
-Section \ref{sec:semantics}, we defines an
+The rest of the paper is organized as follows: In Section \ref{sec:semantics}, we defines an
 operational semantics of Reo, which is used in Section \ref{sec:activelearning} to show how to
@@
 omitted in this paper.
-Please refer to \todo{github repo} for further contents.
+Please refer to \cite{reo-learn-github} for further contents.
 
@@
 
-In this section, we illustrate how to transform a timed connector into a Mealy machine with timed
-action.
-Since time is not involved in original Mealy machine, we first discuss how to formalize the time
-dimension in Mealy machine. After that, we present the notion of \emph{parameterized Mealy
-machine} as a bridge between connectors and Mealy machines.
-
-\todo{time domain?}
+In this section, we introduce PMM as an intermediate form to transform timed connectors into
+Mealy machines with timed action. In this paper, we assume that time dimension is defined on the
+national number $\mathbb{Q}$, which is generally as expressive as $\mathbb{R}$ and much easier to
+formalize\cite{DBLP:journals/fmsd/PrabhakarDM015}. Since connectors contain only finite number of
+channels, we can always find a minimal time unit (denoted as $T$) where real-time connectors can be
+discretized.
 
@@
 \subsection{Parameterized Mealy Machine}
-We present a model named \emph{parameterized Mealy machine} to model timed connectors. PMM is
-supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
-defined as PMMs, and composed by \emph{product} and \emph{link} operators. Then, concrete
-Mealy-machine model can be generated from the PMM model.
-Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the
-\emph{parameterized Mealy machine} as follows.
+In this work, we use \emph{Mealy machines} to model Reo connectors.
+Mealy machine is an extension of finite state machine to model reactive systems.
+Following its definition in \cite{DBLP:conf/sfm/SteffenHM11}, we present a model here named
+\emph{parameterized Mealy machine} to formalize timed connectors.
 
@@
 and output actions from the corresponding alphabets and source/sink ends. $Input(\Sigma,I,O)$ is
-defined as a set of functions on $I\cup O$ and an additional \emph{time action} T,  
-where for all $f\in Input(\Sigma,I,O)\backslash \{T\}$ we have
+defined as the intersection of the set of input events $Evt_{in}$ and an additional \emph{time
+action} T. Here every $in\in Evt_{in}$ is an evaluation on both sink and source ends and
 \[
-\forall i\in I.f(i)\in \Sigma\cup\{\bot\}\land \forall o\in O.f(o)\in\{\rread, \rnoread\}
+\forall i\in I.in(i)\in\Sigma\cup\{\rempty\}\land \forall o\in O.in(o)\in\{\rnoread, \rread\}
 \]
@@
 In the same way,
-$Output(\Sigma,O)$ is defined as a set of functions on $O$, with an additional symbol
-$\rblock$ indicating an input failure. Similarly, for all $f\in
-Output(\Sigma,O)\backslash\{\rblock\}$,
-\[
-\forall o\in O. f(o)\in \Sigma\cup\{\bot\}
-\]
+$Output(\Sigma,O)$ is defined as a set of output events in form of evaluations on $O$, with an
+additional symbol $\rblock$ indicating an input failure.
 
-A non-timed input action $a\in Input(\Sigma,I,O)$ can be restricted to $I'\subseteq I$, denoted by
-$a\downarrow_{I'}$ which is defined on $Input(\Sigma,I',O)$ and satisfies
-\[
-\forall i\in I'. a\downarrow_{I'}(i)=a(i)
-\]
-Restriction on output actions can be defined similarly.
+%A non-timed input action $a\in Input(\Sigma,I,O)$ can be restricted to $I'\subseteq I$, denoted by
+%$a\downarrow_{I'}$ which is defined on $Input(\Sigma,I',O)$ and satisfies
+%\[
+%\forall i\in I'. a\downarrow_{I'}(i)=a(i)
+%\]
+%Restriction on output actions can be defined similarly.
 
@@
   \[
-  Output(\{d_0\},\{A\},\{B\}) =\{\{B\mapsto d_0\},\{B\mapsto \bot\}, \rblock\}
+  Output(\{d_0\},\{A\},\{B\}) =\{\{B\mapsto d_0\},\varnothing, \rblock\}
   \]
@@
 We use $\varnothing$ to denote the empty output when no data item is written to any sink end.
-For example, in this case $\{B\mapsto\bot\}$ can be briefly denoted as $\rempty$.
+For example, in the above case $\varnothing$ is used to denote $\{B\mapsto\bot\}$.
 
-Parameterized Mealy machines can be seen as an abstraction of Mealy machines, and we
+Parameterized Mealy machines can be seen as an abstraction of Mealy machines, hence we
 still need a convert function between the two models.
@@
 
-Now we can use PMMs to specify timed Reo. Here we take the asynchronous channel (FIFO1), the
-synchronous channel (Sync) and the timed channel (Timer) as examples. For simplicity, we use $A=\_$
-to indicate that there is no constraint on channel end $A$.
-
-%\begin{example}[FIFO1]
-  %\label{example:pmmfifo}
-  %The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
-  %\begin{itemize}
-    %\item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
-    %\item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
-    %\item[-] output function
-      %\begin{small}
-        %\begin{displaymath}
-          %\delta(\Sigma)(s,i)=\left\{
-          %\begin{array}[ht]{ll}
-            %\rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
-            %\rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
-            %\rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
-            %\rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
-            %\{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
-            %\rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
-          %\end{array}
-          %\right.
-        %\end{displaymath}
-      %\end{small}
-    %\item[-] transition function
-      %\begin{small}
-        %\begin{displaymath}
-          %\lambda(\Sigma)(s,i)=\left\{
-          %\begin{array}[ht]{ll}
-            %q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
-            %q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
-            %q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
-            %q_0 & otherwise \\
-          %\end{array}
-          %\right.
-        %\end{displaymath}
-      %\end{small}
-  %\end{itemize}
-%\end{example}
-
-%Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Fig. \ref{fig:pmmfifo},
-%where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
-%clearance.
-%\begin{figure}[ht]
-  %\begin{center}
-    %\input{./images/pmmfifo.tex}
-  %\end{center}
-  %\caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{d\}$}
-  %\label{fig:pmmfifo}
-%\end{figure}
-
-%\begin{example}[Sync]
-  %The PMM of a Sync with a source-end A and a sink-end B can be defined as:
-  %\begin{itemize}
-    %\item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
-    %\item[-] output function
-      %\begin{displaymath}
-        %\delta(\Sigma)(s,i)=\left\{
-        %\begin{array}[ht]{ll}
-          %\rempty & i=\{A\mapsto\bot,B\mapsto\rnoread\} \\
-          %\{B\mapsto d\} & i=\{A\mapsto d,B\mapsto\rread\}\\
-          %\rblock & i=\{A\mapsto\bot,B\mapsto\rread\} \\
-          %\rblock & i=\{A\mapsto d,B\mapsto\rnoread\} \\
-        %\end{array}
-        %\right.
-      %\end{displaymath}
-    %\item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
-  %\end{itemize}
-%\end{example}
+Now we can use PMMs to specify timed Reo. Here we take the timed channel (Timer) as an example. In
+timed Reo, a n-timer accepts a data item from its source end, and then put it to its sink end after
+n time units. Throughout the duration, the channel cannot accept any more data items.
+For simplicity, we use $A=\_$ to indicate that there is no constraint on channel end $A$.
 
@@
 
-\begin{definition}[Product]
-  For two PMMs $\mathcal{PM}_1$ and $\mathcal{PM}_2$, if
-  $\mathcal{PM}_2.O\cap\mathcal{PM}_1.I=\varnothing$, their product 
-  \[
-  \mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)  \]
-  can be defined as follows.
-  \begin{itemize}
-  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}_1.S(\Sigma)\times \mathcal{PM}_2.S(\Sigma)$
-    \item[-] $\mathcal{PM}'.I=(\mathcal{PM}_1.I\cup \mathcal{PM}_2.I)\backslash \mathcal{PM}_1.O$
-    \item[-] $\mathcal{PM}'.O=(\mathcal{PM}_1.O\cup \mathcal{PM}_2.O)\backslash \mathcal{PM}_2.I$
-  \end{itemize}
-  \emph{(Here we assume that sink ends of $\mathcal{PM}_1$ can be connected to source ends of
-  $\mathcal{PM}_2$, but not vise versa)}
-  \begin{itemize}
-    \item[-] $\mathcal{PM}'.s_0=(\mathcal{PM}_1.s_0, \mathcal{PM}_2.s_0)$
-    \item[-] $\forall\Sigma. \mathcal{PM}'.\delta(\Sigma)((s_1,s_2), i)=$
-      \begin{displaymath}
-        \left\{
-        \begin{array}[ht]{ll}
-          (\bigcup_{j=1,2} Out_j)\downarrow_{\mathcal{PM}'.O} & i\neq T\land(\bigwedge_{j=1,2} Out_j\neq\rblock) \\
-          \rempty & i = T \\
-          \rblock & otherwise \\
-        \end{array}
-        \right.
-      \end{displaymath}
-      where we have
-      \begin{itemize}
-        \item[*] $i\in Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O)$
-        \item[*] $In_1 = i\downarrow_{\mathcal{PM}_1.I}$
-        \item[*] $In_2 = (Out_1 \cup i)\downarrow_{\mathcal{PM}_2.I}$
-        \item[*] $Out_j = \mathcal{PM}_j.\delta(\Sigma)(s_j,In_j)$ for $j=1,2$
-      \end{itemize}
-    \item[-] $\forall\Sigma. \mathcal{PM}'. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
-      where for $j=1,2$, $s_j' = \mathcal{PM}_j.\lambda(\Sigma)(s_j,In_j)$.
-  \end{itemize}
-\end{definition}
+\liyi{Actually I'm not sure if omitting definition of prod and link is a good idea. Generally I
+think this paper should focus on two parts: definition of PMM and optimization of L* algorithm.}
 
-The idea in \emph{product} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
-input of $\mathcal{PM}_2$. Timed action $T$ is only executed simultaneously between $\mathcal{PM}_1$
-and $\mathcal{PM}_2$.
+%\begin{definition}[Product]
+  %For two PMMs $\mathcal{PM}_1$ and $\mathcal{PM}_2$, if
+  %$\mathcal{PM}_2.O\cap\mathcal{PM}_1.I=\varnothing$, their product 
+  %\[
+  %\mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)  \]
+  %can be defined as follows.
+  %\begin{itemize}
+    %\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}_1.S(\Sigma)\times \mathcal{PM}_2.S(\Sigma)$
+    %\item[-] $\mathcal{PM}'.I=(\mathcal{PM}_1.I\cup \mathcal{PM}_2.I)\backslash \mathcal{PM}_1.O$
+    %\item[-] $\mathcal{PM}'.O=(\mathcal{PM}_1.O\cup \mathcal{PM}_2.O)\backslash \mathcal{PM}_2.I$
+  %\end{itemize}
+  %\emph{(Here we assume that sink ends of $\mathcal{PM}_1$ can be connected to source ends of
+  %$\mathcal{PM}_2$, but not vise versa)}
+  %\begin{itemize}
+    %\item[-] $\mathcal{PM}'.s_0=(\mathcal{PM}_1.s_0, \mathcal{PM}_2.s_0)$
+    %\item[-] $\forall\Sigma. \mathcal{PM}'.\delta(\Sigma)((s_1,s_2), i)=$
+      %\begin{displaymath}
+        %\left\{
+        %\begin{array}[ht]{ll}
+          %(\bigcup_{j=1,2} Out_j)\downarrow_{\mathcal{PM}'.O} & i\neq T\land(\bigwedge_{j=1,2} Out_j\neq\rblock) \\
+          %\rempty & i = T \\
+          %\rblock & otherwise \\
+        %\end{array}
+        %\right.
+      %\end{displaymath}
+      %where we have
+      %\begin{itemize}
+        %\item[*] $i\in Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O)$
+        %\item[*] $In_1 = i\downarrow_{\mathcal{PM}_1.I}$
+        %\item[*] $In_2 = (Out_1 \cup i)\downarrow_{\mathcal{PM}_2.I}$
+        %\item[*] $Out_j = \mathcal{PM}_j.\delta(\Sigma)(s_j,In_j)$ for $j=1,2$
+      %\end{itemize}
+    %\item[-] $\forall\Sigma. \mathcal{PM}'. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
+      %where for $j=1,2$, $s_j' = \mathcal{PM}_j.\lambda(\Sigma)(s_j,In_j)$.
+  %\end{itemize}
+%\end{definition}
 
-As mentioned above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
-$\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Fig.
-\ref{fig:reoconnector}. To solve the problem, we define a \emph{link} operator to connect sink
-ends and source ends in the same connector.
+%The idea in \emph{product} is quite simple. The output of $\mathcal{PM}_1$ would be provided as part of the
+%input of $\mathcal{PM}_2$. Timed action $T$ is only executed simultaneously between $\mathcal{PM}_1$
+%and $\mathcal{PM}_2$.
 
-\begin{definition}[Link]
-  The \emph{link} operator constructs connector by connecting a sink end $\OUT$ to a source end $\IN$
-  within the same connector.   
-  \[
-  \mathcal{PM}' = link(\mathcal{PM}, \OUT, \IN)
-  \]
-  Here we assume that $\IN\in \mathcal{PM}.I$ and $\OUT\in \mathcal{PM}.O$.
+%As mentioned above, we cannot connect a sink end of $\mathcal{PM}_2$ to a source end of
+%$\mathcal{PM}_1$, which makes it difficult to construct connectors like alternator in Fig.
+%\ref{fig:reoconnector}. To solve the problem, we define a \emph{link} operator to connect sink
+%ends and source ends in the same connector.
 
-  \begin{itemize}
-  	\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}.S(\Sigma)$
-    \item[-] $\mathcal{PM}'.I=\mathcal{PM}.I\backslash\{\IN\}$
-    \item[-] $\mathcal{PM}'.O=\mathcal{PM}.O\backslash\{\OUT\}$
-    \item[-] $\mathcal{PM}'.s_0=\mathcal{PM}.s_0$
-    \item[-] $\forall\Sigma, i\in
-      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
-      \begin{small}
-        \begin{displaymath}
-          \left\{
-          \begin{array}[h]{lr}
-            \rempty & i=T \\
-            \mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
-            \rblock & otherwise \\
-          \end{array}
-          \right.
-        \end{displaymath}
-      \end{small}
-      where the condition (*) is defined as
-      \[
-      \exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})(\OUT)=d
-      \]
-    \item[-] $\forall\Sigma, i\in
-      Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
-      \begin{small}
-        \begin{displaymath}
-          \mathcal{PM}.\lambda(\Sigma)(s,i)=
-          \left\{
-          \begin{array}[ht]{lr}
-            \mathcal{PM}.\lambda(\Sigma,T) & i=T \\
-            \mathcal{PM}.\lambda(\Sigma,i\cup\{\IN\mapsto d\}) & (*)\\
-            s & otherwise \\
-          \end{array}
-          \right.
-        \end{displaymath}
-      \end{small}
-  \end{itemize}
-\end{definition}
+%\begin{definition}[Link]
+  %The \emph{link} operator constructs connector by connecting a sink end $\OUT$ to a source end $\IN$
+  %within the same connector.   
+  %\[
+  %\mathcal{PM}' = link(\mathcal{PM}, \OUT, \IN)
+  %\]
+  %Here we assume that $\IN\in \mathcal{PM}.I$ and $\OUT\in \mathcal{PM}.O$.
+
+  %\begin{itemize}
+    %\item[-] $\forall\Sigma. \mathcal{PM}'.S(\Sigma)=\mathcal{PM}.S(\Sigma)$
+    %\item[-] $\mathcal{PM}'.I=\mathcal{PM}.I\backslash\{\IN\}$
+    %\item[-] $\mathcal{PM}'.O=\mathcal{PM}.O\backslash\{\OUT\}$
+    %\item[-] $\mathcal{PM}'.s_0=\mathcal{PM}.s_0$
+    %\item[-] $\forall\Sigma, i\in
+      %Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).\mathcal{PM}'.\delta(\Sigma)(s,i)=$
+      %\begin{small}
+        %\begin{displaymath}
+          %\left\{
+          %\begin{array}[h]{lr}
+            %\rempty & i=T \\
+            %\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})\downarrow_{\mathcal{PM}'.O} & (*)\\
+            %\rblock & otherwise \\
+          %\end{array}
+          %\right.
+        %\end{displaymath}
+      %\end{small}
+      %where the condition (*) is defined as
+      %\[
+      %\exists d.\mathcal{PM}.\delta(\Sigma)(s,i\cup\{\IN\mapsto d\})(\OUT)=d
+      %\]
+    %\item[-] $\forall\Sigma, i\in
+      %Input(\Sigma,\mathcal{PM}'.I,\mathcal{PM}'.O).$
+      %\begin{small}
+        %\begin{displaymath}
+          %\mathcal{PM}.\lambda(\Sigma)(s,i)=
+          %\left\{
+          %\begin{array}[ht]{lr}
+            %\mathcal{PM}.\lambda(\Sigma,T) & i=T \\
+            %\mathcal{PM}.\lambda(\Sigma,i\cup\{\IN\mapsto d\}) & (*)\\
+            %s & otherwise \\
+          %\end{array}
+          %\right.
+        %\end{displaymath}
+      %\end{small}
+  %\end{itemize}
+%\end{definition}
 
@@
 
-\subsection{Observation Table}
-\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
-hypothetical Mealy machines from the results of membership queries.
+\subsection{Active Learning: Overview}
+In this section, we briefly introduce the main ideas of active automata learning.
 
-Mealy machines consist of \emph{states} and \emph{transitions}.
-As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
-after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
-state of $s$ after executing $a$.
-However, under such notations, there are \emph{infinite} number of states, among which most are
-duplicate.
+Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
+a learning algorithm is able to interactively query the target systems to obtain the desired outputs
+under certain inputs. By well-designed query strategy, active learning is able to obtain more
+accurate models with smaller data-set.
 
-States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
-\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
-\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
-alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
-\begin{definition}[$D$-Equivalence]
-  Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
-  $s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
-  iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
-\end{definition}
+\begin{figure}[ht]
+  \begin{center}
+    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
+  \end{center}
+  \caption{Active Automata Learning}
+  \label{fig:activelearning}
+\end{figure}
 
-Now we use \emph{access sequence} to describe the states. Given an input sequence $s$, the access
-sequence $acc(s,D)$ of $s$ is defined as the shortest sequence in $\{s'\in\mathcal{I}^*|s'\sim_D
-s\}$\footnote{When there are multiple satisfying sequences with the same length, we use a certain tactic
-to pick up one from them determinstically.}.
-
-Formally, an observation table (see Fig. \ref{fig:hypo} as an example) is determined by a tuple $(S,D)$ where
-$S\subset\mathcal{I}^*$ is a set of the access sequences of states and $D\subset\mathcal{I}^*$
-is a set of suffixes. In such tables, columns are labelled with suffixes in $D$, and rows are
-labelled with input sequences. As shown in Fig. \ref{fig:hypo}, rows are divided into two parts. The upper
-part, labelled with access sequence $s\in S$, denotes the states covered in the current hypothesis.
-The lower part, labelled with sequences in $\{sa|s\in S,a\in\mathcal{I}\}\backslash S$ (representing
-any potentially unclosed transition) denotes all the transitions outside $s\in S$. A cell with row
-label $s$ and column label $d$ is filled with $mq(sd)$.
-
-An observation table $(S,D)$ is \emph{closed} if 
-\[
-\forall s\in S,a\in\mathcal{I}.\exists s'\in S. sa\sim_D s'
-\]
-
-From a closed observation table $obs$, we can construct a hypothetical Mealy machine $\mathcal{H}=\langle
-S,s_0,\mathcal{I},\mathcal{O},\delta,\lambda\rangle$ in a straight-forward way:
+Fig. \ref{fig:activelearning} shows the sketch of active learning, wherein:
 \begin{itemize}
-  \item[-] Every state in $S$ corresponds to an input sequence in $obs.S$
-  \item[-] $s_0$ corresponds to the empty sequence $\varepsilon$
-
-    \emph{(we use input sequences to indicate their corresponding states in following parts)}
-  \item[-] $\delta(s,a)=mq(sa)$
-  \item[-] $\lambda(s,a)=acc(sa,obs.D)$. Since $obs$ is closed, we always have $\lambda(s,a)\in S$.
+  \item[-] \emph{Teacher} and \emph{Student}: Active learning is an interactive process where
+    students ask questions and teachers answer. Here learning algorithm plays the role of student.
+  \item[-] \emph{Oracles} is an interface specifying which kind of questions can be answered by the
+    teacher.
+  \item[-] \emph{SUL} is an abbreviation of System Under Learn. In this paper, we take blackbox
+    models as our SULs.
+  \item[-] \emph{CEGAR} indicates Counter-Example Guided Abstraction
+    Refinement\cite{DBLP:conf/cav/ClarkeGJLV00}. In active learning, we need counter-examples to
+    guide us on further queries and cover the undistinguished states.
 \end{itemize}
 
-Algorithm \ref{alg:buildtable} shows how to build a closed observation table.
+When applying active automata learning on some model, we assume that the model should be equivalent
+to some \emph{Mealy machine}, i.e., a deterministic model accepting a finite set of inputs and
+mapping them to a finite set of outputs.
 
-\begin{algorithm} 
-  \caption{EncloseTable} 
-  \label{alg:buildtable}
-  \small
-  \KwIn{An oracle interface $mq$, An input actions $\mathcal{I}$, An observation table $obs$}
-  \KwOut{A closed observation table $obs'$} 
-  \Repeat{$unclosed=\varnothing$}
-  {
-    $next=\{st|\forall s\in obs.S,\forall t\in \mathcal{I}\}\backslash obs.S$\;
-    $unclosed=\{seq\in next|\forall a\in obs.S, seq \not\sim_{obs.D} a\}$\;
-    $obs'.S$ = $obs.S\cup unclosed$\;
-    $obs'.D$ = $obs.D$\;
-  }
-  \Return $obs'$\; 
-\end{algorithm}
+Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
+all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate Teacher}
+interface, which is responsible for two types of queries.
 
-Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
-We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$, and the alphabet
-is $\{a\}$. We briefly denote $\{A\mapsto a,B\mapsto \rnoread\}$ and other input/output actions in form of
-$(a,\rnoread)$.
+\begin{itemize}
+  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
+    \cite{DBLP:journals/iandc/Angluin87}, \emph{mq} checks if a word is a member of certain language
+    defined by the given grammar. When it comes to
+    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
+    sequences.
+  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
+    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
+    equivalent to the system-under-learn and generates a counter-example if needed. Generally,
+    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
+    approximate results.
+\end{itemize}
 
-Firstly, $obs.S$ is initialized with the initial state (denoted by $\varepsilon$), and $obs.D$ is
-initialized with all one-step suffixes.
-Then we explore all the access sequences in $obs.S$ and calculate its successors. Here
-$unclosed$ consists of access sequences that has no equivalent sequence in $obs.S$. 
-For example, Fig. \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
-iteration. The five successors of $\varepsilon$ are presented at the bottom of the table, where
-four are equivalent with $\varepsilon$ but $(a,\rnoread)$ is not. Therefore, we take $(a,\rnoread)$ as a
-brand-new state and all of its successors need further exploration.
+These queries are given by \emph{learning algorithms}, or so-called \emph{students} in Fig.
+\ref{fig:activelearning}. From the \emph{mq} results, a learning algorithm constructs a
+\emph{hypothesis} and then check it with \emph{eq}. If counter-examples are found, we turn back and
+repeat the hypothesis construction until the equivalence query returns \emph{true}.
 
-%\begin{figure}[ht]
-  %\begin{center}
-    %\begin{displaymath}
-      %\begin{array}{l||ccccc||c}
-        %\hline
-        %& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        %\hline\hline
-        %\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %\hline
-        %(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %\rowcolor[gray]{.9}
-        %(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
-        %(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %\hline
-      %\end{array}
-    %\end{displaymath}
-    %% \input{./images/hypo.tex}
-  %\end{center}
-  %\caption{Observation Table and Corresponding Hypothesis}
-  %\label{fig:hypo}
-%\end{figure}
+More details on the active automata learning algorithm will be presented in Section
+\ref{sec:activelearning}.
 
-In the second iteration, we explore the successors of $(a,\rnoread)$. Fortunately, now every
-successor has an equivalence sequence in $obs.S$, \emph{i.e.}, itself. Consequently, the algorithm terminates
-with a closed hypothesis where all the unclosed edges turn into
-self-loop.
+%\subsection{Observation Table}
+%\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
+%hypothetical Mealy machines from the results of membership queries.
 
-%\begin{figure}[ht]
-  %\begin{center}
-    %\begin{displaymath}
-      %\begin{array}{l||ccccc||c}
-        %\hline
-        %& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        %\hline\hline
-        %\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        %\hline
-        %(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %(a,\rnoread),(a,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        %(a,\rnoread),(\bot,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        %(a,\rnoread),(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        %(a,\rnoread),(\bot,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty &
-        %(a,\rnoread) \\
-        %(a,\rnoread),T & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
-        %\hline
-      %\end{array}
-    %\end{displaymath}
-  %\end{center}
-  %\caption{A Closed Version of Fig. \ref{fig:hypo}}
-  %\label{fig:hypo2}
-%\end{figure}
+%Mealy machines consist of \emph{states} and \emph{transitions}.
+%As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
+%after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
+%state of $s$ after executing $a$.
+%However, under such notations, there are \emph{infinite} number of states, among which most are
+%duplicate.
 
-\subsection{Counter Examples' Analysis} 
-Apparently, the closed hypothesis presented in Fig. \ref{fig:hypo2} is different with the 2-Timer
-channel. It's easy to find a counter-example $s_0=(a,\rnoread),T,T,(\bot,\rread)$ where $mq(s_0)=a$ while
-according to the hypothesis, the result should be $\rempty$. In this section, we show how to
-find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.
+%States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
+%\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
+%\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
+%alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
+%\begin{definition}[$D$-Equivalence]
+  %Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
+  %$s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
+  %iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
+%\end{definition}
 
-Firstly, we give a formal definition of \emph{counter examples}. With an observation table $obs$ and
-a sequence $s$, we use $hq(obs,s)$ to denote the execution result of its corresponding hypothesis
-$\mathcal{H}$ under the input sequence
-$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $s=s'a,a\in\mathcal{I}$.
+%Now we use \emph{access sequence} to describe the states. Given an input sequence $s$, the access
+%sequence $acc(s,D)$ of $s$ is defined as the shortest sequence in $\{s'\in\mathcal{I}^*|s'\sim_D
+%s\}$\footnote{When there are multiple satisfying sequences with the same length, we use a certain tactic
+%to pick up one from them determinstically.}.
 
-\begin{definition}[Counter Example]
-  an input sequence $s$ is a counter example of $obs$ iff $mq(s)\neq hq(obs,s)$.
-\end{definition}
+%Formally, an observation table (see Fig. \ref{fig:hypo} as an example) is determined by a tuple $(S,D)$ where
+%$S\subset\mathcal{I}^*$ is a set of the access sequences of states and $D\subset\mathcal{I}^*$
+%is a set of suffixes. In such tables, columns are labelled with suffixes in $D$, and rows are
+%labelled with input sequences. As shown in Fig. \ref{fig:hypo}, rows are divided into two parts. The upper
+%part, labelled with access sequence $s\in S$, denotes the states covered in the current hypothesis.
+%The lower part, labelled with sequences in $\{sa|s\in S,a\in\mathcal{I}\}\backslash S$ (representing
+%any potentially unclosed transition) denotes all the transitions outside $s\in S$. A cell with row
+%label $s$ and column label $d$ is filled with $mq(sd)$.
 
-Now we consider the reason that leads to existance of counter examples. Since
-the suffix set $D$ is used to distinguish states, the existance of counter-examples
-shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
-$next$ (see Algorithm \ref{alg:buildtable}).
+%An observation table $(S,D)$ is \emph{closed} if 
+%\[
+%\forall s\in S,a\in\mathcal{I}.\exists s'\in S. sa\sim_D s'
+%\]
 
-For a counter example $s$, we need a new Suffix$(s,obs)$ to distinguish the uncovered state
-represented by $s$, which is defined as the longest sequence in
-\[
-\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
-\]
-After appending Suffix$(s,obs)$ to $D$, it's obvious that at least one uncovered state will be found.
+%From a closed observation table $obs$, we can construct a hypothetical Mealy machine $\mathcal{H}=\langle
+%S,s_0,\mathcal{I},\mathcal{O},\delta,\lambda\rangle$ in a straight-forward way:
+%\begin{itemize}
+  %\item[-] Every state in $S$ corresponds to an input sequence in $obs.S$
+  %\item[-] $s_0$ corresponds to the empty sequence $\varepsilon$
 
-The whole L* algorithm can be concluded as follows.
-\begin{algorithm} 
-  \caption{L*} 
-  \label{alg:lstar}
-  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
-  \KwOut{Observation table $obs$} 
-  $obs.S$ initialized as empty\;
-  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
-  \Repeat{$ce=true$}{
-    $obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
-    $ce=eq(obs)$\;
-    \If {$ce\neq true$} {
-      $obs.D$.append(Suffix$(ce, obs)$)\;
-    }
-  }
-  \Return $obs$\; 
-\end{algorithm}
+    %\emph{(we use input sequences to indicate their corresponding states in following parts)}
+  %\item[-] $\delta(s,a)=mq(sa)$
+  %\item[-] $\lambda(s,a)=acc(sa,obs.D)$. Since $obs$ is closed, we always have $\lambda(s,a)\in S$.
+%\end{itemize}
+
+%Algorithm \ref{alg:buildtable} shows how to build a closed observation table.
+
+%\begin{algorithm} 
+  %\caption{EncloseTable} 
+  %\label{alg:buildtable}
+  %\small
+  %\KwIn{An oracle interface $mq$, An input actions $\mathcal{I}$, An observation table $obs$}
+  %\KwOut{A closed observation table $obs'$} 
+  %\Repeat{$unclosed=\varnothing$}
+  %{
+    %$next=\{st|\forall s\in obs.S,\forall t\in \mathcal{I}\}\backslash obs.S$\;
+    %$unclosed=\{seq\in next|\forall a\in obs.S, seq \not\sim_{obs.D} a\}$\;
+    %$obs'.S$ = $obs.S\cup unclosed$\;
+    %$obs'.D$ = $obs.D$\;
+  %}
+  %\Return $obs'$\; 
+%\end{algorithm}
+
+%Taking a 2-Timer channel as an example, we now illustrate how this algorithm works. 
+%We assume that the source end of this 2-Timer channel is $A$, the sink end is $B$, and the alphabet
+%is $\{a\}$. We briefly denote $\{A\mapsto a,B\mapsto \rnoread\}$ and other input/output actions in form of
+%$(a,\rnoread)$.
+
+%Firstly, $obs.S$ is initialized with the initial state (denoted by $\varepsilon$), and $obs.D$ is
+%initialized with all one-step suffixes.
+%Then we explore all the access sequences in $obs.S$ and calculate its successors. Here
+%$unclosed$ consists of access sequences that has no equivalent sequence in $obs.S$. 
+%For example, Fig. \ref{fig:hypo} shows the $obs$ of a 2-Timer channel after the first
+%iteration. The five successors of $\varepsilon$ are presented at the bottom of the table, where
+%four are equivalent with $\varepsilon$ but $(a,\rnoread)$ is not. Therefore, we take $(a,\rnoread)$ as a
+%brand-new state and all of its successors need further exploration.
+
+%%\begin{figure}[ht]
+  %%\begin{center}
+    %%\begin{displaymath}
+      %%\begin{array}{l||ccccc||c}
+        %%\hline
+        %%& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
+        %%\hline\hline
+        %%\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %%\hline
+        %%(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %%(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%\rowcolor[gray]{.9}
+        %%(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
+        %%(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%\hline
+      %%\end{array}
+    %%\end{displaymath}
+    %%% \input{./images/hypo.tex}
+  %%\end{center}
+  %%\caption{Observation Table and Corresponding Hypothesis}
+  %%\label{fig:hypo}
+%%\end{figure}
+
+%In the second iteration, we explore the successors of $(a,\rnoread)$. Fortunately, now every
+%successor has an equivalence sequence in $obs.S$, \emph{i.e.}, itself. Consequently, the algorithm terminates
+%with a closed hypothesis where all the unclosed edges turn into
+%self-loop.
+
+%%\begin{figure}[ht]
+  %%\begin{center}
+    %%\begin{displaymath}
+      %%\begin{array}{l||ccccc||c}
+        %%\hline
+        %%& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
+        %%\hline\hline
+        %%\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %%\hline
+        %%(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        %%(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        %%(a,\rnoread),(a,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %%(a,\rnoread),(\bot,\rread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %%(a,\rnoread),(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %%(a,\rnoread),(\bot,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty &
+        %%(a,\rnoread) \\
+        %%(a,\rnoread),T & \rblock & \rblock & \rblock & \rempty & \rempty & (a,\rnoread) \\
+        %%\hline
+      %%\end{array}
+    %%\end{displaymath}
+  %%\end{center}
+  %%\caption{A Closed Version of Fig. \ref{fig:hypo}}
+  %%\label{fig:hypo2}
+%%\end{figure}
+
+%\subsection{Counter Examples' Analysis} 
+%Apparently, the closed hypothesis presented in Fig. \ref{fig:hypo2} is different with the 2-Timer
+%channel. It's easy to find a counter-example $s_0=(a,\rnoread),T,T,(\bot,\rread)$ where $mq(s_0)=a$ while
+%according to the hypothesis, the result should be $\rempty$. In this section, we show how to
+%find and analyze counter-examples using the method in \cite{DBLP:conf/sfm/SteffenHM11}.
+
+%Firstly, we give a formal definition of \emph{counter examples}. With an observation table $obs$ and
+%a sequence $s$, we use $hq(obs,s)$ to denote the execution result of its corresponding hypothesis
+%$\mathcal{H}$ under the input sequence
+%$s$. Obviously we have $hq(obs,s) = mq(acc(s')a)$ where $s=s'a,a\in\mathcal{I}$.
+
+%\begin{definition}[Counter Example]
+  %an input sequence $s$ is a counter example of $obs$ iff $mq(s)\neq hq(obs,s)$.
+%\end{definition}
+
+%Now we consider the reason that leads to existance of counter examples. Since
+%the suffix set $D$ is used to distinguish states, the existance of counter-examples
+%shows that the current suffix set $D$ is not powerful enough to recognize the uncovered states in
+%$next$ (see Algorithm \ref{alg:buildtable}).
+
+%For a counter example $s$, we need a new Suffix$(s,obs)$ to distinguish the uncovered state
+%represented by $s$, which is defined as the longest sequence in
+%\[
+%\{d\in\mathcal{I}^+|s=s'd, mq(acc(s',obs.D)d)\neq mq(s)\}
+%\]
+%After appending Suffix$(s,obs)$ to $D$, it's obvious that at least one uncovered state will be found.
+
+%The whole L* algorithm can be concluded as follows.
+%\begin{algorithm} 
+  %\caption{L*} 
+  %\label{alg:lstar}
+  %\KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
+  %\KwOut{Observation table $obs$} 
+  %$obs.S$ initialized as empty\;
+  %$obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
+  %\Repeat{$ce=true$}{
+    %$obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
+    %$ce=eq(obs)$\;
+    %\If {$ce\neq true$} {
+      %$obs.D$.append(Suffix$(ce, obs)$)\;
+    %}
+  %}
+  %\Return $obs$\; 
+%\end{algorithm}
 
@@
 Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
-Golang\cite{golang}, which is widely known for its elegant design and impressive efficiency.
-Moreover, with a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model, \texttt{Golang} shares many
-similar ideas with Reo, and in turn makes our implementation much more natural.
+Golang. With a CSP-style\cite{DBLP:books/ph/Hoare85} cocurrency model, the Google-production language
+\texttt{Golang} shares quite a few similar ideas with Reo, and in turn makes our implementation much
+more natural.
 
 All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
-of RAM and a Core i7-3630 CPU. The source code is available at
-\url{https://github.com/liyi-david/reo-learn}.
+of RAM and a Core i7-3630 CPU. The source code is available at \cite{reo-learn-github}.
 
@@
 However, when dealing with timed connectors, the algorithm failed to meet our expectation.
-\todo{draw the two tables in github}
-%\begin{table}[ht]
-  %\renewcommand{\arraystretch}{1.3}
-  %\caption{Time-Cost Analysis}
-  %\label{tabel:timecost}
-  %\centering
-  %\begin{tabular}{l||rrr}
-    %\hline
-    %& FIFO1 & Alternator & Gate \\
-    %\hline\hline
-    %Membership Query(s) & 41.571 & 126.468 & 169.161 \\
-    %Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
-    %Total Time(s) & 41.715 & 165.114 & 247.098 \\
-    %Membership Query(\%) & 99.6 & 76.6 & 68.5 \\
-    %\hline
-  %\end{tabular}
-%\end{table}
+
+\begin{table}[ht]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Time-Cost Analysis}
+  \label{tabel:timecost}
+  \centering
+  \begin{tabular}{l||rrr}
+    \hline
+    & FIFO1 & Alternator & Gate \\
+    \hline\hline
+    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
+    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
+    Total Time(s) & 41.715 & 165.114 & 247.098 \\
+    Membership Query(\%) & 99.6 & 76.6 & 68.5 \\
+    \hline
+  \end{tabular}
+\end{table}
 
@@
 
-%\begin{table}[ht]
-  %\renewcommand{\arraystretch}{1.3}
-  %\caption{Reduction of Membership Queries}
-  %\label{tabel:cacheoptimization}
-  %\centering
-  %\begin{tabular}{l||rrr}
-    %\hline
-    %& FIFO & Alternator & Gate \\
-    %\hline\hline
-    %Original Algorithm & 93 & 880 & 1034 \\
-    %Cached Algorithm & 90 & 725 & 707 \\
-    %Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
-    %\hline
-  %\end{tabular}
-%\end{table}
+\begin{table}[ht]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Reduction of Membership Queries}
+  \label{tabel:cacheoptimization}
+  \centering
+  \begin{tabular}{l||rrr}
+    \hline
+    & FIFO & Alternator & Gate \\
+    \hline\hline
+    Original Algorithm & 93 & 880 & 1034 \\
+    Cached Algorithm & 90 & 725 & 707 \\
+    Reduction Rate & 3.2\% & 21.4\% & 31.6\% \\
+    \hline
+  \end{tabular}
+\end{table}
 

### 2016-04-14 shortpaper/paper.tex
.

@@
 Similarly, we can use PMMs to describe the behavior of other basic timed Reo
-channels. Now we show how to compose these channels into more complicated connectors.
+channels. In Reo, as mentioned before, we compose complex connectors with simpler ones and basic
+channels recursively. Operator \emph{prod} and \emph{link} are used to apply such composing
+operation.
 
-\liyi{Actually I'm not sure if omitting definition of prod and link is a good idea. Generally I
-think this paper should focus on two parts: definition of PMM and optimization of L* algorithm.}
+\begin{definition}[prod]
+  For two PMMs $\mathcal{PM}_1$ and $\mathcal{PM}_2$, we use the \emph{prod} operator
+  $\mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)$ to denote their production, where every
+  sink-end in $\mathcal{PM}_1$ is connected with it's homonymic source-end in $\mathcal{PM}_2$.
+\end{definition}
+
+\begin{definition}[link]
+  For a PMM $\mathcal{PM}$, we use the \emph{link} operator to connect its sink-end $\OUT$ with its
+  source-end $\IN$, formally denoted as $\mathcal{PM}' = link(\mathcal{PM}, \OUT, \IN)$.
+\end{definition}
 
@@
 \label{sec:activelearning}
-In this section, we use L* algorithm to extract Reo coordinators from blackbox
-implementations in 3 steps:
+In this section, we provide a brief introduction on the well-known L* algorithm, which is used
+to extract Reo coordinators from blackbox implementations in 3 steps:
 \emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. 
@@
 
-\subsection{Active Learning: Overview}
-In this section, we briefly introduce the main ideas of active automata learning.
-
+\subsection{An Overview of Active Learning}
 Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
@@
   \begin{center}
-    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
+    \includegraphics[width=.45\textwidth]{./images/actl.pdf}
   \end{center}
@@
 Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
-all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate Teacher}
+all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate
+Teacher} \cite{DBLP:journals/iandc/Angluin87}
 interface, which is responsible for two types of queries.
@@
 repeat the hypothesis construction until the equivalence query returns \emph{true}.
-
-More details on the active automata learning algorithm will be presented in Section
-\ref{sec:activelearning}.
 
@@
 
-%The whole L* algorithm can be concluded as follows.
-%\begin{algorithm} 
-  %\caption{L*} 
-  %\label{alg:lstar}
-  %\KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
-  %\KwOut{Observation table $obs$} 
-  %$obs.S$ initialized as empty\;
-  %$obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
-  %\Repeat{$ce=true$}{
-    %$obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
-    %$ce=eq(obs)$\;
-    %\If {$ce\neq true$} {
-      %$obs.D$.append(Suffix$(ce, obs)$)\;
-    %}
-  %}
-  %\Return $obs$\; 
-%\end{algorithm}
+\subsection{L* Algorithm}
+The whole L* algorithm can be concluded as follows.
+\begin{algorithm} 
+  \caption{L*} 
+  \label{alg:lstar}
+  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
+  \KwOut{Observation table $obs$} 
+  $obs.S$ initialized as empty\;
+  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
+  \Repeat{$ce=true$}{
+    $obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
+    $ce=eq(obs)$\;
+    \If {$ce\neq true$} {
+      $obs.D$.append(Suffix$(ce, obs)$)\;
+    }
+  }
+  \Return $obs$\; 
+\end{algorithm}
+
+In this algorithm, when we use \emph{observation tables} to represent hypothetical models.
 
@@
 
-With cache applied, we have made considerable reduction on the calls of membership queries. The results
+With the help of cache technique, we have made considerable reduction on the calls of membership queries. The results
 can be found in Table \ref{tabel:cacheoptimization}.
 
-\section{Conclusion and Future Work}
+\section{Conclusion and Fu ture Work}
 In this paper, we come up with an approach to extract timed connectors from blackbox

### 2016-04-17 shortpaper/paper.tex
.

@@
 
-%\subsection{Observation Table}
-%\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
-%hypothetical Mealy machines from the results of membership queries.
+\subsection{Observation Table}
+\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
+hypothetical Mealy machines from the results of membership queries.
 
-%Mealy machines consist of \emph{states} and \emph{transitions}.
-%As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
-%after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
-%state of $s$ after executing $a$.
-%However, under such notations, there are \emph{infinite} number of states, among which most are
-%duplicate.
+Mealy machines consist of \emph{states} and \emph{transitions}.
+As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
+after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
+state of $s$ after executing $a$.
+However, under such notations, there are \emph{infinite} number of states, among which most are
+duplicate.
 
-%States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
-%\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
-%\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
-%alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
-%\begin{definition}[$D$-Equivalence]
-  %Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
-  %$s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
-  %iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
-%\end{definition}
+States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
+\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
+\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
+alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
+\begin{definition}[$D$-Equivalence]
+  Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
+  $s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
+  iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
+\end{definition}
 

### 2016-04-18 shortpaper/paper.tex
.

@@
 When applying active automata learning on some model, we assume that the model should be equivalent
-to some \emph{Mealy machine}, i.e., a deterministic model accepting a finite set of inputs and
-mapping them to a finite set of outputs.
-
+to some \emph{Mealy machine}.
 Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
@@
     (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
-    equivalent to the system-under-learn and generates a counter-example if needed. Generally,
-    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
-    approximate results.
+    equivalent to the system-under-learn and generates a counter-example if needed. 
 \end{itemize}
@@
 \subsection{Observation Table}
-\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
-hypothetical Mealy machines from the results of membership queries.
+\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to describe
+hypothetical Mealy machines in learning algorithm L*.
 
-Mealy machines consist of \emph{states} and \emph{transitions}.
-As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
-after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
+As mentioned before, Mealy machines consist of \emph{states} and \emph{transitions}. However in
+blackboxes, we only have \emph{input sequences} and their corresponding \emph{outputs}.
+Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
 state of $s$ after executing $a$.
@@
 
-%%\begin{figure}[ht]
-  %%\begin{center}
-    %%\begin{displaymath}
-      %%\begin{array}{l||ccccc||c}
-        %%\hline
-        %%& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        %%\hline\hline
-        %%\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %%\hline
-        %%(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %%(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%\rowcolor[gray]{.9}
-        %%(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
-        %%(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%\hline
-      %%\end{array}
-    %%\end{displaymath}
-    %%% \input{./images/hypo.tex}
-  %%\end{center}
-  %%\caption{Observation Table and Corresponding Hypothesis}
-  %%\label{fig:hypo}
-%%\end{figure}
+\begin{figure}[ht]
+  \begin{center}
+    \footnotesize
+    \begin{displaymath}
+      \begin{array}{l||ccccc||c}
+        \hline
+        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
+        \hline\hline
+        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        \hline
+        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
+        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        \rowcolor[gray]{.9}
+        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
+        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
+        \hline
+      \end{array}
+    \end{displaymath}
+    % \input{./images/hypo.tex}
+  \end{center}
+  \caption{Observation Table and Corresponding Hypothesis}
+  \label{fig:hypo}
+\end{figure}
 

### 2016-04-19 shortpaper/paper.tex
.

--- 2016-04-14 shortpaper/paper.tex
@@
 %\subsection{Observation Table}
-%\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
-%hypothetical Mealy machines from the results of membership queries.
+%\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to describe
+%hypothesises in form of Mealy machines.
+%As mentioned before, Mealy machines are composed of \emph{states} and \emph{transitions}. However, in
+%blackboxes, only \emph{input sequences} and their corresponding \emph{outputs} are observable. A
+%natural idea is to use input sequences to indicate their corresponding states, and outputs to
+%describe the edges.
 
-%Mealy machines consist of \emph{states} and \emph{transitions}.
-%As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
-%after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
-%state of $s$ after executing $a$.
+%\begin{figure}[ht]
+  %\begin{center}
+    %\footnotesize
+    %\begin{displaymath}
+      %\begin{array}{l||ccccc}
+        %\hline
+        %& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T \\
+        %\hline\hline
+        %\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty  \\
+        %\hline
+        %(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        %(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        %\rowcolor[gray]{.9}
+        %(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty \\
+        %(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty \\
+        %T & \rblock & \rblock & \rempty & \rempty & \rempty  \\
+        %\hline
+      %\end{array}
+    %\end{displaymath}
+    %% \input{./images/hypo.tex}
+  %\end{center}
+  %\caption{Observation Table}
+  %\label{fig:hypo}
+%\end{figure}
+
 %However, under such notations, there are \emph{infinite} number of states, among which most are
 %duplicate.
-
-%States are distinguished, usually, by their \emph{subsequent behavior}. Suppose $s_1\neq s_2\in
-%\mathcal{I}^*$, we say the corresponding of states $s_1$ and $s_2$ are equivalent iff $\forall d\in
-%\mathcal{I}^+. mq(s_1d)=mq(s_2d)$. Since we can never check it on every $d\in\mathcal{I}^+$, an
-%alternative way is to use a set of \emph{suffixes} to distinguish them approximately.
-%\begin{definition}[$D$-Equivalence]
-  %Provided with a set of suffixes $D\subset\mathcal{I}^+$, the corresponding states of
-  %$s_1,s_2\in\mathcal{I}^*$ are $D$-equivalent (denoted as $s_1\sim_D s_2$)
-  %iff $mq(s_1d) = mq(s_2d)$ for all $d\in D$.
-%\end{definition}
 
@@
 
-%%\begin{figure}[ht]
-  %%\begin{center}
-    %%\begin{displaymath}
-      %%\begin{array}{l||ccccc||c}
-        %%\hline
-        %%& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
-        %%\hline\hline
-        %%\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %%\hline
-        %%(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
-        %%(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%\rowcolor[gray]{.9}
-        %%(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
-        %%(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
-        %%\hline
-      %%\end{array}
-    %%\end{displaymath}
-    %%% \input{./images/hypo.tex}
-  %%\end{center}
-  %%\caption{Observation Table and Corresponding Hypothesis}
-  %%\label{fig:hypo}
-%%\end{figure}
-
 %In the second iteration, we explore the successors of $(a,\rnoread)$. Fortunately, now every
@@
 \subsection{L* Algorithm}
-The whole L* algorithm can be concluded as follows.
+The whole L* algorithm can be briefly concluded as follows. In this algorithm,
+\begin{itemize}
+  \item \emph{observation table} is a widely-used data structure to describe the hypothesis.
+\end{itemize}
+Please refer to \cite{DBLP:conf/sfm/SteffenHM11, DBLP:journals/iandc/Angluin87} for further details.
 \begin{algorithm} 
@@
   \Repeat{$ce=true$}{
-    $obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
+    $obs$ = EncloseHypothesis($mq$, $\mathcal{I}$, $obs$)\;
     $ce=eq(obs)$\;
@@
 
-In this algorithm, when we use \emph{observation tables} to represent hypothetical models.
+The L* algorithm takes a set of input actions $\mathcal{I}$ and a oracle interface (which plays the
+role of SUL) as its parameters. And it returns a so-called \emph{observation table} as the final
+hypothesis. (Observation table is a widely-used data structure, which can represent a Mealy machine
+by its external observation.)
+In each iteration, the algorithm will:
+\begin{enumerate}
+  \item \emph{Enclose the hypothesis.} Active learning is very similar to a breadth-first-search
+    process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
+    explore different input actions and check if they can lead to some state that is already known.
+    If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
+  \item \emph{Equivalence checking.} After the hypothesis is enclosed, we need to check if the
+    current hypothesis is equivalent to the real model. Such $eq$ operation returns a
+    \emph{true} if they are equivalent, or a counter-example if not.
+  \item \emph{Counter-example Analysis.}  
+\end{enumerate}
 

### 2016-04-20 shortpaper/paper.tex
.

@@
 \begin{itemize}
-  \item \emph{observation table} is a widely-used data structure to describe the hypothesis.
+  \item \emph{Observation table} is a widely-used data structure to describe the hypothesis. In such
+    tables, rows correspond to a states (denoted as $S$), and columns correspond to \emph{suffixes}
+    (denoted as $D$).
+  \item \emph{Suffixes} are used to distinguish different states. For example, two input sequences
+    $a$ and $b$ lead to the same state iff. $\forall c\in\mathcal{I}^*, mq(ac) = mq(bc)$.
 \end{itemize}
@@
     \emph{true} if they are equivalent, or a counter-example if not.
-  \item \emph{Counter-example Analysis.}  
+  \item \emph{Counter-example Analysis.} As mentioned before, we use suffixes to distinguish
+    different states. Consequently, lack of proper suffix may lead to counter-examples. By the
+    \emph{suffix} function, we can analyze the counter-example and find out which suffix is left out.
 \end{enumerate}

### 2016-04-20 shortpaper/paper.tex
.

@@
   \begin{center}
-    \includegraphics[width=.45\textwidth]{./images/actl.pdf}
+    \includegraphics[width=.45\textwidth]{./images/actl.png}
   \end{center}
@@
     process on an unknown Mealy machine. At first, only the initial state is visible to us. We then
-    explore different input actions and check if they can lead to some state that is already known.
+    explore different input actions, and check if their following state is already explored.
     If every edge targets to an explored state, we will say that the hypothesis is \emph{closed}.
-  \item \emph{Equivalence checking.} After the hypothesis is enclosed, we need to check if the
-    current hypothesis is equivalent to the real model. Such $eq$ operation returns a
-    \emph{true} if they are equivalent, or a counter-example if not.
+  \item \emph{Equivalence checking.} With a closed hypothesis generated, we still need $eq$ to check
+    if it is equivalent to the system-under-learn. \emph{Eq} returns \emph{true} if they are
+    equivalent, or a counter-example if not.
   \item \emph{Counter-example Analysis.} As mentioned before, we use suffixes to distinguish
-    different states. Consequently, lack of proper suffix may lead to counter-examples. By the
-    \emph{suffix} function, we can analyze the counter-example and find out which suffix is left out.
+    different states. Consequently, the correctness of our hypothesis relies heavily on proper suffixes.
+    The \emph{suffix} function are designed to analyze counter-examples and find out which suffix is
+    left out.
 \end{enumerate}
@@
 
-\section{Conclusion and Fu ture Work}
+\section{Conclusion and Future Work}
 In this paper, we come up with an approach to extract timed connectors from blackbox
